### 2019-10-02 paper/egpaper_final.tex
Add CVPR template

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2020 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for CVPR 2020.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2020 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these 
proceedings at the IEEE Computer Society Press: 
\url{https://www.computer.org/about/contact}.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2019-10-02 paper/egpaper_for_review.tex
Add CVPR template

--- 2019-10-02 paper/egpaper_final.tex
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\cvprfinalcopy % *** Uncomment this line for the final submission
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\ifcvprfinal\pagestyle{empty}\fi
 \begin{document}
@@
 high.
-Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
 

### 2019-10-04 newser/models/transformer_pointer_faster.py
Update pointer generation

@@ -542,6 +542,8 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
         X_article = X_article.transpose(0, 1)
         # X_article.shape == [seq_len, batch_size, embed_size]
 
+        Xs = []
+
         for i in range(gen_len):
             if i == 0:
                 prev_target = {self.index: seed_input}
@@ -578,10 +580,21 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
             X = decoder_out[0]
             # X.shape == [batch_size, 1, embed_size]
 
-            entity_logits = self.entity_fc(X)
-            # entity_logits.shape == [batch_size, 1, 2]
+            Xs.append(X)
 
-            entity_logits = entity_logits.squeeze(1)
+            X_full = torch.cat(Xs, dim=1)
+            # X.shape == [batch_size_i, target_len, embed_size]
+
+            X_full = X_full.transpose(0, 1)
+            # X.shape == [target_len, batch_size_i, embed_size]
+
+            X_entity = self.entity_attn(X_full)
+            # X_entity.shape == [target_len, batch_size_i, embed_size]
+
+            X_entity = X_entity.transpose(0, 1)
+            # X_entity.shape == [batch_size_i, target_len, embed_size]
+
+            entity_logits = self.entity_fc(X_entity[:, -1])
             # entity_logits.shape == [batch_size, 2]
 
             should_copy = entity_logits.argmax(dim=-1) == 1
@@ -724,6 +737,8 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
             active_idx = ~is_eos
 
             full_active_idx[full_active_idx.nonzero()[~active_idx]] = 0
+
+            Xs = [x[active_idx] for x in Xs]
 
             seed_input = seed_input[active_idx]
 

### 2019-10-08 paper/paper.tex
Copy template
Add structure to paper

--- 2019-10-02 paper/egpaper_for_review.tex
@@
 \usepackage{amssymb}
+\usepackage{booktabs}
 
@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for CVPR Proceedings}
+\title{News Image Captioning with Transformers}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Alasdair Tran, Alexander Matthews, Lexing Xie\\
+Australian National University\\
+{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
 }
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+   In this work, we present an end-to-end captioning system for news articles
+   that can handle entity names and out-of-vocabulary words. Our model achieves
+   state-of-the-art results on the existing ``GoodNews" dataset. We also
+   re-collected news articles from the New York Times, which are cleaner and
+   more complete. This dataset allows us to explore approaches involving
+   image positions. The code will be made available on GitHub.
 \end{abstract}
@@
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+Our main contributions are as follows:
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+\begin{itemize}
+   \item We scraped articles and images from the New York Times to create the
+   largest news image captioning with 794K images, each with an associated
+   caption and article.
+   \item We use the transformer architecture and Byte Pair Encoding to develop
+   an end-to-end encoder-decoder model that achieves state-of-the-art results
+   on news image captioning.
+   \item
+\end{itemize}
 
-All manuscripts must be in English.
+\section{Related Works}
 
-\subsection{Dual submission}
+Recent image captioning systems are based mostly on ``Show, Attend, Tell"
+\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
+improvements include giving the model the option to not attend to any image
+region \cite{Lu2016KnowingWT}, using reinforcement learning to directly
+optimize for the CIDEr metric \cite{Rennie2016SelfCriticalST}, and using a
+bottom-up approach to propose a region to attend to
+\cite{Anderson2017BottomUpAT}. All of these system generate generic captions.
 
-Please refer to the author guidelines on the CVPR 2020 web page for a
-discussion of the policy on dual submissions.
+A more challenging task is to generate captions for news images, in which we
+need to be able to generate entity names. There are non-neural approaches
+\cite{Feng2013AutomaticCG,Tariq2017ACE}. Neural approaches include using the
+word2vec representation of the article and and the VGG19 representation of the
+image as context to the LSTM generator \cite{Ramisa2016BreakingNewsAA}.
 
-\subsection{Paper length}
-Papers, excluding the references section,
-must be no longer than eight pages in length. The references section
-will not be included in the page count, and there is no limit on the
-length of the references section. For example, a paper of eight pages
-with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for CVPR 2020.}
-
-Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the CVPR70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
+Biten \etal~\cite{Biten2019GoodNews} further refined this approach by
+developing a two-stage architecture to handle entity names. In the first stage,
+the model generates a template with placeholders such as PERSON and
+ORGANIZATION. In the second stage, the model finds the best matched sentence in
+the article and replace the placeholder with an entity mentioned in that
+sentence. They also created the ``GoodNews" dataset, which contains more
+samples than MSCOCO \cite{Lin2014MicrosoftCC} and BreakingNews
+\cite{Ramisa2016BreakingNewsAA} datasets.
 
@@
    \end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
+      \caption{An example caption.}
    \label{fig:long}
@@
 
-\subsection{Miscellaneous}
+\section{Dataset}
 
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
+A summary of the original GoodNews dataset and our new dataset is shown in
+Table \ref{tab:datasets}. The GoodNews+ dataset is our attempt at recollecting
+the original GoodNews dataset. We managed to crawl all the original articles,
+but the number of images is slightly less, either due to dead links or
+not crawling images unrelated to the main article. GoodNews+ allows us to make the
+following observations about the original GoodNews dataset:
 
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
+\begin{itemize}
+   \item On average, half of the article body is missing. This includes
+         the first few paragraphs that might contain important information
+         about the top caption.
+   \item The dataset contains a small number Spanish articles.
+   \item Sometimes images from the recommendation sidebar, which are not part
+         of the main article, are included in the dataset.
+\end{itemize}
 
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
+This motivates us to recollect data from the New York Times in a more careful
+manner. We call this NYTimes+.
 
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
+\begin{table}[t]
+	\caption {Summary of datasets}
+	\label{tab:datasets}
+	\centering
+	\begin{tabular}{llll}
+		\toprule
+		  & GoodNews  & GoodNews+ &   NYTimes+ \\
+		\midrule
+      No of articles & 241 808 & 241 808 & 445 828 \\
+      No of images   & 462 642 & 440 112 & 794 085 \\
+      Article length & 451 & 963 & 974 \\
+      Caption length & 18 & 18 & 18 \\
+      Start month & Jan 10 & Jan 10 & Mar 05\\
+      End month & Jul 18 & Jul 18 & Sep 19 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
+In addition to having a more complete coverage, we also collect information
+about the image position in each article. As shown in Figure \ref{fig:dist},
+about 40\% of the articles have two or more images.
 
-\begin{figure*}
+\begin{figure}[h]
+   \begin{center}
+   \includegraphics[width=0.8\linewidth]{figures/caption_dist.png}
+   \end{center}
+      \caption{Distribution of images across articles.}
+   \label{fig:dist}
+   \end{figure}
+
+\section{Model}
+
+Devlin \etal \cite{Devlin2019BERT} introduced BERT, a language representation
+model which provides pretrained contextual embeddings for text. We use
+RoBERTa \cite{Liu2019RoBERTaAR}, a more carefully trained BERT model, to
+embed the article text. There there two key advantages:
+
+\begin{itemize}
+   \item Unlike glove \cite{Pennington2014Glove} or word2vec
+   \cite{Mikolov2013DistributedRO} where each word has exactly one
+   representation, the bidirectional and attention mechanism in transformers
+   allow words to have different representation depending on the context.
+   \item RoBERTa uses Byte-Pair Encoding (BPE)
+   \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which allows us to
+   represent and generate potentially any word that can be written in
+   Unicode. The vocabulary size is 50,265.
+\end{itemize}
+
+Our decoder is a transformer architecture with dynamic convolutions
+\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
+found that using dynamic convolutions allows the training to converge faster
+than using the current state-of-the-art GPT-2 architecture
+\cite{Radford2019LanguageMA}. We don't have the computational resource to study
+the performance of GPT-2.
+
+To make training more efficient, we use adaptive softmax
+\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
+15K, and 25K. We tie the adaptive weights and we share the decoder input and
+output embeddings. We use sinusoidal positional encoding
+\cite{Vaswani2017AttentionIA} to represent the position of each token.
+
+We use ResNeXt-101 \cite{Xie2016AggregatedRT} to obtain an embedding for
+the images. For each generation step, we use the Scalar-Dot-Product attention
+\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
+The two attended representations are then concatenated and fed as input to
+the self-attention layer.
+
+\begin{figure*}[t]
    \begin{center}
@@
    \end{center}
-   \caption{Example of a short caption, which should be centered.}
+      \caption{Overall architecture of the model.}
    \label{fig:short}
@@
 
-%------------------------------------------------------------------------
-\section{Formatting your paper}
+\section{Results}
 
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
+Table \ref{tab:results-goodnews} shows the results on the original GoodNews
+dataset. Table \ref{tab:results-nytimes} shows additional results done on
+our NYTimes+ dataset.
 
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
+\begin{table*}[t]
+	\caption {Results on the GoodNews dataset}
+	\label{tab:results-goodnews}
+	\centering
+	\begin{tabular}{llllll}
+		\toprule
+		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE \\
+		\midrule
+      Biten \etal \cite{Biten2019GoodNews} & 8.92\% & 3.54\% & 1.60\% & 0.83\% & 12.1\% \\
+      Transformer & 19.2\% & 10.3\% & 5.40\% & 3.13\% & 21.4\% \\
+      \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
+\begin{table*}[t]
+	\caption {Results on the NYTimes+ dataset}
+	\label{tab:results-nytimes}
+	\centering
+	\begin{tabular}{llllll}
+		\toprule
+		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE \\
+		\midrule
+      Transformer & 15.4\% & 7.90\% & 3.93\% & 2.26\% & 19.1\% \\
+      Transformer + Surrounding Text & 16.8\% & 9.09\% & 4.55\% & 2.62\% & 20.5\% \\
+      \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
 
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the CVPR 2020 web page for a discussion
-of the use of color in your document.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
-Please direct any questions to the production editor in charge of these
-proceedings at the IEEE Computer Society Press: 
-\url{https://www.computer.org/about/contact}.
+\section{Conclusion}
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{egbib}
+\bibliography{paper}
 }

### 2019-10-08 scripts/annotate_nytimes_corefs.py
Fix bug in coref annotation

@@ -67,7 +67,7 @@ def get_clusters(doc, article):
                 'text': coref.text,
                 'start': s,
                 'end': e,
-                'pos': [span.pos_ for span in main_span],
+                'pos': [span.pos_ for span in coref],
             }
 
             kept_cluster['mentions'].append(mention)
@@ -139,12 +139,13 @@ def main():
     article_cursor = db.articles.find({
         'parsed': True,  # article body is parsed into paragraphs
         'n_images': {'$gt': 0},  # at least one image is present
+        'language': 'en',
     }, no_cursor_timeout=True).batch_size(128)
 
     logger.info('Annotating articles.')
     for article in tqdm(article_cursor):
-        if 'coref_clusters' in article:
-            continue
+        # if 'coref_clusters' in article:
+        #     continue
 
         calculate_spacy_positions(article)
 

### 2019-10-08 scripts/annotate_nytimes_corefs.py
Annotate parts of speech

@@ -11,6 +11,7 @@ Options:
 import ptvsd
 import spacy
 from docopt import docopt
+from joblib import Parallel, delayed
 from pymongo import MongoClient
 from schema import And, Or, Schema, Use
 from tqdm import tqdm
@@ -45,12 +46,20 @@ def get_clusters(doc, article):
         start = main_span.start_char
         end = main_span.end_char
 
+        pos = []
+        for tok in main_span:
+            pos.append({
+                'start': tok.idx,
+                'end': tok.idx + len(tok.text),
+                'text': tok.text,
+                'pos': tok.pos_,
+            })
         kept_cluster = {
             'main': {
-                'text': main_span.text,
                 'start': start,
                 'end': end,
-                'pos': [span.pos_ for span in main_span],
+                'text': main_span.text,
+                'pos': pos,
             },
             'mentions': [],
         }
@@ -63,11 +72,19 @@ def get_clusters(doc, article):
             if s == start and e == end:
                 continue
 
+            pos = []
+            for tok in main_span:
+                pos.append({
+                    'start': tok.idx,
+                    'end': tok.idx + len(tok.text),
+                    'text': tok.text,
+                    'pos': tok.pos_,
+                })
             mention = {
-                'text': coref.text,
                 'start': s,
                 'end': e,
-                'pos': [span.pos_ for span in coref],
+                'text': coref.text,
+                'pos': pos,
             }
 
             kept_cluster['mentions'].append(mention)
@@ -92,14 +109,56 @@ def assign_coref_to_section(section, coref, i, kind, mention_idx):
     s = section['spacy_start']
     e = section['spacy_end']
     if coref['start'] >= s and coref['end'] <= e:
+        pos = []
+        for o_pos in coref['pos']:
+            pos.append({
+                'start': o_pos['start'] - s,
+                'end': o_pos['end'] - s,
+                'text': o_pos['text'],
+                'pos': o_pos['pos'],
+            })
+
         section['corefs'].append({
             'cluster_idx': i,
             'kind': kind,
             'mention_index': mention_idx,
+            'start': coref['start'] - s,
+            'end': coref['end'] - s,
             'text': coref['text'],
-            'start': coref['start'] - section['spacy_start'],
-            'end': coref['end'] - section['spacy_start'],
[…]

### 2019-10-12 paper/paper.tex
Update contributions

@@
 \begin{itemize}
-   \item We scraped articles and images from the New York Times to create the
-   largest news image captioning with 794K images, each with an associated
-   caption and article.
-   \item We use the transformer architecture and Byte Pair Encoding to develop
-   an end-to-end encoder-decoder model that achieves state-of-the-art results
-   on news image captioning.
-   \item
+   \item We show that combining article attention with pre-trained contextualized
+   word piece embeddings allows our model to generate captions containing
+   relevant words that were not seen during training.
+
+   \item We demonstrate that the location of the image within the article is an
+   important signal for generating relevant news captions.
+
+   \item We build on the “Good News” dataset to produce a larger and more complete
+   news captioning dataset consisting of * articles from the New York Times and
+   their 794K images with captions. In contrast to “Good News” our dataset
+   contains the full article text, and the location of the image within the
+   page.
 \end{itemize}

### 2019-10-13 newser/data/__init__.py
Attend over proper names

@@ -1,4 +1,5 @@
 import newser.data.dataset_readers
 import newser.data.token_indexers
+import newser.data.tokenizers
 
 from .vocabulary import RobertaVocabulary

### 2019-10-13 newser/data/dataset_readers/__init__.py

@@ -4,4 +4,5 @@ from .goodnews_coref import CorefGoodNewsReader
 from .goodnews_flattened import FlattenedGoodNewsReader
 from .goodnews_rare import RareGoodNewsReader
 from .nytimes import NYTimesReader
+from .nytimes_names import NYTimesNamesReader
 from .nytimes_position import NYTimesPositionReader

### 2019-10-13 newser/data/dataset_readers/goodnews_coref.py

@@ -89,11 +89,11 @@ class CorefGoodNewsReader(DatasetReader):
             clusters = self.db.corefs.find_one(
                 {'_id': sample['_id']})['clusters']
 
-            yield self.article_to_instance(article, image, sample['image_index'], clusters)
+            yield self.article_to_instance(article, image, sample['image_index'], clusters, image_path)
 
         sample_cursor.close()
 
-    def article_to_instance(self, article, image, image_index, clusters) -> Instance:
+    def article_to_instance(self, article, image, image_index, clusters, image_path) -> Instance:
         context = article['context'].strip()
 
         caption = article['images'][image_index]
@@ -129,7 +129,9 @@ class CorefGoodNewsReader(DatasetReader):
 
         metadata = {'context': context,
                     'caption': caption,
-                    'web_url': article['web_url']}
+                    'web_url': article['web_url'],
+                    'image_path': image_path,
+                    }
         fields['metadata'] = MetadataField(metadata)
 
         return Instance(fields)

### 2019-10-13 newser/data/dataset_readers/nytimes_names.py

@@ -1,0 +1,198 @@
+import logging
+import os
+import random
+from datetime import datetime
+from typing import Dict
+
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
+                                    ToTensor)
+
+from newser.data.fields import CorefTextField, ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+@DatasetReader.register('nytimes_names')
+class NYTimesNamesReader(DatasetReader):
+    """Read from the New York Times dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.nytimes
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        random.seed(1234)
+
+    @overrides
+    def _read(self, split: str):
+        # split can be either train, valid, or test
+        # validation and test sets contain 10K examples each
+        if split == 'train':
+            start = datetime(2000, 1, 1)
+            end = datetime(2019, 5, 1)
+        elif split == 'valid':
+            start = datetime(2019, 5, 1)
[…]

### 2019-10-13 newser/data/token_indexers/__init__.py

@@ -1,4 +1,5 @@
 from .roberta_indexer import RobertaTokenIndexer
 from .roberta_indexer_coref import RobertaCorefTokenIndexer
+from .roberta_indexer_names import RobertaNamesTokenIndexer
 from .roberta_indexer_rare import RareRobertaTokenIndexer
 from .roberta_indexer_rare_whole_words import RareWholeWordRobertaTokenIndexer

### 2019-10-13 newser/data/token_indexers/roberta_indexer_names.py

@@ -50,8 +50,8 @@ class RobertaTokenizer2(RobertaTokenizer):
         return ids
 
 
-@TokenIndexer.register("roberta_coref")
-class RobertaCorefTokenIndexer(TokenIndexer[int]):
+@TokenIndexer.register("roberta_names")
+class RobertaNamesTokenIndexer(TokenIndexer[int]):
     def __init__(self,
                  model_name: str = 'roberta-base',
                  namespace: str = 'bpe',
@@ -94,12 +94,14 @@ class RobertaCorefTokenIndexer(TokenIndexer[int]):
             self._add_encoding_to_vocabulary(vocabulary)
             self._added_to_vocabulary = True
 
+        copy_pos = copy_pos if copy_pos is not None else []
+
         text = ' '.join([token.text for token in tokens])
-        indices, copy_masks = self.encode(text, copy_pos)
+        indices, name_spans = self.encode(text, copy_pos)
 
         return {
             index_name: indices,
-            f'{index_name}_copy_masks': copy_masks,
+            f'name_spans': name_spans,
         }
 
     def encode(self, sentence, copy_pos):
@@ -119,7 +121,24 @@ class RobertaCorefTokenIndexer(TokenIndexer[int]):
             idx = self.source_dictionary.indices[word]
             token_ids.append(idx)
 
-        return token_ids, copy_masks
+        name_spans = []
+
+        start = None
+        end = None
+        is_middle = False
+
+        for i, mask in enumerate(copy_masks):
+            if mask == 1 and not is_middle:
+                start = i
+                end = i  # Note that span ends are inclusive
+                is_middle = True
+            elif mask == 1 and is_middle:
+                end = i  # Note that span ends are inclusive
+            elif mask == 0 and is_middle:
+                name_spans.append((start, end))
+                is_middle = False
+
+        return token_ids, name_spans
 
     def _byte_pair_encode(self, text, copy_pos):
         bpe_tokens = []
@@ -192,8 +211,8 @@ class RobertaCorefTokenIndexer(TokenIndexer[int]):
                          padding_lengths: Dict[str, int]) -> Dict[str, torch.Tensor]:  # pylint: disable=unused-argument
         padded_dict: Dict[str, torch.Tensor] = {}
         for key, val in tokens.items():
-            if 'copy_masks' in key:
-                def default_value(): return -1
+            if 'name_spans' in key:
+                def default_value(): return [-1, -1]
             else:
                 def default_value(): return self._padding_value
             padded_val = pad_sequence_to_length(sequence=val,

### 2019-10-13 newser/data/tokenizers/__init__.py

@@ -1,0 +1,1 @@
+from .word_splitter import JustSpacesKeepNewlinesWordSplitter

### 2019-10-13 newser/data/tokenizers/word_splitter.py

@@ -1,0 +1,21 @@
+from typing import List
+
+from allennlp.data.tokenizers.token import Token
+from allennlp.data.tokenizers.word_splitter import WordSplitter
+from overrides import overrides
+
+
+@WordSplitter.register('just_spaces_keep_newlines')
+class JustSpacesKeepNewlinesWordSplitter(WordSplitter):
+    """
+    A ``WordSplitter`` that assumes you've already done your own tokenization somehow and have
+    separated the tokens by spaces.  We just split the input string on whitespace and return the
+    resulting list.  We use a somewhat odd name here to avoid coming too close to the more
+    commonly used ``SpacyWordSplitter``.
+
+    Note that we use ``sentence.split()``, which means that the amount of whitespace between the
+    tokens does not matter.  This will never result in spaces being included as tokens.
+    """
+    @overrides
+    def split_words(self, sentence: str) -> List[Token]:
+        return [Token(t) for t in sentence.split(' ')]

### 2019-10-13 newser/models/__init__.py

@@ -1,8 +1,10 @@
 from .baseline import BaselineModel
 from .decoder_gpt2 import GPT2Decoder
 from .decoder_interact import DynamicConvInteractDecoder
+from .decoder_names import DynamicConvNameDecoder
 from .pointer import PointerModel
 from .transformer import TransformerModel
 from .transformer_flattened import TransformerFlattenedModel
+from .transformer_names import TransformerNamesModel
 from .transformer_pointer import TransformerPointerModel
 from .transformer_pointer_faster import TransformerPointerModelFaster

### 2019-10-13 newser/models/decoder_names.py

@@ -1,0 +1,627 @@
+# Copyright (c) 2017-present, Facebook, Inc.
+# All rights reserved.
+#
+# This source code is licensed under the license found in the LICENSE file in
+# the root directory of this source tree. An additional grant of patent rights
+# can be found in the PATENTS file in the same directory.
+
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.common.registrable import Registrable
+from allennlp.modules.text_field_embedders import TextFieldEmbedder
+
+from newser.modules import (AdaptiveSoftmax, DynamicConv1dTBC, GehringLinear,
+                            LightweightConv1dTBC, MultiHeadAttention)
+from newser.modules.token_embedders import AdaptiveEmbedding
+from newser.utils import eval_str_list, fill_with_neg_inf, softmax
+
+from .decoder_flattened import Decoder, DecoderLayer
+
+
+@Decoder.register('dynamic_conv_decoder_names')
+class DynamicConvNameDecoder(Decoder):
+    """
+    DynamicConv decoder consisting of *args.decoder_layers* layers. Each layer
+    is a :class:`DynamicConvDecoderLayer`.
+
+    Args:
+        args (argparse.Namespace): parsed command-line arguments
+        dictionary (~fairseq.data.Dictionary): decoding dictionary
+        embed_tokens (torch.nn.Embedding): output embedding
+        no_encoder_attn (bool, optional): whether to attend to encoder outputs.
+            Default: ``False``
+        left_pad (bool, optional): whether the input is left-padded. Default:
+            ``False``
+    """
+
+    def __init__(self, vocab, embedder: TextFieldEmbedder, max_target_positions, dropout,
+                 share_decoder_input_output_embed,
+                 decoder_output_dim, decoder_conv_dim, decoder_glu,
+                 decoder_conv_type, weight_softmax, decoder_attention_heads,
+                 weight_dropout, relu_dropout, input_dropout,
+                 decoder_normalize_before, attention_dropout, decoder_ffn_embed_dim,
+                 decoder_kernel_size_list, adaptive_softmax_cutoff=None,
+                 tie_adaptive_weights=False, adaptive_softmax_dropout=0,
+                 tie_adaptive_proj=False, adaptive_softmax_factor=0, decoder_layers=6,
+                 final_norm=True, padding_idx=0, namespace='target_tokens',
+                 vocab_size=None, section_attn=False):
+        super().__init__()
+        self.vocab = vocab
[…]

### 2019-10-13 newser/models/transformer_names.py

@@ -1,0 +1,495 @@
+import math
+import re
+import warnings
+from collections import defaultdict
+from dataclasses import dataclass
+from typing import Any, Dict, List, Optional
+
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.data.vocabulary import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import TokenEmbedder
+from allennlp.modules.seq2seq_encoders import _Seq2SeqWrapper
+from allennlp.nn.initializers import InitializerApplicator
+from allennlp.nn.util import get_text_field_mask, sort_batch_by_length
+from allennlp.training.metrics import CategoricalAccuracy
+from overrides import overrides
+from pycocoevalcap.bleu.bleu_scorer import BleuScorer
+from pycocoevalcap.rouge.rouge import Rouge
+from pytorch_transformers.modeling_roberta import RobertaModel
+from pytorch_transformers.modeling_utils import SequenceSummary
+
+from newser.modules import GehringLinear
+from newser.modules.criteria import Criterion
+from newser.modules.span_extractors import (EndpointSpanExtractorFixed,
+                                            SelfAttentiveSpanExtractorFixed)
+
+from .decoder_flattened import Decoder
+from .resnet import resnext101_32x16d_wsl
+
+LSTM = _Seq2SeqWrapper(nn.LSTM)
+
+
+def gelu(x):
+    """Implementation of the gelu activation function.
+        For information: OpenAI GPT's gelu is slightly different (and gives slightly different results):
+        0.5 * x * (1 + torch.tanh(math.sqrt(2 / math.pi)
+                   * (x + 0.044715 * torch.pow(x, 3))))
+        Also see https://arxiv.org/abs/1606.08415
+    """
+    return x * 0.5 * (1.0 + torch.erf(x / math.sqrt(2.0)))
+
+
+class Transformer(nn.Module):
+    def __init__(self, embed_dim, hidden_dim, n_embeds, n_pos, n_heads, n_layers, dropout):
+        super().__init__()
+        self.dropout = nn.Dropout(dropout)
+
+        self.attentions, self.feed_forwards = nn.ModuleList(), nn.ModuleList()
+        self.ln_1, self.ln_2 = nn.ModuleList(), nn.ModuleList()
+
+        for _ in range(n_layers):
+            self.attentions.append(nn.MultiheadAttention(
+                embed_dim, n_heads, dropout=dropout))
[…]

### 2019-10-13 newser/models/transformer_pointer_faster.py

@@ -238,12 +238,21 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
         if not torch.isnan(copy_loss):
             self.batch_history['copy_loss'] += copy_loss.item()
 
+        output_dict = {
+            'loss': loss,
+            'sample_size': caption_ids.shape[0],
+        }
+
         # During evaluation, we will generate a caption and compute BLEU, etc.
         if not self.training and self.evaluate_mode:
             log_probs, copy_probs, should_copy_probs, gen_ids = self._generate(
                 caption_ids, contexts, X_sections_hiddens, article_padding_mask, context)
             gen_texts = [self.roberta.decode(x[x > 1]) for x in gen_ids.cpu()]
             captions = [m['caption'] for m in metadata]
+
+            output_dict['captions'] = captions
+            output_dict['generations'] = gen_texts
+            output_dict['metadata'] = metadata
 
             # Remove punctuation
             gen_texts = [re.sub(r'[^\w\s]', '', t) for t in gen_texts]
@@ -258,17 +267,12 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
                 self.sample_history['bleu-3'] += score[2] * 100
                 self.sample_history['bleu-4'] += score[3] * 100
 
-                rogue_scorer = Rouge()
-                score = rogue_scorer.calc_score([gen], [ref])
-                self.sample_history['rogue'] += score * 100
+                # rogue_scorer = Rouge()
+                # score = rogue_scorer.calc_score([gen], [ref])
+                # self.sample_history['rogue'] += score * 100
 
         self.n_samples += caption_ids.shape[0]
         self.n_batches += 1
-
-        output_dict = {
-            'loss': loss,
-            'sample_size': caption_ids.shape[0],
-        }
 
         return output_dict
 

### 2019-10-13 newser/modules/__init__.py

@@ -1,3 +1,4 @@
+import newser.modules.span_extractors
 import newser.modules.token_embedders
 
 from .attention import (AttentionLayer, DownsampledMultiHeadAttention,

### 2019-10-13 newser/modules/span_extractors/__init__.py

@@ -1,0 +1,2 @@
+from .endpoint_span_extractor import EndpointSpanExtractorFixed
+from .self_attentive_span_extractors import SelfAttentiveSpanExtractorFixed

### 2019-10-13 newser/modules/span_extractors/endpoint_span_extractor.py

@@ -1,0 +1,158 @@
+
+import torch
+from allennlp.common.checks import ConfigurationError
+from allennlp.modules.span_extractors.span_extractor import SpanExtractor
+from allennlp.modules.token_embedders.embedding import Embedding
+from allennlp.nn import util
+from overrides import overrides
+from torch.nn.parameter import Parameter
+
+
+@SpanExtractor.register("endpoint_fixed")
+class EndpointSpanExtractorFixed(SpanExtractor):
+    """
+    Represents spans as a combination of the embeddings of their endpoints. Additionally,
+    the width of the spans can be embedded and concatenated on to the final combination.
+
+    The following types of representation are supported, assuming that
+    ``x = span_start_embeddings`` and ``y = span_end_embeddings``.
+
+    ``x``, ``y``, ``x*y``, ``x+y``, ``x-y``, ``x/y``, where each of those binary operations
+    is performed elementwise.  You can list as many combinations as you want, comma separated.
+    For example, you might give ``x,y,x*y`` as the ``combination`` parameter to this class.
+    The computed similarity function would then be ``[x; y; x*y]``, which can then be optionally
+    concatenated with an embedded representation of the width of the span.
+
+    Parameters
+    ----------
+    input_dim : ``int``, required.
+        The final dimension of the ``sequence_tensor``.
+    combination : str, optional (default = "x,y").
+        The method used to combine the ``start_embedding`` and ``end_embedding``
+        representations. See above for a full description.
+    num_width_embeddings : ``int``, optional (default = None).
+        Specifies the number of buckets to use when representing
+        span width features.
+    span_width_embedding_dim : ``int``, optional (default = None).
+        The embedding size for the span_width features.
+    bucket_widths : ``bool``, optional (default = False).
+        Whether to bucket the span widths into log-space buckets. If ``False``,
+        the raw span widths are used.
+    use_exclusive_start_indices : ``bool``, optional (default = ``False``).
+        If ``True``, the start indices extracted are converted to exclusive indices. Sentinels
+        are used to represent exclusive span indices for the elements in the first
+        position in the sequence (as the exclusive indices for these elements are outside
+        of the the sequence boundary) so that start indices can be exclusive.
+        NOTE: This option can be helpful to avoid the pathological case in which you
+        want span differences for length 1 spans - if you use inclusive indices, you
+        will end up with an ``x - x`` operation for length 1 spans, which is not good.
+    """
+
+    def __init__(self,
[…]

### 2019-10-13 newser/modules/span_extractors/self_attentive_span_extractors.py

@@ -1,0 +1,162 @@
+import torch
+from allennlp.modules.span_extractors.span_extractor import SpanExtractor
+from allennlp.modules.time_distributed import TimeDistributed
+from allennlp.nn import util
+from overrides import overrides
+
+
+@SpanExtractor.register("self_attentive_fixed")
+class SelfAttentiveSpanExtractorFixed(SpanExtractor):
+    """
+    Computes span representations by generating an unnormalized attention score for each
+    word in the document. Spans representations are computed with respect to these
+    scores by normalising the attention scores for words inside the span.
+
+    Given these attention distributions over every span, this module weights the
+    corresponding vector representations of the words in the span by this distribution,
+    returning a weighted representation of each span.
+
+    Key change: remove explicit float conversion
+
+    Parameters
+    ----------
+    input_dim : ``int``, required.
+        The final dimension of the ``sequence_tensor``.
+
+    Returns
+    -------
+    attended_text_embeddings : ``torch.FloatTensor``.
+        A tensor of shape (batch_size, num_spans, input_dim), which each span representation
+        is formed by locally normalising a global attention over the sequence. The only way
+        in which the attention distribution differs over different spans is in the set of words
+        over which they are normalized.
+    """
+
+    def __init__(self,
+                 input_dim: int) -> None:
+        super().__init__()
+        self._input_dim = input_dim
+        self._global_attention = TimeDistributed(torch.nn.Linear(input_dim, 1))
+
+    def get_input_dim(self) -> int:
+        return self._input_dim
+
+    def get_output_dim(self) -> int:
+        return self._input_dim
+
+    @overrides
+    def forward(self,
+                sequence_tensor: torch.FloatTensor,
+                span_indices: torch.LongTensor,
+                sequence_mask: torch.LongTensor = None,
+                span_indices_mask: torch.LongTensor = None) -> torch.FloatTensor:
+        # both of shape (batch_size, num_spans, 1)
+        span_starts, span_ends = span_indices.split(1, dim=-1)
+
+        # shape (batch_size, num_spans, 1)
+        # These span widths are off by 1, because the span ends are `inclusive`.
+        span_widths = span_ends - span_starts
+
+        # We need to know the maximum span width so we can
+        # generate indices to extract the spans from the sequence tensor.
+        # These indices will then get masked below, such that if the length
+        # of a given span is smaller than the max, the rest of the values
+        # are masked.
[…]

### 2019-10-15 scripts/compute_metrics.py
Patch meteor scorer

@@ -13,6 +13,7 @@ import json
 import os
 import pickle
 import re
+import types
 from datetime import datetime
 
 import numpy as np
@@ -29,6 +30,18 @@ from tqdm import tqdm
 from newser.utils import setup_logger
 
 logger = setup_logger()
+
+
+# Patch meteor scorer. See https://github.com/tylin/coco-caption/issues/25
+def _stat(self, hypothesis_str, reference_list):
+    # SCORE ||| reference 1 words ||| reference n words ||| hypothesis words
+    hypothesis_str = hypothesis_str.replace('|||', '').replace('  ', ' ')
+    score_line = ' ||| '.join(
+        ('SCORE', ' ||| '.join(reference_list), hypothesis_str))
+    score_line = score_line.replace('\n', '').replace('\r', '')
+    self.meteor_p.stdin.write('{}\n'.format(score_line).encode())
+    self.meteor_p.stdin.flush()
+    return self.meteor_p.stdout.readline().decode().strip()
 
 
 def validate(args):
@@ -63,6 +76,7 @@ def main():
     rouge_scores = []
     cider_scorer = CiderScorer(n=4, sigma=6.0)
     meteor_scorer = Meteor()
+    meteor_scorer._stat = types.MethodType(_stat, meteor_scorer)
     meteor_scores = []
     eval_line = 'EVAL'
     meteor_scorer.lock.acquire()

### 2019-10-15 paper/paper.tex
Update title
Add METEOR and CIDEr results
Add proper name metrics to paper

@@
 %%%%%%%%% TITLE
-\title{News Image Captioning with Transformers}
+\title{Writing News Captions with Bags of Attention}
 
@@
 	\centering
-	\begin{tabular}{llllll}
+	\begin{tabular}{llllllll}
 		\toprule
-		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE \\
+		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
 		\midrule
-      Biten \etal \cite{Biten2019GoodNews} & 8.92\% & 3.54\% & 1.60\% & 0.83\% & 12.1\% \\
-      Transformer & 19.2\% & 10.3\% & 5.40\% & 3.13\% & 21.4\% \\
+      Biten \etal \cite{Biten2019GoodNews} & 8.92\% & 3.54\% & 1.60\% & 0.83\% & 12.1\% & 4.34\% & 12.8\% \\
+      Transformer & 22.6\% & 13.7\% & 8.90\% & 6.15\% & 21.4\% & 10.3\% & 53.3\% \\
       \\
@@
 	\centering
-	\begin{tabular}{llllll}
+	\begin{tabular}{llllllll}
 		\toprule
-		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE \\
+		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
 		\midrule
-      Transformer & 15.4\% & 7.90\% & 3.93\% & 2.26\% & 19.1\% \\
-      Transformer + Surrounding Text & 16.8\% & 9.09\% & 4.55\% & 2.62\% & 20.5\% \\
+      Transformer & 17.2\% & 10.2\% & 6.55\% & 4.55\% & 19.1\% & 8.41\% & 40.4\% \\
+      Transformer (location-aware) & 18.4\% & 11.2\% & 7.35\% & 5.16\% & 20.5\% & 9.21\% & 47.6\% \\
       \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+	\caption {Proper name metrics on the NYTimes+ dataset}
+	\label{tab:results-names}
+	\centering
+	\begin{tabular}{lllllll}
+		\toprule
+        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
+        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
+		\midrule
+      Transformer & 26.2\% & 31.5\% & 19.6\% & 29.3\% & 17.2\% & 21.3\%  \\
+      Transformer (location-aware) & 30.1\% & 35.4\% & 23.6\% & 32.6\% & 22.1\% & 25.4\%   \\
 		\bottomrule

### 2019-10-15 paper/paper.tex
Add word statistics to paper

@@
 \begin{table*}[t]
-	\caption {Results on the NYTimes+ dataset}
+	\caption {Results on the NYTimes+ test set}
 	\label{tab:results-nytimes}
@@
 \begin{table*}[t]
-	\caption {Proper name metrics on the NYTimes+ dataset}
+	\caption {Proper name metrics on the NYTimes+ test set}
 	\label{tab:results-names}
@@
 
+\begin{table*}[t]
+	\caption {Word statistics on the NYTimes+ test set}
+	\label{tab:results-stats}
+	\centering
+	\begin{tabular}{lllllll}
+		\toprule
+        & Caption length  & Unique words \\
+      \midrule
+      Ground Truths & 18.4 & 17.1 \\
+      Transformer  & 12.8 & 11.5 \\
+      Transformer (location-aware) & 12.9 & 11.6  \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
 \section{Conclusion}

### 2019-10-15 newser/data/dataset_readers/nytimes_names.py
Calculate surrounding text more accurately

@@ -1,9 +1,11 @@
 import logging
 import os
 import random
+import re
 from datetime import datetime
 from typing import Dict
 
+import torch
 from allennlp.data.dataset_readers.dataset_reader import DatasetReader
 from allennlp.data.fields import MetadataField, TextField
 from allennlp.data.instance import Instance
@@ -18,6 +20,15 @@ from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
 from newser.data.fields import CorefTextField, ImageField, ListTextField
 
 logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+SPACE_NORMALIZER = re.compile(r"\s+")
+
+
+def tokenize_line(line):
+    line = SPACE_NORMALIZER.sub(" ", line)
+    line = line.strip()
+    return line.split()
 
 
 @DatasetReader.register('nytimes_names')
@@ -53,6 +64,10 @@ class NYTimesNamesReader(DatasetReader):
             ToTensor(),
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
         random.seed(1234)
+
+        roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
+        self.bpe = roberta.bpe
+        self.indices = roberta.task.source_dictionary.indices
 
     @overrides
     def _read(self, split: str):
@@ -92,7 +107,7 @@ class NYTimesNamesReader(DatasetReader):
                     paragraphs.append(title)
                     paragraph_names.append(
                         self._get_proper_names(article['headline']))
-                    n_words += len(title.split())
+                    n_words += len(self.to_token_ids(title))
 
                 caption = sections[pos]['text'].strip()
                 if not caption:
@@ -116,17 +131,17 @@ class NYTimesNamesReader(DatasetReader):
                         before.insert(0, text)
                         before_names.insert(
                             0, self._get_proper_names(sections[i]))
-                        n_words += len(text.split())
+                        n_words += len(self.to_token_ids(text))
                     i -= 1
 
                     if k < j < len(sections) and sections[j]['type'] == 'paragraph':
                         text = sections[j]['text']
                         after.append(text)
                         after_names.append(self._get_proper_names(sections[j]))
-                        n_words += len(text.split())
+                        n_words += len(self.to_token_ids(text))
                     j += 1
 
-                    if n_words > 500 or (i <= k and j >= len(sections)):
[…]

### 2019-10-15 newser/data/dataset_readers/nytimes_position.py

@@ -1,9 +1,11 @@
 import logging
 import os
 import random
+import re
 from datetime import datetime
 from typing import Dict
 
+import torch
 from allennlp.data.dataset_readers.dataset_reader import DatasetReader
 from allennlp.data.fields import MetadataField, TextField
 from allennlp.data.instance import Instance
@@ -18,6 +20,14 @@ from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
 from newser.data.fields import ImageField, ListTextField
 
 logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+SPACE_NORMALIZER = re.compile(r"\s+")
+
+
+def tokenize_line(line):
+    line = SPACE_NORMALIZER.sub(" ", line)
+    line = line.strip()
+    return line.split()
 
 
 @DatasetReader.register('nytimes_position')
@@ -54,6 +64,10 @@ class NYTimesPositionReader(DatasetReader):
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
         random.seed(1234)
 
+        roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
+        self.bpe = roberta.bpe
+        self.indices = roberta.task.source_dictionary.indices
+
     @overrides
     def _read(self, split: str):
         # split can be either train, valid, or test
@@ -89,7 +103,7 @@ class NYTimesPositionReader(DatasetReader):
                 n_words = 0
                 if title:
                     paragraphs.append(title)
-                    n_words += len(title.split())
+                    n_words += len(self.to_token_ids(title))
 
                 caption = sections[pos]['text'].strip()
                 if not caption:
@@ -108,16 +122,16 @@ class NYTimesPositionReader(DatasetReader):
                     if i > k and sections[i]['type'] == 'paragraph':
                         text = sections[i]['text']
                         before.insert(0, text)
-                        n_words += len(text.split())
+                        n_words += len(self.to_token_ids(text))
                     i -= 1
 
                     if k < j < len(sections) and sections[j]['type'] == 'paragraph':
                         text = sections[j]['text']
                         after.append(text)
-                        n_words += len(text.split())
+                        n_words += len(self.to_token_ids(text))
                     j += 1
 
-                    if n_words > 500 or (i <= k and j >= len(sections)):
+                    if n_words >= 510 or (i <= k and j >= len(sections)):
                         break
 
                 image_path = os.path.join(
[…]

### 2019-10-20 newser/models/baseline_glove.py
Generate with LSTM

@@ -284,7 +284,7 @@ class BaselineGloveModel(Model):
         return caption_ids, target_ids, contexts
 
     def _generate(self, caption_ids, contexts):
-        incremental_state: Dict[str, Any] = {}
+        # incremental_state: Dict[str, Any] = {}
         seed_input = caption_ids[:, 0:1]
         log_prob_list = []
         index_path_list = [seed_input]
@@ -295,13 +295,14 @@ class BaselineGloveModel(Model):
         B = caption_ids.shape[0]
 
         for i in range(gen_len):
-            if i == 0:
-                prev_target = {self.index: seed_input}
-            else:
-                prev_target = {self.index: seed_input[:, -1:]}
+            # if i == 0:
+            #     prev_target = {self.index: seed_input}
+            # else:
+            #     prev_target = {self.index: seed_input[:, -1:]}
+            prev_target = {self.index: seed_input}
 
-            self.decoder.filter_incremental_state(
-                incremental_state, active_idx)
+            # self.decoder.filter_incremental_state(
+            #     incremental_state, active_idx)
 
             contexts_i = {
                 'image': contexts['image'][:, full_active_idx],
@@ -315,7 +316,8 @@ class BaselineGloveModel(Model):
             decoder_out = self.decoder(
                 prev_target,
                 contexts_i,
-                incremental_state=incremental_state)
+                # incremental_state=incremental_state
+            )
 
             # We're only interested in the current final word
             decoder_out = (decoder_out[0][:, -1:], None)

### 2019-10-21 newser/data/dataset_readers/__init__.py
Train pointer generator to copy names

@@ -7,5 +7,6 @@ from .goodnews_rare import RareGoodNewsReader
 from .nytimes import NYTimesReader
 from .nytimes_faces import NYTimesFacesReader
 from .nytimes_names import NYTimesNamesReader
+from .nytimes_names_copy import NYTimesNamesCopyReader
 from .nytimes_names_faces import NYTimesNamesFacesReader
 from .nytimes_position import NYTimesPositionReader

### 2019-10-21 newser/data/dataset_readers/nytimes_names_copy.py

@@ -1,0 +1,232 @@
+import logging
+import os
+import random
+import re
+from datetime import datetime
+from typing import Dict
+
+import torch
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
+                                    ToTensor)
+
+from newser.data.fields import CorefTextField, ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+SPACE_NORMALIZER = re.compile(r"\s+")
+
+
+def tokenize_line(line):
+    line = SPACE_NORMALIZER.sub(" ", line)
+    line = line.strip()
+    return line.split()
+
+
+@DatasetReader.register('nytimes_names_copy')
+class NYTimesNamesCopyReader(DatasetReader):
+    """Read from the New York Times dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.nytimes
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        random.seed(1234)
+
+        roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
+        self.bpe = roberta.bpe
[…]

### 2019-10-21 scripts/compute_metrics.py
Handle using processed caption names

@@ -7,6 +7,7 @@ Options:
     -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
     FILE                Path to the json file.
     -c --counters PATH  Path to the word counters.
+    --use_processed     Use processed captions instead of raw captions.
 
 """
 import json
@@ -14,11 +15,9 @@ import os
 import pickle
 import re
 import types
-from datetime import datetime
 
 import numpy as np
 import ptvsd
-import spacy
 from docopt import docopt
 from pycocoevalcap.bleu.bleu_scorer import BleuScorer
 from pycocoevalcap.cider.cider_scorer import CiderScorer
@@ -52,6 +51,7 @@ def validate(args):
         'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
         'file': os.path.exists,
         'counters': Or(None, os.path.exists),
+        'use_processed': bool,
     })
     args = schema.validate(args)
     return args
@@ -94,7 +94,12 @@ def main():
     with open(args['file']) as f:
         for line in tqdm(f):
             obj = json.loads(line)
-            caption = obj['raw_caption']
+            if args['use_processed']:
+                caption = obj['caption']
+                obj['caption_names'] = obj['processed_caption_names']
+            else:
+                caption = obj['raw_caption']
+
             generation = obj['generation']
 
             if obj['caption_names']:

### 2019-10-21 scripts/goodnews_insert.py

@@ -324,7 +324,8 @@ if __name__ == '__main__':
                     'raw_caption': raw_captions[i],
                     'generation': h,
                     'image_id': i,
-                    'caption_names': get_proper_nouns(r, nlp),
+                    'caption_names': get_proper_nouns(raw_captions[i], nlp),
+                    'processed_caption_names': get_proper_nouns(r, nlp),
                     'generated_names': get_proper_nouns(h, nlp),
                 }
                 with open(dump_path, 'a') as f:

### 2019-10-21 scripts/compute_metrics.py
Save reported metrics

@@ -159,42 +159,60 @@ def main():
     meteor_scorer.lock.release()
 
     blue_score, _ = bleu_scorer.compute_score(option='closest')
-    print(f'BLEU-1: {blue_score[0]}')
-    print(f'BLEU-2: {blue_score[1]}')
-    print(f'BLEU-3: {blue_score[2]}')
-    print(f'BLEU-4: {blue_score[3]}')
-
     rouge_score = np.mean(np.array(rouge_scores))
-    print(f'ROUGE: {rouge_score}')
-
     cider_score, _ = cider_scorer.compute_score()
-    print(f'CIDEr: {cider_score}')
 
-    print(f'METEOR: {meteor_score}')
+    final_metrics = {
+        'BLEU-1': blue_score[0],
+        'BLEU-2': blue_score[1],
+        'BLEU-3': blue_score[2],
+        'BLEU-4': blue_score[3],
+        'ROUGE': rouge_score,
+        'METEOR': meteor_score,
+        'CIDEr': cider_score,
+        'All names - recall': {
+            'count': full_recall,
+            'total': full_recall_total,
+            'percentage': full_recall / full_recall_total,
+        },
+        'All names - precision': {
+            'count': full_precision,
+            'total': full_precision_total,
+            'percentage': full_precision / full_precision_total,
+        },
+        'Caption rare names - recall': {
+            'count': rare_recall,
+            'total': rare_recall_total,
+            'percentage': rare_recall / rare_recall_total,
+        },
+        'Caption rare names - precision': {
+            'count': rare_precision,
+            'total': rare_precision_total,
+            'percentage': rare_precision / rare_precision_total,
+        },
+        'Article rare names - recall': {
+            'count': full_rare_recall,
+            'total': full_rare_recall_total,
+            'percentage': full_rare_recall / full_rare_recall_total,
+        },
+        'Article rare names - precision': {
+            'count': full_rare_precision,
+            'total': full_rare_precision_total,
+            'percentage': full_rare_precision / full_rare_precision_total,
+        },
+        'Length - generation': sum(lengths) / len(lengths),
+        'Length - reference': sum(gt_lengths) / len(gt_lengths),
+        'Unique words - generation': sum(n_uniques) / len(n_uniques),
+        'Unique words - reference': sum(gt_n_uniques) / len(gt_n_uniques),
+    }
 
[…]

### 2019-10-21 scripts/compute_metrics.py
Handle division by zero

@@ -173,32 +173,32 @@ def main():
         'All names - recall': {
             'count': full_recall,
             'total': full_recall_total,
-            'percentage': full_recall / full_recall_total,
+            'percentage': (full_recall / full_recall_total) if full_recall_total else None,
         },
         'All names - precision': {
             'count': full_precision,
             'total': full_precision_total,
-            'percentage': full_precision / full_precision_total,
+            'percentage': (full_precision / full_precision_total) if full_precision_total else None,
         },
         'Caption rare names - recall': {
             'count': rare_recall,
             'total': rare_recall_total,
-            'percentage': rare_recall / rare_recall_total,
+            'percentage': (rare_recall / rare_recall_total) if rare_recall_total else None,
         },
         'Caption rare names - precision': {
             'count': rare_precision,
             'total': rare_precision_total,
-            'percentage': rare_precision / rare_precision_total,
+            'percentage': (rare_precision / rare_precision_total) if rare_precision_total else None,
         },
         'Article rare names - recall': {
             'count': full_rare_recall,
             'total': full_rare_recall_total,
-            'percentage': full_rare_recall / full_rare_recall_total,
+            'percentage': (full_rare_recall / full_rare_recall_total) if full_rare_recall_total else None,
         },
         'Article rare names - precision': {
             'count': full_rare_precision,
             'total': full_rare_precision_total,
-            'percentage': full_rare_precision / full_rare_precision_total,
+            'percentage': (full_rare_precision / full_rare_precision_total) if full_rare_precision_total else None,
         },
         'Length - generation': sum(lengths) / len(lengths),
         'Length - reference': sum(gt_lengths) / len(gt_lengths),

### 2019-10-21 scripts/compute_metrics.py
Make output filenames unique

@@ -207,7 +207,12 @@ def main():
     }
 
     serialization_dir = os.path.dirname(args['file'])
-    output_file = os.path.join(serialization_dir, 'reported_metrics.json')
+    filename = os.path.basename(args['file']).split('.')[0]
+    if args['use_processed']:
+        filename += '_processed'
+
+    output_file = os.path.join(
+        serialization_dir, f'{filename}_reported_metrics.json')
     with open(output_file, 'w') as file:
         json.dump(final_metrics, file, indent=4)
 

### 2019-10-21 newser/models/__init__.py
Train transformer with glove embeddings

@@ -11,6 +11,7 @@ from .pointer import PointerModel
 from .transformer import TransformerModel
 from .transformer_faces import TransformerFacesModel
 from .transformer_flattened import TransformerFlattenedModel
+from .transformer_glove import TransformerGloveModel
 from .transformer_names import TransformerNamesModel
 from .transformer_names_faces import TransformerNamesFacesModel
 from .transformer_pointer import TransformerPointerModel

### 2019-10-21 newser/models/decoder_flattened.py

@@ -52,7 +52,7 @@ class DynamicConvDecoder(Decoder):
                  tie_adaptive_weights=False, adaptive_softmax_dropout=0,
                  tie_adaptive_proj=False, adaptive_softmax_factor=0, decoder_layers=6,
                  final_norm=True, padding_idx=0, namespace='target_tokens',
-                 vocab_size=None, section_attn=False):
+                 vocab_size=None, section_attn=False, article_embed_size=1024):
         super().__init__()
         self.vocab = vocab
         vocab_size = vocab_size or vocab.get_vocab_size(namespace)
@@ -77,6 +77,7 @@ class DynamicConvDecoder(Decoder):
                                     decoder_conv_type, weight_softmax, decoder_attention_heads,
                                     weight_dropout, dropout, relu_dropout, input_dropout,
                                     decoder_normalize_before, attention_dropout, decoder_ffn_embed_dim,
+                                    article_embed_size,
                                     kernel_size=decoder_kernel_size_list[i])
             for i in range(decoder_layers)
         ])
@@ -464,7 +465,7 @@ class DynamicConvDecoderLayer(DecoderLayer):
                  decoder_conv_type, weight_softmax, decoder_attention_heads,
                  weight_dropout, dropout, relu_dropout, input_dropout,
                  decoder_normalize_before, attention_dropout, decoder_ffn_embed_dim,
-                 kernel_size=0):
+                 article_embed_size, kernel_size=0):
         super().__init__()
         self.embed_dim = decoder_embed_dim
         self.conv_dim = decoder_conv_dim
@@ -505,7 +506,7 @@ class DynamicConvDecoderLayer(DecoderLayer):
         self.context_attn_lns['image'] = nn.LayerNorm(self.embed_dim)
 
         self.context_attns['article'] = MultiHeadAttention(
-            self.embed_dim, decoder_attention_heads, kdim=1024, vdim=1024,
+            self.embed_dim, decoder_attention_heads, kdim=article_embed_size, vdim=article_embed_size,
             dropout=attention_dropout)
         self.context_attn_lns['article'] = nn.LayerNorm(self.embed_dim)
 

### 2019-10-21 newser/models/transformer_glove.py

@@ -1,0 +1,397 @@
+import math
+import re
+import warnings
+from collections import defaultdict
+from dataclasses import dataclass
+from typing import Any, Dict, List, Optional
+
+import numpy as np
+import spacy
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.data.vocabulary import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import TokenEmbedder
+from allennlp.modules.seq2seq_encoders import _Seq2SeqWrapper
+from allennlp.nn.initializers import InitializerApplicator
+from allennlp.nn.util import get_text_field_mask, sort_batch_by_length
+from allennlp.training.metrics import CategoricalAccuracy
+from overrides import overrides
+from pycocoevalcap.bleu.bleu_scorer import BleuScorer
+from pycocoevalcap.rouge.rouge import Rouge
+from pytorch_transformers.modeling_roberta import RobertaModel
+from pytorch_transformers.modeling_utils import SequenceSummary
+
+from newser.modules import GehringLinear
+from newser.modules.criteria import Criterion
+
+from .decoder_flattened import Decoder
+from .resnet import resnext101_32x16d_wsl
+
+LSTM = _Seq2SeqWrapper(nn.LSTM)
+
+
+def gelu(x):
+    """Implementation of the gelu activation function.
+        For information: OpenAI GPT's gelu is slightly different (and gives slightly different results):
+        0.5 * x * (1 + torch.tanh(math.sqrt(2 / math.pi)
+                   * (x + 0.044715 * torch.pow(x, 3))))
+        Also see https://arxiv.org/abs/1606.08415
+    """
+    return x * 0.5 * (1.0 + torch.erf(x / math.sqrt(2.0)))
+
+
+@Model.register("transformer_glove")
+class TransformerGloveModel(Model):
+    """
+    An AllenNLP Model that runs pretrained BERT,
+    takes the pooled output, and adds a Linear layer on top.
+    If you want an easy way to use BERT for classification, this is it.
+    Note that this is a somewhat non-AllenNLP-ish model architecture,
+    in that it essentially requires you to use the "bert-pretrained"
+    token indexer, rather than configuring whatever indexing scheme you like.
+
+    See `allennlp/tests/fixtures/bert/bert_for_classification.jsonnet`
+    for an example of what your config might look like.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
[…]

### 2019-10-21 paper/paper.tex
Add results to paper

@@
 \usepackage{graphicx}
+\usepackage{multirow} % creates cells that span multiple rows in a table
 \usepackage{amsmath}
@@
       \midrule
-      Biten \etal \cite{Biten2019GoodNews} & 8.92\% & 3.54\% & 1.60\% & 0.83\% & 12.1\% & 4.34\% & 12.8\% \\
-      Transformer & 22.6\% & 13.7\% & 8.90\% & 6.15\% & 21.4\% & 10.3\% & 53.3\% \\
-      \\
+      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04\% & 3.65\% & 1.71\% & 0.89\% & 12.2\% & 4.37\% & 13.1\% \\
+      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10\% & 3.33\% & 1.60\% & 0.85\% & 11.9\% & 4.23\% & 12.8\% \\
+      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44\% & 3.42\% & 1.62\% & 0.87\% & 12.2\% & 4.30\% & 13.1\% \\
+      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68\% & 3.47\% & 1.58\% & 0.82\% & 12.1\% & 4.23\% & 12.6\% \\
+      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74\% & 3.15\% & 1.45\% & 0.75\% & 11.9\% & 4.10\% & 12.5\% \\
+      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10\% & 3.26\% & 1.48\% & 0.76\% & 12.2\% & 4.17\% & 12.7\% \\
+      \midrule
+      LSTM + GloVe & 13.6\% & 6.19\% & 3.13\% & 1.81\% & 13.5\% & 5.26\% & 11.9\% \\
+      LSTM + RoBERTa &  &  &  &  &  &  &  \\
+      Transformer + GloVe &  &  &  &  &  &  &  \\
+      Transformer + RoBERTa & 22.7\% & 13.7\% & 8.93\% & 6.17\% & 21.4\% & 10.3\% & 53.9\% \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+   \caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
+   since train-test split were created using a random shuffle.}
+	\label{tab:results-names}
+	\centering
+	\begin{tabular}{lll}
+		\toprule
+        & \multicolumn{2}{c}{All names}  \\
+        & Recall  & Precision \\
+      \midrule
+      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% \\
+      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
+      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
+      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
+      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
+      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% \\
+      \midrule
+      LSTM + GloVe & 10.1\% & 14.9\%  \\
+      LSTM + RoBERTa &  &   \\
+      Transformer + GloVe & &  \\
+      Transformer + RoBERTa & 29.8\% & 34.4\%  \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+	\caption {Word statistics on the GoodNews test set}
+	\label{tab:results-stats}
+	\centering
+	\begin{tabular}{lllllll}
+		\toprule
+        & Caption length  & Unique words \\
+      \midrule
+      Ground Truths & 18.1 & 17.0 \\
+      Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
+      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
+      Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
+      Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
+      Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
+      Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
+      \midrule
+      LSTM + GloVe & 13.9 & 11.4 \\
+      LSTM + RoBERTa &  &  \\
+      Transformer + GloVe & &  \\
+      Transformer + RoBERTa & 15.7 & 13.8 \\
 		\bottomrule
@@
 		\midrule
-      Transformer & 17.2\% & 10.2\% & 6.55\% & 4.55\% & 19.1\% & 8.41\% & 40.4\% \\
-      Transformer (location-aware) & 18.4\% & 11.2\% & 7.35\% & 5.16\% & 20.5\% & 9.21\% & 47.6\% \\
+      Transformer (first 512 tokens) & 17.6\% & 10.4\% & 6.68\% & 4.65\% & 19.1\% & 8.49\% & 41.1\% \\
+      Transformer (location-aware) & 19.0\% & 11.7\% & 7.76\% & 5.48\% & 21.1\% & 9.51\% & 51.4\% \\
       \\
@@
 		\midrule
-      Transformer & 26.2\% & 31.5\% & 19.6\% & 29.3\% & 17.2\% & 21.3\%  \\
-      Transformer (location-aware) & 30.1\% & 35.4\% & 23.6\% & 32.6\% & 22.1\% & 25.4\%   \\
+      Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
+      Transformer (location-aware) & 31.5\% & 36.8\% & 25.3\% & 33.2\% & 23.5\% & 25.3\%   \\
 		\bottomrule
@@
       Ground Truths & 18.4 & 17.1 \\
-      Transformer  & 12.8 & 11.5 \\
-      Transformer (location-aware) & 12.9 & 11.6  \\
+      Transformer (first 512 tokens)  & 13.1 & 11.7 \\
+      Transformer (location-aware) & 13.0 & 11.7  \\
 		\bottomrule

### 2019-10-21 newser/commands/evaluate.py
Copy rare names

@@ -135,9 +135,9 @@ def evaluate(model: Model,
         final_metrics = model.get_metrics(reset=True)
         if loss_count > 0:
             # Sanity check
-            if loss_count != batch_count:
-                raise RuntimeError("The model you are trying to evaluate only sometimes " +
-                                   "produced a loss!")
+            # if loss_count != batch_count:
+            #     raise RuntimeError("The model you are trying to evaluate only sometimes " +
+            #                        "produced a loss!")
             final_metrics["loss"] = total_loss / total_weight
 
         return final_metrics
@@ -153,7 +153,9 @@ def write_to_json(output_dict, serialization_dir, nlp):
 
     out_path = os.path.join(serialization_dir, 'generations.jsonl')
     with open(out_path, 'a') as f:
-        for caption, generation, m in zip(captions, generations, metadatas):
+        for i, caption in enumerate(captions):
+            m = metadatas[i]
+            generation = generations[i]
             obj = {
                 'caption': caption,
                 'raw_caption': m['caption'],
@@ -164,6 +166,10 @@ def write_to_json(output_dict, serialization_dir, nlp):
                 'caption_names': get_proper_nouns(m['caption'], nlp),
                 'generated_names': get_proper_nouns(generation, nlp),
             }
+
+            if 'copied_texts' in output_dict:
+                obj['copied_text'] = output_dict['copied_texts'][i]
+
             f.write(f'{json.dumps(obj)}\n')
 
 

### 2019-10-21 newser/data/dataset_readers/nytimes_names_copy.py

@@ -1,5 +1,6 @@
 import logging
 import os
+import pickle
 import random
 import re
 from datetime import datetime
@@ -51,6 +52,8 @@ class NYTimesNamesCopyReader(DatasetReader):
                  tokenizer: Tokenizer,
                  token_indexers: Dict[str, TokenIndexer],
                  image_dir: str,
+                 name_counters_path: str = None,
+                 threshold: int = 10,
                  mongo_host: str = 'localhost',
                  mongo_port: int = 27017,
                  lazy: bool = True) -> None:
@@ -68,6 +71,15 @@ class NYTimesNamesCopyReader(DatasetReader):
         roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
         self.bpe = roberta.bpe
         self.indices = roberta.task.source_dictionary.indices
+
+        if name_counters_path is not None:
+            with open(name_counters_path, 'rb') as f:
+                counters = pickle.load(f)
+                counter = counters['context'] + counters['caption']
+                self.rare_names = set([w for w in counter
+                                       if counter[w] < threshold])
+        else:
+            self.rare_names = None
 
     @overrides
     def _read(self, split: str):
@@ -200,9 +212,10 @@ class NYTimesNamesCopyReader(DatasetReader):
         parts_of_speech = section['parts_of_speech']
         for pos in parts_of_speech:
             if pos['pos'] == 'PROPN' and not is_middle:
-                start = pos['start']
-                end = pos['end']
-                is_middle = True
+                if not self.rare_names or pos['text'] in self.rare_names:
+                    start = pos['start']
+                    end = pos['end']
+                    is_middle = True
             elif pos['pos'] == 'PROPN' and is_middle:
                 end = pos['end']
             elif pos['pos'] != 'PROPN' and is_middle:

### 2019-10-21 newser/models/transformer_pointer_faster.py

@@ -245,14 +245,18 @@ class TransformerPointerModelFaster(LoadStateDictWithPrefix, Model):
 
         # During evaluation, we will generate a caption and compute BLEU, etc.
         if not self.training and self.evaluate_mode:
-            log_probs, copy_probs, should_copy_probs, gen_ids = self._generate(
+            log_probs, copy_probs, should_copy_mask, gen_ids = self._generate(
                 caption_ids, contexts, X_sections_hiddens, article_padding_mask, context)
             gen_texts = [self.roberta.decode(x[x > 1]) for x in gen_ids.cpu()]
             captions = [m['caption'] for m in metadata]
 
+            copied_texts = [self.roberta.decode(x[should_copy_mask[i]])
+                            for i, x in enumerate(gen_ids.cpu())]
+
             output_dict['captions'] = captions
             output_dict['generations'] = gen_texts
             output_dict['metadata'] = metadata
+            output_dict['copied_texts'] = copied_texts
 
             # Remove punctuation
             gen_texts = [re.sub(r'[^\w\s]', '', t) for t in gen_texts]

### 2019-10-21 newser/commands/evaluate.py
Assert generation file doesn't exist

@@ -82,6 +82,8 @@ def evaluate(model: Model,
              batch_weight_key: str) -> Dict[str, Any]:
     check_for_gpu(cuda_device)
     nlp = spacy.load("en_core_web_lg", disable=['parser', 'ner'])
+    assert not os.path.exists(os.path.join(
+        serialization_dir, 'generations.jsonl'))
     with torch.no_grad():
         model.eval()
 

### 2019-10-21 paper/paper.tex
Add more citations

@@
 \begin{abstract}
-   In this work, we present an end-to-end captioning system for news articles
-   that can handle entity names and out-of-vocabulary words. Our model achieves
-   state-of-the-art results on the existing ``GoodNews" dataset. We also
-   re-collected news articles from the New York Times, which are cleaner and
-   more complete. This dataset allows us to explore approaches involving
-   image positions. The code will be made available on GitHub.
+   We propose an end-to-end model to generate image captions in news articles.
+   By combining the transformer architecture, byte-pair encoding, pretrained
+   text and image embeddings, and bags of attentions, our system is able to
+   describe an image using specific events and names mentioned in the article.
+   Our model achieves state-of-the-art results on the existing GoodNews
+   dataset. We also extend the GoodNews dataset to improve the quality of
+   articles and study the importance of the image location on the page.
 \end{abstract}
@@
 \begin{itemize}
-   \item We show that combining article attention with pre-trained contextualized
-   word piece embeddings allows our model to generate captions containing
-   relevant words that were not seen during training.
+   \item We show that combining article attention with pre-trained
+   contextualized word piece embeddings allows our model to generate captions
+   containing relevant words that were not seen during training.
 
@@
 
-   \item We build on the “Good News” dataset to produce a larger and more complete
-   news captioning dataset consisting of * articles from the New York Times and
-   their 794K images with captions. In contrast to “Good News” our dataset
-   contains the full article text, and the location of the image within the
-   page.
+   \item We build on the GoodNews dataset to produce a larger and more
+   complete news captioning dataset consisting of 445,828 articles from the New
+   York Times and their 794K images with captions. In contrast to GoodNews
+   our dataset contains the full article text, and the location of the image
+   within the page.
 \end{itemize}
@@
 
+We use MTCNN \cite{Zhang2016JointFD} to detect faces and FaceNet
+\cite{Schroff2015FaceNetAU} trained on the VGGFace2 dataset
+\cite{Cao2017VGGFace2AD}
+to classify the faces.
+
 \begin{figure*}[t]
@@
 
-\section{Results}
+\section{Experiments}
+
+The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
+the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
+dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
+will made public on GitHub.
 
@@
       Ground Truths & 18.1 & 17.0 \\
+      \midrule
       Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\

### 2019-10-21 newser/models/__init__.py
Train with parallel attention over faces

@@ -1,6 +1,7 @@
 from .baseline import BaselineModel
 from .baseline_glove import BaselineGloveModel
 from .decoder_faces import DynamicConvFacesDecoder
+from .decoder_faces_parallel import DynamicConvFacesParallelDecoder
 from .decoder_flattened_lstm import LSTMDecoder
 from .decoder_gpt2 import GPT2Decoder
 from .decoder_interact import DynamicConvInteractDecoder

### 2019-10-21 newser/models/decoder_faces_parallel.py

@@ -1,0 +1,629 @@
+# Copyright (c) 2017-present, Facebook, Inc.
+# All rights reserved.
+#
+# This source code is licensed under the license found in the LICENSE file in
+# the root directory of this source tree. An additional grant of patent rights
+# can be found in the PATENTS file in the same directory.
+
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.common.registrable import Registrable
+from allennlp.modules.text_field_embedders import TextFieldEmbedder
+
+from newser.modules import (AdaptiveSoftmax, DynamicConv1dTBC, GehringLinear,
+                            LightweightConv1dTBC, MultiHeadAttention)
+from newser.modules.token_embedders import AdaptiveEmbedding
+from newser.utils import eval_str_list, fill_with_neg_inf, softmax
+
+from .decoder_flattened import Decoder, DecoderLayer
+
+
+@Decoder.register('dynamic_conv_decoder_faces_parallel')
+class DynamicConvFacesParallelDecoder(Decoder):
+    """
+    DynamicConv decoder consisting of *args.decoder_layers* layers. Each layer
+    is a :class:`DynamicConvDecoderLayer`.
+
+    Args:
+        args (argparse.Namespace): parsed command-line arguments
+        dictionary (~fairseq.data.Dictionary): decoding dictionary
+        embed_tokens (torch.nn.Embedding): output embedding
+        no_encoder_attn (bool, optional): whether to attend to encoder outputs.
+            Default: ``False``
+        left_pad (bool, optional): whether the input is left-padded. Default:
+            ``False``
+    """
+
+    def __init__(self, vocab, embedder: TextFieldEmbedder, max_target_positions, dropout,
+                 share_decoder_input_output_embed,
+                 decoder_output_dim, decoder_conv_dim, decoder_glu,
+                 decoder_conv_type, weight_softmax, decoder_attention_heads,
+                 weight_dropout, relu_dropout, input_dropout,
+                 decoder_normalize_before, attention_dropout, decoder_ffn_embed_dim,
+                 decoder_kernel_size_list, adaptive_softmax_cutoff=None,
+                 tie_adaptive_weights=False, adaptive_softmax_dropout=0,
+                 tie_adaptive_proj=False, adaptive_softmax_factor=0, decoder_layers=6,
+                 final_norm=True, padding_idx=0, namespace='target_tokens',
+                 vocab_size=None, section_attn=False, swap=False):
+        super().__init__()
+        self.vocab = vocab
[…]

### 2019-10-22 paper/paper.tex
Add works on transformer captioning

@@
 
+Zhu \etal \cite{Zhu2018CaptioningTW} used transformers to achieve competitive
+results on the MSCOCO dataset. Li \etal \cite{Li2019Boosted} added attention
+over image regions and semantic concepts using Faster-RCNN
+\cite{Ren2015FasterRCNN}. Both of these works, however, used the MSCOCO dataset
+which contains generic captions with no named entities.
+
 \begin{figure}[t]
@@
 This motivates us to recollect data from the New York Times in a more careful
-manner. We call this NYTimes+.
+manner, using our own parser. We call this NYTimes+.
 

### 2019-10-22 newser/data/dataset_readers/nytimes_faces.py
Keep only the top 8 faces

@@ -151,7 +151,8 @@ class NYTimesFacesReader(DatasetReader):
                     face_embeds = sections[pos]['facenet']['embeddings']
                 else:
                     face_embeds = [[]]
-                face_embeds = np.array(face_embeds)
+                # Keep only the top 8 faces (sorted by detection probabilities)
+                face_embeds = np.array(face_embeds[:8])
 
                 paragraphs = paragraphs + before + after
 

### 2019-10-22 scripts/detect_facenet.py
Process high quality faces

@@ -5,7 +5,7 @@ Usage:
 
 Options:
     -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
-    -d --image-dir DIR  Image directory [default: ./data/nytimes/images_processed].
+    -d --image-dir DIR  Image directory [default: ./data/nytimes/images].
     -f --face-dir DIR   Image directory [default: ./data/nytimes/facenet].
     -b --batch INT      Batch number [default: 1]
     -h --host HOST      Mongo host name [default: localhost]
@@ -45,12 +45,12 @@ def validate(args):
 
 
 def detect_faces(article, nytimes, image_dir, face_dir, mtcnn, resnet):
-    if 'facenet_positions' in article:
+    if 'detected_face_positions' in article:
         return
 
     sections = article['parsed_section']
     image_positions = article['image_positions']
-    article['facenet_positions'] = []
+    article['detected_face_positions'] = []
 
     for pos in image_positions:
         section = sections[pos]
@@ -60,7 +60,13 @@ def detect_faces(article, nytimes, image_dir, face_dir, mtcnn, resnet):
                            f"{article['_id']} at position {pos}")
             continue
 
-        img = Image.open(image_path)
+        try:
+            img = Image.open(image_path)
+            img = img.convert('RGB')
+        except OSError:
+            logger.warning(f"OSError on image: {image_path} from article "
+                           f"{article['_id']} at position {pos}")
+            continue
         face_path = os.path.join(face_dir, f"{section['hash']}_{pos:02}.jpg")
         with torch.no_grad():
             try:
@@ -74,16 +80,16 @@ def detect_faces(article, nytimes, image_dir, face_dir, mtcnn, resnet):
                 continue
             embeddings, face_probs = resnet(faces)
 
-        section['facenet'] = {
-            'n_faces': len(faces),
-            'embeddings': embeddings.cpu().tolist(),
-            'detect_probs': probs.tolist(),
-            'face_probs': face_probs.cpu().tolist(),
+        section['facenet_details'] = {
+            'n_faces': len(faces[:10]),
+            'embeddings': embeddings.cpu().tolist()[:10],
+            'detect_probs': probs.tolist()[:10],
[…]

### 2019-10-22 scripts/detect_facenet_goodnews.py

@@ -5,7 +5,7 @@ Usage:
 
 Options:
     -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
-    -d --image-dir DIR  Image directory [default: ./data/goodnews/images_processed].
+    -d --image-dir DIR  Image directory [default: ./data/goodnews/images].
     -f --face-dir DIR   Image directory [default: ./data/goodnews/facenet].
     -h --host HOST      Mongo host name [default: localhost]
 
@@ -42,12 +42,13 @@ def validate(args):
 
 
 def detect_faces(sample, goodnews, image_dir, face_dir, mtcnn, resnet):
-    if 'facenet' in sample:
+    if 'facenet_details' in sample:
         return
 
     image_path = os.path.join(image_dir, f"{sample['_id']}.jpg")
     try:
         image = Image.open(image_path)
+        image = image.convert('RGB')
     except (FileNotFoundError, OSError):
         return
 
@@ -64,11 +65,12 @@ def detect_faces(sample, goodnews, image_dir, face_dir, mtcnn, resnet):
             return
         embeddings, face_probs = resnet(faces)
 
-    sample['facenet'] = {
-        'n_faces': len(faces),
-        'embeddings': embeddings.cpu().tolist(),
-        'detect_probs': probs.tolist(),
-        'face_probs': face_probs.cpu().tolist(),
+    # We keep only top 10 faces
+    sample['facenet_details'] = {
+        'n_faces': len(faces[:10]),
+        'embeddings': embeddings.cpu().tolist()[:10],
+        'detect_probs': probs.tolist()[:10],
+        'face_probs': face_probs.cpu().tolist()[:10],
     }
 
     try:

### 2019-10-22 scripts/annotate_goodnews_ner.py
Annotate named entities

@@ -1,0 +1,87 @@
+"""Annotate Good News with parts of speech.
+
+Usage:
+    annotate_goodnews_ner.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      MongoDB host [default: localhost].
+
+"""
+
+import ptvsd
+import spacy
+from docopt import docopt
+from pymongo import MongoClient
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str,
+    })
+    args = schema.validate(args)
+    return args
+
+
+def main():
+    args = docopt(__doc__, version='0.0.1')
+    args = validate(args)
+
+    if args['ptvsd']:
+        address = ('0.0.0.0', args['ptvsd'])
+        ptvsd.enable_attach(address)
+        ptvsd.wait_for_attach()
+
+    logger.info('Loading spacy.')
+    nlp = spacy.load("en_core_web_lg")
+    client = MongoClient(host=args['host'], port=27017)
+    db = client.goodnews
+
+    sample_cursor = db.splits.find({}, no_cursor_timeout=True).batch_size(128)
+
+    done_article_ids = set()
+    for sample in tqdm(sample_cursor):
+        if sample['article_id'] in done_article_ids:
+            continue
+        done_article_ids.add(sample['article_id'])
+
+        article = db.articles.find_one({
+            '_id': {'$eq': sample['article_id']},
+        })
+
+        article['caption_ner'] = {}
+        for idx, caption in article['images'].items():
+            caption = caption.strip()
+            caption_doc = nlp(caption)
+            get_caption_ner(caption_doc, article, idx)
+
+        db.articles.find_one_and_update(
+            {'_id': article['_id']}, {'$set': article})
+
+
+def get_caption_ner(doc, article, idx):
+    ner = []
+    for ent in doc.ents:
+        ent_info = {
+            'start': ent.start_char,
+            'end': ent.end_char,
+            'text': ent.text,
+            'label': ent.label_,
+        }
[…]

### 2019-10-22 scripts/annotate_nytimes_ner.py

@@ -1,0 +1,87 @@
+"""Get articles from the New York Times API.
+
+Usage:
+    annotate_nytimes_ner.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      MongoDB host [default: localhost].
+
+"""
+
+import ptvsd
+import spacy
+from docopt import docopt
+from joblib import Parallel, delayed
+from pymongo import MongoClient
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str,
+    })
+    args = schema.validate(args)
+    return args
+
+
+def parse_article(article, nlp, db):
+    sections = article['parsed_section']
+    changed = False
+
+    for section in sections:
+        if section['type'] == 'caption':
+            doc = nlp(section['text'].strip())
+            section['named_entities'] = []
+            for ent in doc.ents:
+                changed = True
+                ent_info = {
+                    'start': ent.start_char,
+                    'end': ent.end_char,
+                    'text': ent.text,
+                    'label': ent.label_,
+                }
+                section['named_entities'].append(ent_info)
+
+    if changed:
+        db.articles.find_one_and_update(
+            {'_id': article['_id']}, {'$set': article})
+
+
+def main():
+    args = docopt(__doc__, version='0.0.1')
+    args = validate(args)
+
+    if args['ptvsd']:
+        address = ('0.0.0.0', args['ptvsd'])
+        ptvsd.enable_attach(address)
+        ptvsd.wait_for_attach()
+
+    logger.info('Loading spacy.')
+    nlp = spacy.load("en_core_web_lg")
+    client = MongoClient(host=args['host'], port=27017)
+    db = client.nytimes
+
+    article_cursor = db.articles.find({
+        'parsed': True,  # article body is parsed into paragraphs
+        'n_images': {'$gt': 0},  # at least one image is present
+        'language': 'en',
+    }, no_cursor_timeout=True).batch_size(128)
+
+    logger.info('Annotating articles.')
[…]

### 2019-10-22 newser/data/dataset_readers/__init__.py
Attend over unique proper names

@@ -9,4 +9,5 @@ from .nytimes_faces import NYTimesFacesReader
 from .nytimes_names import NYTimesNamesReader
 from .nytimes_names_copy import NYTimesNamesCopyReader
 from .nytimes_names_faces import NYTimesNamesFacesReader
+from .nytimes_names_set import NYTimesNamesSetReader
 from .nytimes_position import NYTimesPositionReader

### 2019-10-22 newser/data/dataset_readers/nytimes_names_set.py

@@ -1,0 +1,213 @@
+import logging
+import os
+import random
+import re
+from datetime import datetime
+from typing import Dict
+
+import torch
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
+                                    ToTensor)
+
+from newser.data.fields import CorefTextField, ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+SPACE_NORMALIZER = re.compile(r"\s+")
+
+
+def tokenize_line(line):
+    line = SPACE_NORMALIZER.sub(" ", line)
+    line = line.strip()
+    return line.split()
+
+
+@DatasetReader.register('nytimes_names_set')
+class NYTimesNamesSetReader(DatasetReader):
+    """Read from the New York Times dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.nytimes
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        random.seed(1234)
+
+        roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
+        self.bpe = roberta.bpe
[…]

### 2019-10-22 newser/models/__init__.py

@@ -15,5 +15,6 @@ from .transformer_flattened import TransformerFlattenedModel
 from .transformer_glove import TransformerGloveModel
 from .transformer_names import TransformerNamesModel
 from .transformer_names_faces import TransformerNamesFacesModel
+from .transformer_names_set import TransformerNamesSetModel
 from .transformer_pointer import TransformerPointerModel
 from .transformer_pointer_faster import TransformerPointerModelFaster

### 2019-10-22 newser/models/decoder_names.py

@@ -508,6 +508,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
             dropout=attention_dropout)
         self.context_attn_lns['names'] = nn.LayerNorm(self.embed_dim)
 
+        context_size = self.embed_dim * 3
+        self.context_fc = GehringLinear(context_size, self.embed_dim)
+
         self.fc1 = GehringLinear(self.embed_dim, decoder_ffn_embed_dim)
         self.fc2 = GehringLinear(decoder_ffn_embed_dim, self.embed_dim)
 
@@ -537,6 +540,7 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X = self.maybe_layer_norm(self.conv_layer_norm, X, after=True)
 
         attn = None
+        X_contexts = []
 
         # Image attention
         residual = X
@@ -552,8 +556,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
             need_weights=(not self.training and self.need_attn))
         X_image = F.dropout(X_image, p=self.dropout, training=self.training)
         X_image = residual + X_image
-        X = self.maybe_layer_norm(
+        X_image = self.maybe_layer_norm(
             self.context_attn_lns['image'], X_image, after=True)
+        X_contexts.append(X_image)
 
         # Article attention
         residual = X
@@ -570,8 +575,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X_article = F.dropout(X_article, p=self.dropout,
                               training=self.training)
         X_article = residual + X_article
-        X = self.maybe_layer_norm(
+        X_article = self.maybe_layer_norm(
             self.context_attn_lns['article'], X_article, after=True)
+        X_contexts.append(X_article)
 
         # Name attention
         residual = X
@@ -588,8 +594,12 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X_names = F.dropout(X_names, p=self.dropout,
                             training=self.training)
         X_names = residual + X_names
-        X = self.maybe_layer_norm(
+        X_names = self.maybe_layer_norm(
             self.context_attn_lns['article'], X_names, after=True)
+        X_contexts.append(X_names)
+
+        X_context = torch.cat(X_contexts, dim=-1)
+        X = self.context_fc(X_context)
 
         residual = X
         X = self.maybe_layer_norm(self.final_layer_norm, X, before=True)

### 2019-10-22 newser/models/transformer_names_set.py

@@ -1,0 +1,418 @@
+import math
+import re
+import warnings
+from collections import defaultdict
+from dataclasses import dataclass
+from typing import Any, Dict, List, Optional
+
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.data.vocabulary import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import TokenEmbedder
+from allennlp.modules.seq2seq_encoders import _Seq2SeqWrapper
+from allennlp.nn.initializers import InitializerApplicator
+from allennlp.nn.util import get_text_field_mask, sort_batch_by_length
+from allennlp.training.metrics import CategoricalAccuracy
+from overrides import overrides
+from pycocoevalcap.bleu.bleu_scorer import BleuScorer
+from pycocoevalcap.rouge.rouge import Rouge
+from pytorch_transformers.modeling_roberta import RobertaModel
+from pytorch_transformers.modeling_utils import SequenceSummary
+
+from newser.modules import GehringLinear
+from newser.modules.criteria import Criterion
+
+from .decoder_flattened import Decoder
+from .resnet import resnext101_32x16d_wsl
+
+LSTM = _Seq2SeqWrapper(nn.LSTM)
+
+
+def gelu(x):
+    """Implementation of the gelu activation function.
+        For information: OpenAI GPT's gelu is slightly different (and gives slightly different results):
+        0.5 * x * (1 + torch.tanh(math.sqrt(2 / math.pi)
+                   * (x + 0.044715 * torch.pow(x, 3))))
+        Also see https://arxiv.org/abs/1606.08415
+    """
+    return x * 0.5 * (1.0 + torch.erf(x / math.sqrt(2.0)))
+
+
+@Model.register("transformer_names_set")
+class TransformerNamesSetModel(Model):
+    """
+    An AllenNLP Model that runs pretrained BERT,
+    takes the pooled output, and adds a Linear layer on top.
+    If you want an easy way to use BERT for classification, this is it.
+    Note that this is a somewhat non-AllenNLP-ish model architecture,
+    in that it essentially requires you to use the "bert-pretrained"
+    token indexer, rather than configuring whatever indexing scheme you like.
+
+    See `allennlp/tests/fixtures/bert/bert_for_classification.jsonnet`
+    for an example of what your config might look like.
+
+    Parameters
+    ----------
+    vocab : ``Vocabulary``
[…]

### 2019-10-23 newser/models/transformer_flattened.py
Fix generation with LSTM

@@ -26,6 +26,7 @@ from newser.modules import GehringLinear
 from newser.modules.criteria import Criterion
 
 from .decoder_flattened import Decoder
+from .decoder_flattened_lstm import LSTMDecoder
 from .resnet import resnext101_32x16d_wsl
 
 LSTM = _Seq2SeqWrapper(nn.LSTM)
@@ -195,7 +196,10 @@ class TransformerFlattenedModel(Model):
 
         # During evaluation, we will generate a caption and compute BLEU, etc.
         if not self.training and self.evaluate_mode:
-            _, gen_ids = self._generate(caption_ids, contexts)
+            if isinstance(self.decoder, LSTMDecoder):
+                _, gen_ids = self._generate_full(caption_ids, contexts)
+            else:
+                _, gen_ids = self._generate(caption_ids, contexts)
             # We ignore <s> and <pad>
             gen_texts = [self.roberta.decode(x[x > 1]) for x in gen_ids.cpu()]
             captions = [m['caption'] for m in metadata]
@@ -372,6 +376,98 @@ class TransformerFlattenedModel(Model):
                 prev_target,
                 contexts_i,
                 incremental_state=incremental_state)
+
+            # We're only interested in the current final word
+            decoder_out = (decoder_out[0][:, -1:], None)
+
+            lprobs = self.decoder.get_normalized_probs(
+                decoder_out, log_probs=True)
+            # lprobs.shape == [batch_size, 1, vocab_size]
+
+            lprobs = lprobs.squeeze(1)
+            # lprobs.shape == [batch_size, vocab_size]
+
+            topk_lprobs, topk_indices = lprobs.topk(self.sampling_topk)
+            topk_lprobs = topk_lprobs.div_(self.sampling_temp)
+            # topk_lprobs.shape == [batch_size, topk]
+
+            # Take a random sample from those top k
+            topk_probs = topk_lprobs.exp()
+            sampled_index = torch.multinomial(topk_probs, num_samples=1)
+            # sampled_index.shape == [batch_size, 1]
+
+            selected_lprob = topk_lprobs.gather(
+                dim=-1, index=sampled_index)
+            # selected_prob.shape == [batch_size, 1]
+
+            selected_index = topk_indices.gather(
+                dim=-1, index=sampled_index)
+            # selected_index.shape == [batch_size, 1]
+
+            log_prob = selected_lprob.new_zeros(B, 1)
+            log_prob[full_active_idx] = selected_lprob
[…]

### 2019-10-23 scripts/compute_ner_statistics_nytimes.py
Compute NER statistics for NYTimes+

@@ -1,0 +1,99 @@
+"""Get articles from the New York Times API.
+
+Usage:
+    compute_ner_statistics_nytimes.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      MongoDB host [default: localhost].
+
+"""
+import pickle
+from collections import Counter
+from datetime import datetime
+
+import ptvsd
+from docopt import docopt
+from pymongo import MongoClient
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str
+    })
+    args = schema.validate(args)
+    return args
+
+
+def main():
+    args = docopt(__doc__, version='0.0.1')
+    args = validate(args)
+
+    if args['ptvsd']:
+        address = ('0.0.0.0', args['ptvsd'])
+        ptvsd.enable_attach(address)
+        ptvsd.wait_for_attach()
+
+    client = MongoClient(host=args['host'], port=27017)
+    nytimes = client.nytimes
+
+    start = datetime(2000, 1, 1)
+    end = datetime(2019, 5, 1)
+
+    type_counter = Counter()
+    noun_counter = Counter()
+
+    article_cursor = nytimes.articles.find({
+        'parsed': True,  # article body is parsed into paragraphs
+        'n_images': {'$gt': 0},  # at least one image is present
+        'pub_date': {'$gte': start, '$lt': end},
+        'language': 'en',
+    }, no_cursor_timeout=True, projection=['parsed_section']).batch_size(128)
+
+    for article in tqdm(article_cursor):
+        sections = article['parsed_section']
+        for section in sections:
+            if section['type'] == 'caption':
+                get_ner_statistics(section, type_counter, noun_counter)
+
+    counters = {
+        'type': type_counter,
+        'noun': noun_counter,
+    }
+    with open('./data/nytimes/ner_noun_counters.pkl', 'wb') as f:
+        pickle.dump(counters, f)
+
+
+def get_ner_statistics(section, type_counter, noun_counter):
+    entity_locs = []
+    if 'named_entities' in section:
[…]

### 2019-10-23 paper/paper.tex
Add paper on hierarchical attention network
Add Good News baseline results

@@
 which contains generic captions with no named entities.
+
+Wang \etal \cite{Wang2019Hierarchical} examined different strategies of
+combining embeddings from three modalities: concept terms, object regions,
+and image patches. These strategies include addition, concatenation, and
+multivariate residual modules.
 
@@
       \midrule
-      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04\% & 3.65\% & 1.71\% & 0.89\% & 12.2\% & 4.37\% & 13.1\% \\
-      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10\% & 3.33\% & 1.60\% & 0.85\% & 11.9\% & 4.23\% & 12.8\% \\
-      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44\% & 3.42\% & 1.62\% & 0.87\% & 12.2\% & 4.30\% & 13.1\% \\
-      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68\% & 3.47\% & 1.58\% & 0.82\% & 12.1\% & 4.23\% & 12.6\% \\
-      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74\% & 3.15\% & 1.45\% & 0.75\% & 11.9\% & 4.10\% & 12.5\% \\
-      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10\% & 3.26\% & 1.48\% & 0.76\% & 12.2\% & 4.17\% & 12.7\% \\
+      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
+      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
+      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
+      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
+      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
+      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
       \midrule
-      LSTM + GloVe & 13.6\% & 6.19\% & 3.13\% & 1.81\% & 13.5\% & 5.26\% & 11.9\% \\
-      LSTM + RoBERTa &  &  &  &  &  &  &  \\
-      Transformer + GloVe &  &  &  &  &  &  &  \\
-      Transformer + RoBERTa & 22.7\% & 13.7\% & 8.93\% & 6.17\% & 21.4\% & 10.3\% & 53.9\% \\
+      GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
+      GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
+      RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
+      RoBERTa + Transformer & 22.7 & 13.7 & 8.93 & 6.17 & 21.4 & 10.3 & 53.9 \\
 		\bottomrule
@@
       \midrule
-      LSTM + GloVe & 10.1\% & 14.9\%  \\
-      LSTM + RoBERTa &  &   \\
-      Transformer + GloVe & &  \\
-      Transformer + RoBERTa & 29.8\% & 34.4\%  \\
+      GloVe + LSTM & 10.1\% & 14.9\%  \\
+      GloVe + Transformer & 16.6\% & 21.7\% \\
+      RoBERTa + LSTM & 23.4\% & 28.8\%  \\
+      RoBERTa + Transformer & 29.8\% & 34.4\%  \\
 		\bottomrule
@@
       \midrule
-      LSTM + GloVe & 13.9 & 11.4 \\
-      LSTM + RoBERTa &  &  \\
-      Transformer + GloVe & &  \\
-      Transformer + RoBERTa & 15.7 & 13.8 \\
+      GloVe + LSTM & 13.9 & 11.4 \\
+      GloVe + Transformer & 14.9 & 12.9 \\
+      RoBERTa + LSTM & 14.7 & 12.7  \\
+      RoBERTa + Transformer & 15.7 & 13.8 \\
 		\bottomrule
@@
 		\midrule
-      Transformer (first 512 tokens) & 17.6\% & 10.4\% & 6.68\% & 4.65\% & 19.1\% & 8.49\% & 41.1\% \\
-      Transformer (location-aware) & 19.0\% & 11.7\% & 7.76\% & 5.48\% & 21.1\% & 9.51\% & 51.4\% \\
+      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
+      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
       \\

### 2019-10-23 newser/data/dataset_readers/__init__.py
Train GloVe + LSTM model with NYTimes+

@@ -6,6 +6,7 @@ from .goodnews_flattened_glove import FlattenedGloveGoodNewsReader
 from .goodnews_rare import RareGoodNewsReader
 from .nytimes import NYTimesReader
 from .nytimes_faces import NYTimesFacesReader
+from .nytimes_glove import NYTimesGloveReader
 from .nytimes_names import NYTimesNamesReader
 from .nytimes_names_copy import NYTimesNamesCopyReader
 from .nytimes_names_faces import NYTimesNamesFacesReader

### 2019-10-23 newser/data/dataset_readers/nytimes_glove.py

@@ -1,0 +1,130 @@
+import logging
+import os
+import random
+from datetime import datetime
+from typing import Dict
+
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
+                                    ToTensor)
+
+from newser.data.fields import ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+@DatasetReader.register('nytimes_glove')
+class NYTimesGloveReader(DatasetReader):
+    """Read from the New York Times dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.nytimes
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        random.seed(1234)
+
+    @overrides
+    def _read(self, split: str):
+        # split can be either train, valid, or test
+        # validation and test sets contain 10K examples each
+        if split == 'train':
+            start = datetime(2000, 1, 1)
+            end = datetime(2019, 5, 1)
+        elif split == 'valid':
+            start = datetime(2019, 5, 1)
[…]

### 2019-10-24 scripts/clean_nytimes.py
Clean mongo database

@@ -1,0 +1,130 @@
+"""Get articles from the New York Times API.
+
+Usage:
+    clean_nytimes.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      Mongo host name [default: localhost]
+
+"""
+import os
+from datetime import datetime
+
+import ptvsd
+import pymongo
+import torch
+from docopt import docopt
+from PIL import Image
+from pymongo import MongoClient
+from pymongo.errors import DocumentTooLarge
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.facenet import MTCNN, InceptionResnetV1
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str,
+    })
+    args = schema.validate(args)
+    return args
+
+
+def main():
+    args = docopt(__doc__, version='0.0.1')
+    args = validate(args)
+
+    if args['ptvsd']:
+        address = ('0.0.0.0', args['ptvsd'])
+        ptvsd.enable_attach(address)
+        ptvsd.wait_for_attach()
+
+    client = MongoClient(host=args['host'], port=27017)
+    nytimes = client.nytimes
+
+    article_cursor = nytimes.text_articles.find({
+    }, no_cursor_timeout=True).batch_size(128)
+    for article in tqdm(article_cursor):
+        if 'raw_html' not in article:
+            continue
+        source = {
+            '_id': article['_id'],
+            'raw_html': article['raw_html']
+        }
+        nytimes.source.find_one_and_update(
+            {'_id': article['_id']}, {'$set': source})
+        del article['raw_html']
+        nytimes.text_articles.find_one_and_update(
+            {'_id': article['_id']}, {'$set': article})
+
+    article_cursor = nytimes.articles.find({
+    }, no_cursor_timeout=True).batch_size(128)
+
+    logger.info('Processing NYTimes+')
+    for article in tqdm(article_cursor):
+        if 'facenet_positions' in article:
+            del article['facenet_positions']
+        if 'n_images_with_dfsd_faces' in article:
+            del article['n_images_with_dfsd_faces']
[…]

### 2019-10-25 newser/data/dataset_readers/nytimes_faces.py
Update face data loader

@@ -87,15 +87,15 @@ class NYTimesFacesReader(DatasetReader):
 
         projection = ['_id', 'parsed_section.type', 'parsed_section.text',
                       'parsed_section.hash', 'parsed_section.parts_of_speech',
-                      'parsed_section.facenet', 'image_positions', 'headline',
+                      'parsed_section.facenet_details', 'image_positions', 'headline',
                       'web_url', 'n_images_with_faces']
 
         # Setting the batch size is needed to avoid cursor timing out
         article_cursor = self.db.articles.find({
-            'parsed': True,  # article body is parsed into paragraphs
-            'n_images': {'$gt': 0},  # at least one image is present
+            # 'parsed': True,  # article body is parsed into paragraphs
+            # 'n_images': {'$gt': 0},  # at least one image is present
             'pub_date': {'$gte': start, '$lt': end},
-            'language': 'en',
+            # 'language': 'en',
         }, no_cursor_timeout=True, projection=projection).batch_size(128)
 
         for article in article_cursor:
@@ -147,8 +147,8 @@ class NYTimesFacesReader(DatasetReader):
                 except (FileNotFoundError, OSError):
                     continue
 
-                if 'facenet' in sections[pos]:
-                    face_embeds = sections[pos]['facenet']['embeddings']
+                if 'facenet_details' in sections[pos]:
+                    face_embeds = sections[pos]['facenet_details']['embeddings']
                 else:
                     face_embeds = [[]]
                 # Keep only the top 8 faces (sorted by detection probabilities)

### 2019-10-25 scripts/detect_facenet.py

@@ -145,9 +145,9 @@ def main():
         raise ValueError(f"Unknown batch: {args['batch']}")
 
     article_cursor = nytimes.articles.find({
-        'parsed': True,  # article body is parsed into paragraphs
-        'n_images': {'$gt': 0},  # at least one image is present
-        'language': 'en',
+        # 'parsed': True,  # article body is parsed into paragraphs
+        # 'n_images': {'$gt': 0},  # at least one image is present
+        # 'language': 'en',
         'pub_date': {'$gte': start, '$lt': end},
     }, no_cursor_timeout=True).batch_size(128)
 

### 2019-10-25 scripts/annotate_nytimes_ner.py
Run NER on all NYTimes+ texts

@@ -6,13 +6,17 @@ Usage:
 Options:
     -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
     -h --host HOST      MongoDB host [default: localhost].
+    -b --batch INT      Batch number [default: 1]
 
 """
+
+import functools
+from datetime import datetime
+from multiprocessing import Pool
 
 import ptvsd
 import spacy
 from docopt import docopt
-from joblib import Parallel, delayed
 from pymongo import MongoClient
 from schema import And, Or, Schema, Use
 from tqdm import tqdm
@@ -29,6 +33,7 @@ def validate(args):
     schema = Schema({
         'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
         'host': str,
+        'batch': Use(int),
     })
     args = schema.validate(args)
     return args
@@ -38,8 +43,23 @@ def parse_article(article, nlp, db):
     sections = article['parsed_section']
     changed = False
 
+    if 'main' in article['headline'] and 'named_entities' not in article['headline']:
+        section = article['headline']
+        title = section['main'].strip()
+        doc = nlp(title)
+        section['named_entities'] = []
+        for ent in doc.ents:
+            changed = True
+            ent_info = {
+                'start': ent.start_char,
+                'end': ent.end_char,
+                'text': ent.text,
+                'label': ent.label_,
+            }
+            section['named_entities'].append(ent_info)
+
     for section in sections:
-        if section['type'] == 'caption':
+        if 'named_entities' not in section:
             doc = nlp(section['text'].strip())
             section['named_entities'] = []
             for ent in doc.ents:
@@ -57,6 +77,20 @@ def parse_article(article, nlp, db):
             {'_id': article['_id']}, {'$set': article})
 
 
+def annotate_with_host(host, period):
+    start, end = period
+    nlp = spacy.load("en_core_web_lg")
+    client = MongoClient(host=host, port=27017)
+    db = client.nytimes
+
+    article_cursor = db.articles.find({
+        'pub_date': {'$gte': start, '$lt': end},
+    }, no_cursor_timeout=True).batch_size(128)
+
+    for article in tqdm(article_cursor):
+        parse_article(article, nlp, db)
+
+
 def main():
     args = docopt(__doc__, version='0.0.1')
[…]

### 2019-10-25 scripts/clean_nytimes.py
Move scraping scripts

@@ -49,81 +49,6 @@ def main():
         ptvsd.wait_for_attach()
 
     client = MongoClient(host=args['host'], port=27017)
-    nytimes = client.nytimes
-
-    article_cursor = nytimes.text_articles.find({
-    }, no_cursor_timeout=True).batch_size(128)
-    for article in tqdm(article_cursor):
-        if 'raw_html' not in article:
-            continue
-        source = {
-            '_id': article['_id'],
-            'raw_html': article['raw_html']
-        }
-        nytimes.source.find_one_and_update(
-            {'_id': article['_id']}, {'$set': source})
-        del article['raw_html']
-        nytimes.text_articles.find_one_and_update(
-            {'_id': article['_id']}, {'$set': article})
-
-    article_cursor = nytimes.articles.find({
-    }, no_cursor_timeout=True).batch_size(128)
-
-    logger.info('Processing NYTimes+')
-    for article in tqdm(article_cursor):
-        if 'facenet_positions' in article:
-            del article['facenet_positions']
-        if 'n_images_with_dfsd_faces' in article:
-            del article['n_images_with_dfsd_faces']
-        if 'face_positions' in article:
-            del article['face_positions']
-
-        if 'parsed_section' in article:
-            for s in article['parsed_section']:
-                if 'facenet' in s:
-                    del s['facenet']
-                if 'faces' in s:
-                    del s['faces']
-                if 'n_faces' in s:
-                    del s['n_faces']
-
-        # Save source separately
-        if 'raw_html' in article:
-            source = {
-                '_id': article['_id'],
-                'raw_html': article['raw_html']
-            }
-            nytimes.source.find_one_and_update(
-                {'_id': article['_id']}, {'$set': source})
-            del article['raw_html']
-
-        if not article['parsed'] or article['n_images'] == 0 or article['language'] != 'en':
-            nytimes.text_articles.insert_one(article)
-            nytimes.articles.delete_one({'_id': article['_id']})
-        else:
-            nytimes.articles.find_one_and_update(
-                {'_id': article['_id']}, {'$set': article})
-
-    logger.info('Building NYTimes+ indices')
-    nytimes.articles.create_index([
-        ('n_images', pymongo.ASCENDING),
-        ('n_images_with_faces', pymongo.ASCENDING),
-        ('pub_date', pymongo.DESCENDING),
-    ])
-
-    nytimes.articles.create_index([
[…]

### 2019-10-25 scripts/get_articles_nytimes.py

@@ -160,8 +160,8 @@ def retrieve_article(article, root_dir, db):
     if article['_id'].startswith('nyt://article/'):
         article['_id'] = article['_id'][14:]
 
-    result = db.articles.find_one({'_id': article['_id']})
-    if result is not None and result['scraped']:
+    result = db.source.find_one({'_id': article['_id']})
+    if result is not None:
         return
 
     data = article
@@ -170,9 +170,6 @@ def retrieve_article(article, root_dir, db):
     data['error'] = False
     data['pub_date'] = datetime.strptime(article['pub_date'],
                                          '%Y-%m-%dT%H:%M:%S%z')
-
-    if result is None:
-        db.articles.insert_one(data)
 
     if not article['web_url']:
         return
@@ -185,41 +182,25 @@ def retrieve_article(article, root_dir, db):
         except (ValueError, HTTPError):
             # ValueError: unknown url type: '/interactive/2018/12/05/business/05Markets.html'
             # urllib.error.HTTPError: HTTP Error 404: Not Found
-            data['error'] = True
-            db.articles.find_one_and_update(
-                {'_id': article['_id']}, {'$set': data})
             return
         except (URLError, ConnectionResetError):
-            if i == 9:
-                # urllib.error.URLError: <urlopen error [Errno 110] Connection timed out>
-                data['error'] = True
-                data['timeout'] = True
-                db.articles.find_one_and_update(
-                    {'_id': article['_id']}, {'$set': data})
-                return
-            else:
-                time.sleep(60)
-                continue
+            time.sleep(60)
+            continue
         except socket.timeout:
             pass
         # urllib.error.URLError: <urlopen error [Errno 110] Connection timed out>
-        data['error'] = True
-        data['timeout'] = True
-        db.articles.find_one_and_update(
-            {'_id': article['_id']}, {'$set': data})
         return
 
     data['web_url'] = url
     try:
         raw_html = response.read().decode('utf-8')
     except UnicodeDecodeError:
-        data['error'] = True
-        data['decode_error'] = True
-        db.articles.find_one_and_update(
-            {'_id': article['_id']}, {'$set': data})
         return
 
-    data['raw_html'] = raw_html
+    raw_data = {
+        '_id': article['_id'],
+        'raw_html': raw_html,
+    }
 
[…]

### 2019-10-26 paper/paper.tex
Add model complexity table
Add GloVe + LSTM result for NYTimes+

@@
       \midrule
+      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
       Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
@@
       \midrule
+      GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
       Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
@@
       Ground Truths & 18.4 & 17.1 \\
+      GloVe + LSTM  & 15.3 & 12.3 \\
       Transformer (first 512 tokens)  & 13.1 & 11.7 \\
       Transformer (location-aware) & 13.0 & 11.7  \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+	\caption {Model complexity: Number of trainable parameters}
+	\label{tab:models}
+	\centering
+	\begin{tabular}{lllllll}
+		\toprule
+        & Parameters \\
+      \midrule
+      GloVe + LSTM & 137M \\
+      GloVe + Transformer & 148M \\
+      RoBERTa + LSTM & 139M \\
+      RoBERTa + Transformer & 154M \\
+        + faces & 171M \\
 		\bottomrule

### 2019-10-27 newser/data/dataset_readers/nytimes_ner_set.py
Speed up filtering

@@ -91,10 +91,7 @@ class NYTimesNERSetReader(DatasetReader):
 
         # Setting the batch size is needed to avoid cursor timing out
         article_cursor = self.db.articles.find({
-            'parsed': True,  # article body is parsed into paragraphs
-            'n_images': {'$gt': 0},  # at least one image is present
             'pub_date': {'$gte': start, '$lt': end},
-            'language': 'en',
         }, no_cursor_timeout=True, projection=projection).batch_size(128)
 
         for article in article_cursor:

### 2019-10-27 newser/data/dataset_readers/__init__.py
Attend over both names and faces

@@ -6,6 +6,7 @@ from .goodnews_flattened_glove import FlattenedGloveGoodNewsReader
 from .goodnews_rare import RareGoodNewsReader
 from .nytimes import NYTimesReader
 from .nytimes_faces import NYTimesFacesReader
+from .nytimes_faces_ner import NYTimesFacesNERReader
 from .nytimes_glove import NYTimesGloveReader
 from .nytimes_hierarchical import NYTimesHierarchicalReader
 from .nytimes_names import NYTimesNamesReader

### 2019-10-27 newser/data/dataset_readers/nytimes_faces_ner.py

@@ -1,0 +1,223 @@
+import logging
+import os
+import random
+import re
+from datetime import datetime
+from typing import Dict
+
+import numpy as np
+import torch
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import ArrayField, MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from torchvision.transforms import Compose, Normalize, ToTensor
+
+from newser.data.fields import ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+SPACE_NORMALIZER = re.compile(r"\s+")
+
+
+def tokenize_line(line):
+    line = SPACE_NORMALIZER.sub(" ", line)
+    line = line.strip()
+    return line.split()
+
+
+@DatasetReader.register('nytimes_faces_ner')
+class NYTimesFacesNERReader(DatasetReader):
+    """Read from the New York Times dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.nytimes
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        random.seed(1234)
+
+        roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
+        self.bpe = roberta.bpe
[…]

### 2019-10-27 newser/models/__init__.py

@@ -13,6 +13,7 @@ from .decoder_summary import DynamicConvSummaryDecoder
 from .pointer import PointerModel
 from .transformer import TransformerModel
 from .transformer_faces import TransformerFacesModel
+from .transformer_faces_ner import TransformerFacesNERModel
 from .transformer_flattened import TransformerFlattenedModel
 from .transformer_glove import TransformerGloveModel
 from .transformer_hierarchical import TransformerHierarchicalModel

### 2019-10-27 newser/models/decoder_names_faces.py

@@ -513,6 +513,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
             dropout=attention_dropout)
         self.context_attn_lns['faces'] = nn.LayerNorm(self.embed_dim)
 
+        context_size = self.embed_dim * 4
+        self.context_fc = GehringLinear(context_size, self.embed_dim)
+
         self.fc1 = GehringLinear(self.embed_dim, decoder_ffn_embed_dim)
         self.fc2 = GehringLinear(decoder_ffn_embed_dim, self.embed_dim)
 
@@ -542,6 +545,7 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X = self.maybe_layer_norm(self.conv_layer_norm, X, after=True)
 
         attn = None
+        X_contexts = []
 
         # Image attention
         residual = X
@@ -557,8 +561,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
             need_weights=(not self.training and self.need_attn))
         X_image = F.dropout(X_image, p=self.dropout, training=self.training)
         X_image = residual + X_image
-        X = self.maybe_layer_norm(
+        X_image = self.maybe_layer_norm(
             self.context_attn_lns['image'], X_image, after=True)
+        X_contexts.append(X_image)
 
         # Article attention
         residual = X
@@ -575,8 +580,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X_article = F.dropout(X_article, p=self.dropout,
                               training=self.training)
         X_article = residual + X_article
-        X = self.maybe_layer_norm(
+        X_article = self.maybe_layer_norm(
             self.context_attn_lns['article'], X_article, after=True)
+        X_contexts.append(X_article)
 
         # Face attention
         residual = X
@@ -593,8 +599,9 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X_faces = F.dropout(X_faces, p=self.dropout,
                             training=self.training)
         X_faces = residual + X_faces
-        X = self.maybe_layer_norm(
+        X_faces = self.maybe_layer_norm(
             self.context_attn_lns['faces'], X_faces, after=True)
+        X_contexts.append(X_faces)
 
         # Name attention
         residual = X
@@ -611,8 +618,12 @@ class DynamicConvDecoderLayer(DecoderLayer):
         X_names = F.dropout(X_names, p=self.dropout,
                             training=self.training)
         X_names = residual + X_names
-        X = self.maybe_layer_norm(
[…]

### 2019-10-27 newser/models/transformer_faces_ner.py

@@ -1,0 +1,424 @@
+import math
+import re
+import warnings
+from collections import defaultdict
+from dataclasses import dataclass
+from typing import Any, Dict, List, Optional
+
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.data.vocabulary import Vocabulary
+from allennlp.models.model import Model
+from allennlp.modules import TokenEmbedder
+from allennlp.modules.seq2seq_encoders import _Seq2SeqWrapper
+from allennlp.nn.initializers import InitializerApplicator
+from allennlp.nn.util import get_text_field_mask, sort_batch_by_length
+from allennlp.training.metrics import CategoricalAccuracy
+from overrides import overrides
+from pycocoevalcap.bleu.bleu_scorer import BleuScorer
+from pycocoevalcap.rouge.rouge import Rouge
+from pytorch_transformers.modeling_roberta import RobertaModel
+from pytorch_transformers.modeling_utils import SequenceSummary
+
+from newser.modules import GehringLinear
+from newser.modules.criteria import Criterion
+from newser.modules.span_extractors import (EndpointSpanExtractorFixed,
+                                            SelfAttentiveSpanExtractorFixed)
+
+from .decoder_flattened import Decoder
+from .resnet import resnext101_32x16d_wsl
+
+LSTM = _Seq2SeqWrapper(nn.LSTM)
+
+
+def gelu(x):
+    """Implementation of the gelu activation function.
+        For information: OpenAI GPT's gelu is slightly different (and gives slightly different results):
+        0.5 * x * (1 + torch.tanh(math.sqrt(2 / math.pi)
+                   * (x + 0.044715 * torch.pow(x, 3))))
+        Also see https://arxiv.org/abs/1606.08415
+    """
+    return x * 0.5 * (1.0 + torch.erf(x / math.sqrt(2.0)))
+
+
+@Model.register("transformer_faces_ner")
+class TransformerFacesNERModel(Model):
+    """
+    An AllenNLP Model that runs pretrained BERT,
+    takes the pooled output, and adds a Linear layer on top.
+    If you want an easy way to use BERT for classification, this is it.
+    Note that this is a somewhat non-AllenNLP-ish model architecture,
+    in that it essentially requires you to use the "bert-pretrained"
+    token indexer, rather than configuring whatever indexing scheme you like.
+
+    See `allennlp/tests/fixtures/bert/bert_for_classification.jsonnet`
[…]

### 2019-10-27 scripts/detect_facenet_goodnews.py
Remove old facenet runs

@@ -45,6 +45,9 @@ def detect_faces(sample, goodnews, image_dir, face_dir, mtcnn, resnet):
     if 'facenet_details' in sample:
         return
 
+    if 'facenet' in sample:
+        del sample['facenet']
+
     image_path = os.path.join(image_dir, f"{sample['_id']}.jpg")
     try:
         image = Image.open(image_path)
@@ -70,7 +73,6 @@ def detect_faces(sample, goodnews, image_dir, face_dir, mtcnn, resnet):
         'n_faces': len(faces[:10]),
         'embeddings': embeddings.cpu().tolist()[:10],
         'detect_probs': probs.tolist()[:10],
-        'face_probs': face_probs.cpu().tolist()[:10],
     }
 
     try:

### 2019-10-27 paper/paper.tex
Add result for RoBERTa + LSTM with NYTimes+

@@
       GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
+      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
       Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
@@
       GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
+      RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
       Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
@@
       GloVe + LSTM  & 15.3 & 12.3 \\
+      RoBERTa + LSTM  & 15.6 & 13.4 \\
       Transformer (first 512 tokens)  & 13.1 & 11.7 \\

### 2019-10-27 paper/paper.tex
Add model parameter count

@@
         + faces & 171M \\
+        + names & 175M \\
+        + faces + names & 192M \\
 		\bottomrule

### 2019-10-30 paper/paper.tex
Add GloVe + Transformer for NYTimes+

@@
       GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
+      GloVe + Transformer & 18.0 & 8.88 & 4.90 & 2.98 & 16.3 & 7.30 & 21.0 \\
       RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
@@
       GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
+      GloVe + Transformer & 19.2\% & 21.5\% & 0\% & 0\% & 0\% & 0\%  \\
       RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
@@
       GloVe + LSTM  & 15.3 & 12.3 \\
+      GloVe + Transformer  & 16.1 & 13.6 \\
       RoBERTa + LSTM  & 15.6 & 13.4 \\

### 2019-10-30 newser/models/__init__.py
Avoid attention concatenation bottleneck

@@ -3,6 +3,7 @@ from .baseline_glove import BaselineGloveModel
 from .decoder import DynamicConvDecoder
 from .decoder_faces import DynamicConvFacesDecoder
 from .decoder_faces_parallel import DynamicConvFacesParallelDecoder
+from .decoder_faces_parallel_2 import DynamicConvFacesParallel2Decoder
 from .decoder_flattened_lstm import LSTMDecoder
 from .decoder_gpt2 import GPT2Decoder
 from .decoder_interact import DynamicConvInteractDecoder

### 2019-10-30 newser/models/decoder_faces_parallel_2.py

@@ -1,0 +1,627 @@
+# Copyright (c) 2017-present, Facebook, Inc.
+# All rights reserved.
+#
+# This source code is licensed under the license found in the LICENSE file in
+# the root directory of this source tree. An additional grant of patent rights
+# can be found in the PATENTS file in the same directory.
+
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from allennlp.common.registrable import Registrable
+from allennlp.modules.text_field_embedders import TextFieldEmbedder
+
+from newser.modules import (AdaptiveSoftmax, DynamicConv1dTBC, GehringLinear,
+                            LightweightConv1dTBC, MultiHeadAttention)
+from newser.modules.token_embedders import AdaptiveEmbedding
+from newser.utils import eval_str_list, fill_with_neg_inf, softmax
+
+from .decoder_base import Decoder, DecoderLayer
+
+
+@Decoder.register('dynamic_conv_decoder_faces_parallel_2')
+class DynamicConvFacesParallel2Decoder(Decoder):
+    """
+    DynamicConv decoder consisting of *args.decoder_layers* layers. Each layer
+    is a :class:`DynamicConvDecoderLayer`.
+
+    Args:
+        args (argparse.Namespace): parsed command-line arguments
+        dictionary (~fairseq.data.Dictionary): decoding dictionary
+        embed_tokens (torch.nn.Embedding): output embedding
+        no_encoder_attn (bool, optional): whether to attend to encoder outputs.
+            Default: ``False``
+        left_pad (bool, optional): whether the input is left-padded. Default:
+            ``False``
+    """
+
+    def __init__(self, vocab, embedder: TextFieldEmbedder, max_target_positions, dropout,
+                 share_decoder_input_output_embed,
+                 decoder_output_dim, decoder_conv_dim, decoder_glu,
+                 decoder_conv_type, weight_softmax, decoder_attention_heads,
+                 weight_dropout, relu_dropout, input_dropout,
+                 decoder_normalize_before, attention_dropout, decoder_ffn_embed_dim,
+                 decoder_kernel_size_list, adaptive_softmax_cutoff=None,
+                 tie_adaptive_weights=False, adaptive_softmax_dropout=0,
+                 tie_adaptive_proj=False, adaptive_softmax_factor=0, decoder_layers=6,
+                 final_norm=True, padding_idx=0, namespace='target_tokens',
+                 vocab_size=None, section_attn=False, swap=False):
+        super().__init__()
+        self.vocab = vocab
[…]

### 2019-10-30 scripts/classify_faces_nytimes.py
Classify faces

@@ -1,0 +1,101 @@
+"""Get articles from the New York Times API.
+
+Usage:
+    classify_faces_nytimes.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      Mongo host name [default: localhost]
+    -f --face-dir DIR   Image directory [default: ./data/nytimes/facenet].
+
+"""
+import os
+import pickle
+from collections import Counter
+
+import numpy as np
+import ptvsd
+from docopt import docopt
+from keras.preprocessing import image
+from keras_vggface import utils
+from keras_vggface.vggface import VGGFace
+from pymongo import MongoClient
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str,
+        'face_dir': str,
+    })
+    args = schema.validate(args)
+    return args
+
+
+def classify_face(face_path, vggface, counter):
+    img = image.load_img(face_path, target_size=(224, 224))
+    x = image.img_to_array(img)
+    x = np.expand_dims(x, axis=0)
+    x = utils.preprocess_input(x, version=2)  # or version=2
+    preds = vggface.predict(x)
+    name, prob = utils.decode_predictions(preds)[0][0]
+    if prob > 0.5:
+        counter.update([name])
+    else:
+        counter.update(['unknown'])
+
+
+def main():
+    args = docopt(__doc__, version='0.0.1')
+    args = validate(args)
+
+    if args['ptvsd']:
+        address = ('0.0.0.0', args['ptvsd'])
+        ptvsd.enable_attach(address)
+        ptvsd.wait_for_attach()
+
+    face_dir = args['face_dir']
+    vggface = VGGFace(model='resnet50')
+
+    client = MongoClient(host=args['host'], port=27017)
+    db = client.nytimes
+
+    article_cursor = db.articles.find(
+        {}, no_cursor_timeout=True).batch_size(128)
+
+    counter = Counter()
+
+    for i, article in tqdm(enumerate(article_cursor)):
+        sections = article['parsed_section']
+        image_positions = article['image_positions']
+        for pos in image_positions:
[…]

### 2019-11-04 paper/paper.tex
Write introduction

@@
    We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, pretrained
-   text and image embeddings, and bags of attentions, our system is able to
-   describe an image using specific events and names mentioned in the article.
-   Our model achieves state-of-the-art results on the existing GoodNews
-   dataset. We also extend the GoodNews dataset to improve the quality of
-   articles and study the importance of the image location on the page.
+   By combining the transformer architecture, byte-pair encoding, RoBERTa
+   embeddings for text, ResNet-152 embeddings for images, and bags of
+   attentions, our system is able to describe an image with specific named
+   entities mentioned in the article. Our model achieves a CIDEr score of 54 on
+   the GoodNews dataset, significantly outperforming the previous state-of-art
+   CIDEr of 13. We also introduce the NYTimes+ dataset, an extended version of
+   GoodNews with higher-quality articles and metadata that allow us to study
+   the importance of the image location within the text. On NYTimes+, we
+   achieve a CIDEr of 51. Pretrained models and source code are available from
+   \href{https://github.com}{https://anonymized}.
 \end{abstract}
@@
 
-Our main contributions are as follows:
+Most existing captioning systems can only generate a generic description of an
+image \cite{Vinyals2014ShowAT, Fang2014FromCT, Karpathy2015DeepVA,
+Rennie2016SelfCriticalST, Lu2016KnowingWT, Anderson2017BottomUpAT}, mainly
+because these architectures cannot handle an open vocabulary and early
+captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
+Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
+only visual cues present in the image. More recently, datasets such as TIME
+\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
+\cite{Biten2019GoodNews} include real-life captions scraped from online
+newspapers. To the best of our knowledge, all of the existing models
+that are trained on these news datasets use template-based methods to insert
+named entities.
 
-\begin{itemize}
+This motivates us to ask whether it is possible to design a fully end-to-end
+model for news image captioning. The model would need to 1) attend to
+contextual cues from different modalities (image and text) and 2) generate
+captions that contain specific information including rare proper names that
+have not been seen in the training data. To answer this, we look at the recent
+development in sequence-to-sequence architectures and language modeling.
+
+The most successful family of models in natural language understanding and
+generation are the transformer networks, which consist of layers of
+self-attention and feed-forward connections stacked on top of each other
+\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
+outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
+story generation \cite{Fan2018HierarchicalNS}, summarization
+\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
+
+Furthermore, transformers have led to the rise of unsupervised language
+representation learning such as BERT \cite{Devlin2019BERT}, XLM
+\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
+\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
+embeddings provided by these methods have helped establish new state-of-the-art
+results on many natural language understanding benchmarks including GLUE
+\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
+\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
+baselines in many cases.
+
+In parallel to the development of these pre-training methods, many novel
+techniques have been proposed to improve training convergence and handle more
+diverse data inputs. The most significant contribution is the use of byte-pair
+encoding \cite{Sennrich2015NeuralMT} to handle an open vocabulary. This is done
+by representing a rare word as a sequence of subword units.
+
+The goal of this paper is to make use of these recent developments, along with
+their bags of tricks, to carefully design a captioning system most appropriate
+for news images. Our main contributions are thus threefold:
+
+\begin{enumerate}
    \item We show that combining article attention with pre-trained
@@
 
-   \item We build on the GoodNews dataset to produce a larger and more
-   complete news captioning dataset consisting of 445,828 articles from the New
-   York Times and their 794K images with captions. In contrast to GoodNews
-   our dataset contains the full article text, and the location of the image
-   within the page.
-\end{itemize}
+   \item We build on the GoodNews dataset to produce a larger and more complete
+   news captioning dataset consisting of 445,828 articles from the New York
+   Times and their 794K images with captions. This constitutes the largest
+   news image captioning dataset to date. In contrast to GoodNews our dataset
+   contains the full article text, and the location of the image within the
+   page.
+\end{enumerate}
 
@@
 sentence. They also created the ``GoodNews" dataset, which contains more
-samples than MSCOCO \cite{Lin2014MicrosoftCC} and BreakingNews
+samples than MSCOCO and BreakingNews
 \cite{Ramisa2016BreakingNewsAA} datasets.
@@
       \midrule
-      GloVe + LSTM & 137M \\
+      GloVe + LSTM & 153M \\
       GloVe + Transformer & 148M \\

### 2019-11-04 newser/commands/evaluate.py
Compute readability metrics

@@ -1,9 +1,12 @@
 import json
 import logging
+import math
 import os
+import string
 from typing import Any, Dict, Iterable
 
 import spacy
+import textstat
 import torch
 from allennlp.common.checks import check_for_gpu
 from allennlp.common.tqdm import Tqdm
@@ -16,6 +19,7 @@ from allennlp.models.archival import load_archive
 from allennlp.nn import util as nn_util
 from allennlp.nn.util import move_to_device
 from allennlp.training.util import HasBeenWarned, datasets_from_params
+from nltk.tokenize import word_tokenize
 
 from .train import yaml_to_params
 
@@ -170,6 +174,10 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
                 'context': m['context'],
                 'caption_names': get_proper_nouns(m['caption'], nlp),
                 'generated_names': get_proper_nouns(generation, nlp),
+                'caption_readability': get_readability_scores(m['caption']),
+                'gen_readability': get_readability_scores(generation),
+                'caption_np': get_narrative_productivity(m['caption']),
+                'gen_np': get_narrative_productivity(generation),
             }
 
             if 'copied_texts' in output_dict:
@@ -185,3 +193,105 @@ def get_proper_nouns(text, nlp):
         if token.pos_ == 'PROPN':
             proper_nouns.append(token.text)
     return proper_nouns
+
+
+def get_readability_scores(text):
+    scores = {
+        'flesch_reading_ease': textstat.flesch_reading_ease(text),
+        'flesch_kincaid_grade': textstat.flesch_kincaid_grade(text),
+        'gunning_fog': textstat.gunning_fog(text),
+        'smog_index': textstat.smog_index(text),
+        'automated_readability_index': textstat.automated_readability_index(text),
+        'coleman_liau_index': textstat.coleman_liau_index(text),
+        'linsear_write_formula': textstat.linsear_write_formula(text),
+        'dale_chall_readability_score': textstat.dale_chall_readability_score(text),
+        'text_standard': textstat.text_standard(text, float_output=True),
+        'difficult_words': textstat.difficult_words(text) / len(text.split()),
+    }
+    return scores
+
+
+def is_word(tok):
+    return tok not in string.punctuation
+
+
+def get_narrative_productivity(text):
+    doc = word_tokenize(text)
[…]

### 2019-11-04 newser/data/dataset_readers/nytimes_ner_set.py
Fix NER experiment

@@ -5,6 +5,8 @@ import re
 from datetime import datetime
 from typing import Dict
 
+import numpy as np
+import pymongo
 import torch
 from allennlp.data.dataset_readers.dataset_reader import DatasetReader
 from allennlp.data.fields import MetadataField, TextField
@@ -16,6 +18,7 @@ from PIL import Image
 from pymongo import MongoClient
 from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
                                     ToTensor)
+from tqdm import tqdm
 
 from newser.data.fields import CorefTextField, ImageField, ListTextField
 
@@ -64,6 +67,7 @@ class NYTimesNERSetReader(DatasetReader):
             ToTensor(),
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
         random.seed(1234)
+        self.rs = np.random.RandomState(1234)
 
         roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
         self.bpe = roberta.bpe
@@ -73,28 +77,24 @@ class NYTimesNERSetReader(DatasetReader):
     def _read(self, split: str):
         # split can be either train, valid, or test
         # validation and test sets contain 10K examples each
-        if split == 'train':
-            start = datetime(2000, 1, 1)
-            end = datetime(2019, 5, 1)
-        elif split == 'valid':
-            start = datetime(2019, 5, 1)
-            end = datetime(2019, 6, 1)
-        elif split == 'test':
-            start = datetime(2019, 6, 1)
-            end = datetime(2019, 9, 1)
-        else:
+        if split not in ['train', 'valid', 'test']:
             raise ValueError(f'Unknown split: {split}')
+
+        logger.info('Grabbing all article IDs')
+        sample_cursor = self.db.articles.find({
+            'split': split,
+        }, projection=['_id']).sort('_id', pymongo.ASCENDING)
+        ids = np.array([article['_id'] for article in tqdm(sample_cursor)])
+        sample_cursor.close()
+        self.rs.shuffle(ids)
 
         projection = ['_id', 'parsed_section.type', 'parsed_section.text',
                       'parsed_section.hash', 'parsed_section.named_entities',
                       'image_positions', 'headline', 'web_url']
 
-        # Setting the batch size is needed to avoid cursor timing out
-        article_cursor = self.db.articles.find({
-            'pub_date': {'$gte': start, '$lt': end},
-        }, no_cursor_timeout=True, projection=projection).batch_size(128)
-
-        for article in article_cursor:
[…]

### 2019-11-04 newser/data/dataset_readers/nytimes_faces_ner_matched.py
Select top 4 faces

@@ -55,6 +55,7 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
                  image_dir: str,
                  mongo_host: str = 'localhost',
                  mongo_port: int = 27017,
+                 use_caption_names: bool = True,
                  lazy: bool = True) -> None:
         super().__init__(lazy)
         self._tokenizer = tokenizer
@@ -65,12 +66,14 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
         self.preprocess = Compose([
             ToTensor(),
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        self.use_caption_names = use_caption_names
         random.seed(1234)
         self.rs = np.random.RandomState(1234)
 
         roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
         self.bpe = roberta.bpe
         self.indices = roberta.task.source_dictionary.indices
+
 
     @overrides
     def _read(self, split: str):
@@ -115,7 +118,10 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
                 if not caption:
                     continue
 
-                n_persons = len(self._get_person_names(sections[pos]))
+                if self.use_caption_names:
+                    n_persons = len(self._get_person_names(sections[pos]))
+                else:
+                    n_persons = 4
 
                 before = []
                 after = []

### 2019-11-04 paper/paper.tex
Add main contributions

@@
 %%%%%%%%% TITLE
-\title{Writing News Captions with Bags of Attention}
+\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
 
@@
    We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, RoBERTa
-   embeddings for text, ResNet-152 embeddings for images, and bags of
-   attentions, our system is able to describe an image with specific named
-   entities mentioned in the article. Our model achieves a CIDEr score of 54 on
-   the GoodNews dataset, significantly outperforming the previous state-of-art
-   CIDEr of 13. We also introduce the NYTimes+ dataset, an extended version of
-   GoodNews with higher-quality articles and metadata that allow us to study
-   the importance of the image location within the text. On NYTimes+, we
-   achieve a CIDEr of 51. Pretrained models and source code are available from
+   By combining the transformer architecture, byte-pair encoding, and
+   pretrained embeddings from three different modalities (RoBERTa for text,
+   ResNet-152 for images, and FaceNet for faces), our system is able to
+   describe an image with specific named entities mentioned in the article. Our
+   model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
+   outperforming the previous state-of-art CIDEr of 13. We also introduce the
+   NYTimes+ dataset, the largest news image captioning dataset to date.
+   NYTimes+ is an extended version of GoodNews with higher-quality articles and
+   metadata that allow us to study the importance of the image location within
+   the text. On NYTimes+, we achieve a CIDEr of 51. Pretrained models and
+   source code are available from
    \href{https://github.com}{https://anonymized}.
@@
 \cite{Biten2019GoodNews} include real-life captions scraped from online
-newspapers. To the best of our knowledge, all of the existing models
-that are trained on these news datasets use template-based methods to insert
-named entities.
+newspapers. To the best of our knowledge, all existing models that are trained
+on these news datasets use template-based methods to insert named entities.
 
@@
 model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities (image and text) and 2) generate
-captions that contain specific information including rare proper names that
-have not been seen in the training data. To answer this, we look at the recent
-development in sequence-to-sequence architectures and language modeling.
+contextual cues from different modalities and 2) generate captions that contain
+specific information including rare proper names that have not been seen in the
+training data. To answer this, we look at the recent development in
+sequence-to-sequence architectures and language modeling.
 
@@
 
+\begin{figure}[t]
+   \begin{center}
+   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+      %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+   \end{center}
+      \caption{An example caption.}
+   \label{fig:long}
+   \label{fig:onecol}
+\end{figure}
+
 In parallel to the development of these pre-training methods, many novel
@@
 \begin{enumerate}
-   \item We show that combining article attention with pre-trained
-   contextualized word piece embeddings allows our model to generate captions
-   containing relevant words that were not seen during training.
+   \item We introduce the NYTimes+ dataset, containing 446K articles and 794K
+   images with captions from the New York Times spanning 14 years. This
+   constitutes the largest news image captioning dataset to date. NYTimes+ is
+   built upon the GoodNews dataset, but we write a custom parser to collect
+   higher-quality articles and metadata such as the location of an image within
+   the page.
 
-   \item We demonstrate that the location of the image within the article is an
-   important signal for generating relevant news captions.
+   \item We build a captioning model that combines the power of transformers,
+   byte-pair encoding, and attention over three different modalities (text,
+   images, and faces). We show that our model achieves state-of-the-art results
+   with a significant margin over previous methods, and in particular, it can
+   generate names not seen during training.
 
-   \item We build on the GoodNews dataset to produce a larger and more complete
-   news captioning dataset consisting of 445,828 articles from the New York
-   Times and their 794K images with captions. This constitutes the largest
-   news image captioning dataset to date. In contrast to GoodNews our dataset
-   contains the full article text, and the location of the image within the
-   page.
+   \item We provide a detailed model analysis, deconstructing the most
+   important modeling components and quantifying the incremental contribution
+   that each of them makes not only to the popular metrics such as BLEU, ROUGE,
+   METEOR, and CIDEr; but also to other linguistic measures like readability
+   scores, caption length, and recall of rare names.
 \end{enumerate}
@@
 multivariate residual modules.
-
-\begin{figure}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-      %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-   \end{center}
-      \caption{An example caption.}
-   \label{fig:long}
-   \label{fig:onecol}
-   \end{figure}
 
@@
       GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
-      GloVe + Transformer & 18.0 & 8.88 & 4.90 & 2.98 & 16.3 & 7.30 & 21.0 \\
+      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\
       RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
@@
       GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
-      GloVe + Transformer & 19.2\% & 21.5\% & 0\% & 0\% & 0\% & 0\%  \\
+      GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
       RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
@@
       GloVe + LSTM  & 15.3 & 12.3 \\
-      GloVe + Transformer  & 16.1 & 13.6 \\
+      GloVe + Transformer  & 15.1 & 12.9 \\
       RoBERTa + LSTM  & 15.6 & 13.4 \\

### 2019-11-05 scripts/get_unknown_caption_names.py
Count unknown caption names

@@ -1,0 +1,107 @@
+"""Get articles from the New York Times API.
+
+Usage:
+    get_unknown_caption_names.py [options]
+
+Options:
+    -p --ptvsd PORT     Enable debug mode with ptvsd on PORT, e.g. 5678.
+    -h --host HOST      Mongo host name [default: localhost]
+
+"""
+import pickle
+
+import ptvsd
+from docopt import docopt
+from pymongo import MongoClient
+from schema import And, Or, Schema, Use
+from tqdm import tqdm
+
+from newser.utils import setup_logger
+
+logger = setup_logger()
+
+
+def validate(args):
+    """Validate command line arguments."""
+    args = {k.lstrip('-').lower().replace('-', '_'): v
+            for k, v in args.items()}
+    schema = Schema({
+        'ptvsd': Or(None, And(Use(int), lambda port: 1 <= port <= 65535)),
+        'host': str,
+    })
+    args = schema.validate(args)
+    return args
+
+
+def get_name_stats(host):
+    client = MongoClient(host=host, port=27017)
+    db = client.nytimes
+
+    projection = ['_id', 'parsed_section.type', 'parsed_section.text',
+                  'parsed_section.hash', 'parsed_section.parts_of_speech',
+                  'parsed_section.named_entities',
+                  'image_positions', 'headline',
+                  'web_url', 'n_images_with_faces']
+
+    article_cursor = db.articles.find({
+        'split': 'train',
+    }, no_cursor_timeout=True, projection=projection).batch_size(128)
+
+    results = {}
+    count, total = 0, 0
+
+    for article in tqdm(article_cursor):
+        article_names = set()
+        caption_names = set()
+
+        sections = article['parsed_section']
+        for section in sections:
+            if section['type'] == 'paragraph':
+                article_names |= get_proper_names(section)
+            elif section['type'] == 'caption':
+                caption_names |= get_proper_names(section)
+
+        unknown_names = set()
+        for name in caption_names:
+            if name not in article_names:
+                unknown_names.add(name)
+
+        if unknown_names:
+            results[article['_id']] = sorted(unknown_names)
+        count += len(unknown_names)
+        total += len(caption_names)
+
+    print('Count:', count)
+    print('Total:', total)
+    print('No articles with unknown names:', len(results))
+
+    with open('./data/nytimes/unknown_caption_names.pkl', 'wb') as f:
[…]

### 2019-11-05 paper/paper.tex
Update references

@@
 Most existing captioning systems can only generate a generic description of an
-image \cite{Vinyals2014ShowAT, Fang2014FromCT, Karpathy2015DeepVA,
-Rennie2016SelfCriticalST, Lu2016KnowingWT, Anderson2017BottomUpAT}, mainly
+image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
+Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
 because these architectures cannot handle an open vocabulary and early
@@
 \begin{enumerate}
-   \item We introduce the NYTimes+ dataset, containing 446K articles and 794K
-   images with captions from the New York Times spanning 14 years. This
-   constitutes the largest news image captioning dataset to date. NYTimes+ is
-   built upon the GoodNews dataset, but we write a custom parser to collect
-   higher-quality articles and metadata such as the location of an image within
-   the page.
+   \item We introduce NYTimes+, the largest news image captioning dataset to
+   date, containing 446K articles and 794K images with captions from the New
+   York Times spanning 14 years. NYTimes+ is built upon the GoodNews dataset,
+   but we write a custom parser to collect higher-quality articles and metadata
+   such as the location of an image within the page.
 
@@
    with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training.
+   generate names not seen during training without the use of templates.
 
@@
 improvements include giving the model the option to not attend to any image
-region \cite{Lu2016KnowingWT}, using reinforcement learning to directly
-optimize for the CIDEr metric \cite{Rennie2016SelfCriticalST}, and using a
+region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
+optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
 bottom-up approach to propose a region to attend to
-\cite{Anderson2017BottomUpAT}. All of these system generate generic captions.
+\cite{Anderson2017BottomUpAT}. All of these systems generate generic captions.
 
@@
 
-\section{Dataset}
-
-A summary of the original GoodNews dataset and our new dataset is shown in
-Table \ref{tab:datasets}. The GoodNews+ dataset is our attempt at recollecting
-the original GoodNews dataset. We managed to crawl all the original articles,
-but the number of images is slightly less, either due to dead links or
-not crawling images unrelated to the main article. GoodNews+ allows us to make the
-following observations about the original GoodNews dataset:
-
-\begin{itemize}
-   \item On average, half of the article body is missing. This includes
-         the first few paragraphs that might contain important information
-         about the top caption.
-   \item The dataset contains a small number Spanish articles.
-   \item Sometimes images from the recommendation sidebar, which are not part
-         of the main article, are included in the dataset.
-\end{itemize}
-
-This motivates us to recollect data from the New York Times in a more careful
-manner, using our own parser. We call this NYTimes+.
+\section{Datasets}
 
@@
 		\midrule
-      No of articles & 241 808 & 241 808 & 445 828 \\
-      No of images   & 462 642 & 440 112 & 794 085 \\
+      No. of articles & 241 808 & 241 808 & 445 828 \\
+      No. of images   & 462 642 & 440 112 & 794 085 \\
       Article length & 451 & 963 & 974 \\
@@
 
-In addition to having a more complete coverage, we also collect information
-about the image position in each article. As shown in Figure \ref{fig:dist},
-about 40\% of the articles have two or more images.
+\subsection{GoodNews and GoodNews+}
 
-\begin{figure}[h]
+As a starting point, we use the GoodNews dataset, previously the largest
+dataset on news image captioning. As part of the quality check, we also
+reconstruct the same dataset on our own. We use the New York Times API and
+write a custom parser to recollect and extract all the articles and images in
+in the same period as GoodNews from the original source. We call this
+GoodNews+. We managed to crawl all the original articles, but the number of
+images is slightly less, either due to dead links or not crawling images
+unrelated to the main article. GoodNews+ allows us to make the following
+observations about the original GoodNews dataset:
+
+\begin{itemize}
+   \item The average length of an article in GoodNews is 451 words, while it is
+         963 words in GoodNews+. Thus half of the article body is missing in
+         GoodNews. This includes the first few paragraphs that might contain
+         important information about the top caption. Looking through the
+         publicly released code, we found that this is because the original
+         parser used by \cite{Biten2019GoodNews} fails to recognize certain
+         HTML tags used in New York Times web pages.
+   \item GoodNews contains X Spanish articles, adding unwanted noise to the
+         training.
+   \item GoodNews sometimes include images from the recommendation sidebar,
+         which are not part of the main article.
+\end{itemize}
+
+Despite the above limitation, we will use the original GoodNews dataset in our
+experiments, along with the original train-validation-test split to make
+comparison to previous works easier.
+
+\subsection{NYTimes+}
+
+At the same time, we also construct a new dataset, which we call NYTimes+.
+NYTimes+ exhibits several advantages over GoodNews:
+
+\begin{itemize}
+   \item By increasing the collection period to the last 14 years (March 2005
+   -- September 2019), NYTimes+ contains 80\% more articles and images, thus
+   becoming the largest news captioning dataset.
+   \item NYTimes+ contains only English articles.
+   \item We are careful to include only images that are part of the main
+   article.
+   \item In addition to having a more complete coverage, we also collect
+   information about the image position in each article. As shown in Figure
+   \ref{fig:dist}, about 40\% of the articles have two or more images.
+\end{itemize}
+
+A summary of the datasets is shown in Table \ref{tab:datasets}.
+
+\begin{figure}[t]
    \begin{center}
@@
 
-We use ResNeXt-101 \cite{Xie2016AggregatedRT} to obtain an embedding for
+We use ResNeXt-101 \cite{Xie2017AggregatedRT} to obtain an embedding for
 the images. For each generation step, we use the Scalar-Dot-Product attention

### 2019-11-06 newser/models/baseline_glove.py
Train with wider LSTM

@@ -70,11 +70,6 @@ class BaselineGloveModel(Model):
                  decoder: Decoder,
                  criterion: Criterion,
                  evaluate_mode: bool = False,
-                 attention_dim: int = 1024,
-                 hidden_size: int = 1024,
-                 dropout: float = 0.1,
-                 vocab_size: int = 50264,
-                 model_name: str = 'roberta-base',
                  namespace: str = 'bpe',
                  index: str = 'roberta',
                  padding_value: int = 1,

### 2019-11-06 newser/models/decoder_flattened_lstm.py

@@ -121,8 +121,8 @@ class LSTMDecoder(Decoder):
 
         self.adaptive_softmax = None
 
-        self.project_out_dim = GehringLinear(embed_dim, output_embed_dim, bias=False) \
-            if embed_dim != output_embed_dim and not tie_adaptive_weights else None
+        self.project_out_dim = GehringLinear(hidden_size, output_embed_dim, bias=False) \
+            if hidden_size != output_embed_dim else None
 
         if adaptive_softmax_cutoff is not None:
             adaptive_inputs = None

### 2019-11-06 newser/data/dataset_readers/__init__.py
Train pointer generator with GoodNews

@@ -1,5 +1,6 @@
 from .goodnews import GoodNewsReader
 from .goodnews_annotated import AnnotatedGoodNewsReader
+from .goodnews_copy_matched import GoodNewsCopyMatchedReader
 from .goodnews_coref import CorefGoodNewsReader
 from .goodnews_face_ner_matched import GoodNewsFaceNERMatchedReader
 from .goodnews_flattened import FlattenedGoodNewsReader

### 2019-11-06 newser/data/dataset_readers/goodnews_copy_matched.py

@@ -1,0 +1,222 @@
+import logging
+import os
+import pickle
+import random
+from collections import OrderedDict
+from typing import Dict
+
+import numpy as np
+import pymongo
+import spacy
+from allennlp.data.dataset_readers.dataset_reader import DatasetReader
+from allennlp.data.fields import ArrayField, MetadataField, TextField
+from allennlp.data.instance import Instance
+from allennlp.data.token_indexers import TokenIndexer
+from allennlp.data.tokenizers import Tokenizer
+from overrides import overrides
+from PIL import Image
+from pymongo import MongoClient
+from spacy.tokens import Doc
+from torchvision.transforms import (CenterCrop, Compose, Normalize, Resize,
+                                    ToTensor)
+from tqdm import tqdm
+
+from newser.data.fields import CopyTextField, ImageField, ListTextField
+
+logger = logging.getLogger(__name__)  # pylint: disable=invalid-name
+
+
+@DatasetReader.register('goodnews_copy_matched')
+class GoodNewsCopyMatchedReader(DatasetReader):
+    """Read from the Good News dataset.
+
+    See the repo README for more instruction on how to download the dataset.
+
+    Parameters
+    ----------
+    tokenizer : ``Tokenizer``
+        We use this ``Tokenizer`` for both the premise and the hypothesis.
+        See :class:`Tokenizer`.
+    token_indexers : ``Dict[str, TokenIndexer]``
+        We similarly use this for both the premise and the hypothesis.
+        See :class:`TokenIndexer`.
+    """
+
+    def __init__(self,
+                 tokenizer: Tokenizer,
+                 token_indexers: Dict[str, TokenIndexer],
+                 image_dir: str,
+                 annotation_path: str = None,
+                 mongo_host: str = 'localhost',
+                 mongo_port: int = 27017,
+                 eval_limit: int = 5120,
+                 use_caption_names: bool = True,
+                 lazy: bool = True) -> None:
+        super().__init__(lazy)
+        self._tokenizer = tokenizer
+        self._token_indexers = token_indexers
+        self.client = MongoClient(host=mongo_host, port=mongo_port)
+        self.db = self.client.goodnews
+        self.image_dir = image_dir
+        self.preprocess = Compose([
+            # Resize(256), CenterCrop(224),
+            ToTensor(),
+            Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+        self.eval_limit = eval_limit
[…]

### 2019-11-06 paper/paper.tex
Update parameter count

@@
 \cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
-\cite{Biten2019GoodNews} include real-life captions scraped from online
-newspapers. To the best of our knowledge, all existing models that are trained
+\cite{Biten2019GoodNews} include real-life captions written by professional
+journalists. To the best of our knowledge, all existing models that are trained
 on these news datasets use template-based methods to insert named entities.
@@
 bottom-up approach to propose a region to attend to
-\cite{Anderson2017BottomUpAT}. All of these systems generate generic captions.
+\cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
+captions with a limited vocabulary.
 
-A more challenging task is to generate captions for news images, in which we
+A more challenging task is to produce captions for news images, in which we
 need to be able to generate entity names. There are non-neural approaches
@@
 write a custom parser to recollect and extract all the articles and images in
-in the same period as GoodNews from the original source. We call this
-GoodNews+. We managed to crawl all the original articles, but the number of
-images is slightly less, either due to dead links or not crawling images
-unrelated to the main article. GoodNews+ allows us to make the following
-observations about the original GoodNews dataset:
+the same period as GoodNews from the original source. We call this GoodNews+.
+We were able to crawl all the original articles, but the number of images is
+slightly less, either due to dead links or not crawling images unrelated to the
+main article. GoodNews+ allows us to make the following observations about the
+original GoodNews dataset:
 
@@
       GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
-      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\
+      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
       RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
@@
       \midrule
-      GloVe + LSTM & 153M \\
+      GloVe + LSTM & 157M \\
       GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 139M \\
+      RoBERTa + LSTM & 159M \\
       RoBERTa + Transformer & 154M \\
         + faces & 171M \\
-        + names & 175M \\
-        + faces + names & 192M \\
+      %   + names & 175M \\
+      %   + faces + names & 192M \\
 		\bottomrule

### 2019-11-06 newser/commands/evaluate.py
Store entities during evaluation

@@ -87,7 +87,7 @@ def evaluate(model: Model,
              eval_suffix: str,
              batch_weight_key: str) -> Dict[str, Any]:
     check_for_gpu(cuda_device)
-    nlp = spacy.load("en_core_web_lg", disable=['parser', 'ner'])
+    nlp = spacy.load("en_core_web_lg")
     assert not os.path.exists(os.path.join(
         serialization_dir, f'generations{eval_suffix}.jsonl'))
     with torch.no_grad():
@@ -165,6 +165,8 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
         for i, caption in enumerate(captions):
             m = metadatas[i]
             generation = generations[i]
+            caption_doc = nlp(m['caption'])
+            gen_doc = nlp(generation)
             obj = {
                 'caption': caption,
                 'raw_caption': m['caption'],
@@ -172,8 +174,10 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
                 'web_url': m['web_url'],
                 'image_path': m['image_path'],
                 'context': m['context'],
-                'caption_names': get_proper_nouns(m['caption'], nlp),
-                'generated_names': get_proper_nouns(generation, nlp),
+                'caption_names': get_proper_nouns(caption_doc),
+                'generated_names': get_proper_nouns(gen_doc),
+                'caption_entities': get_entities(caption_doc),
+                'generated_entities': get_entities(gen_doc),
                 'caption_readability': get_readability_scores(m['caption']),
                 'gen_readability': get_readability_scores(generation),
                 'caption_np': get_narrative_productivity(m['caption']),
@@ -186,13 +190,19 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
             f.write(f'{json.dumps(obj)}\n')
 
 
-def get_proper_nouns(text, nlp):
-    doc = nlp(text)
+def get_proper_nouns(doc):
     proper_nouns = []
     for token in doc:
         if token.pos_ == 'PROPN':
             proper_nouns.append(token.text)
     return proper_nouns
+
+
+def get_entities(doc):
+    entities = []
+    for ent in doc.ents:
+        entities.append(ent.text)
+    return entities
 
 
 def get_readability_scores(text):

### 2019-11-06 newser/commands/evaluate.py
Get context entities during evaluation

@@ -167,6 +167,7 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
             generation = generations[i]
             caption_doc = nlp(m['caption'])
             gen_doc = nlp(generation)
+            context_doc = nlp(m['context'])
             obj = {
                 'caption': caption,
                 'raw_caption': m['caption'],
@@ -176,8 +177,10 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
                 'context': m['context'],
                 'caption_names': get_proper_nouns(caption_doc),
                 'generated_names': get_proper_nouns(gen_doc),
+                'context_names': get_proper_nouns(context_doc),
                 'caption_entities': get_entities(caption_doc),
                 'generated_entities': get_entities(gen_doc),
+                'context_entities': get_entities(context_doc),
                 'caption_readability': get_readability_scores(m['caption']),
                 'gen_readability': get_readability_scores(generation),
                 'caption_np': get_narrative_productivity(m['caption']),
@@ -201,7 +204,11 @@ def get_proper_nouns(doc):
 def get_entities(doc):
     entities = []
     for ent in doc.ents:
-        entities.append(ent.text)
+        entities.append({
+            'text': ent.text,
+            'label': ent.label_,
+            'tokens': [{'text': tok.text, 'pos': tok.pos_} for tok in ent],
+        })
     return entities
 
 
@@ -239,6 +246,8 @@ def get_narrative_productivity(text):
         'summer': summer(n_terms, n_words),
         'maas': maas(n_terms, n_words),
     }
+
+    return scores
 
 
 def basic_ttr(n_terms, n_words):

### 2019-11-06 newser/commands/evaluate.py
Cache spacized text during evaluation

@@ -1,7 +1,9 @@
+import hashlib
 import json
 import logging
 import math
 import os
+import pickle
 import string
 from typing import Any, Dict, Iterable
 
@@ -20,6 +22,7 @@ from allennlp.nn import util as nn_util
 from allennlp.nn.util import move_to_device
 from allennlp.training.util import HasBeenWarned, datasets_from_params
 from nltk.tokenize import word_tokenize
+from spacy.tokens import Doc
 
 from .train import yaml_to_params
 
@@ -90,6 +93,18 @@ def evaluate(model: Model,
     nlp = spacy.load("en_core_web_lg")
     assert not os.path.exists(os.path.join(
         serialization_dir, f'generations{eval_suffix}.jsonl'))
+
+    # caching saves us extra 30 minutes
+    if 'goodnews' in serialization_dir:
+        cache_path = 'data/goodnews/evaluation_cache.pkl'
+    elif 'nytimes' in serialization_dir:
+        cache_path = 'data/nytimes/evaluation_cache.pkl'
+    if os.path.exists(cache_path):
+        with open(cache_path, 'rb') as f:
+            cache = pickle.load(f)
+    else:
+        cache = {}
+
     with torch.no_grad():
         model.eval()
 
@@ -115,7 +130,8 @@ def evaluate(model: Model,
             output_dict = model(**batch)
             loss = output_dict.get("loss")
 
-            write_to_json(output_dict, serialization_dir, nlp, eval_suffix)
+            write_to_json(output_dict, serialization_dir,
+                          nlp, eval_suffix, cache)
 
             metrics = model.get_metrics()
 
@@ -148,10 +164,14 @@ def evaluate(model: Model,
             #                        "produced a loss!")
             final_metrics["loss"] = total_loss / total_weight
 
-        return final_metrics
+    if not os.path.exists(cache_path):
+        with open(cache_path, 'wb') as f:
+            pickle.dump(cache, f)
+
+    return final_metrics
 
 
-def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
+def write_to_json(output_dict, serialization_dir, nlp, eval_suffix, cache):
     if 'captions' not in output_dict:
         return
 
@@ -165,9 +185,9 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix):
         for i, caption in enumerate(captions):
             m = metadatas[i]
             generation = generations[i]
[…]

### 2019-11-06 newser/data/dataset_readers/nytimes_copy_matched.py
Ensure named_entities key exists

@@ -274,8 +274,9 @@ class NYTimesCopyMatchedReader(DatasetReader):
                 offset += len(par) + 1
 
     def is_in_ner(self, text, section):
-        ners = section['named_entities']
-        for ner in ners:
-            if text in ner['text']:
-                return True
+        if 'named_entities' in section:
+            ners = section['named_entities']
+            for ner in ners:
+                if text in ner['text']:
+                    return True
         return False

### 2019-11-06 newser/data/dataset_readers/goodnews_face_ner_matched.py
Parametrize n_faces

@@ -50,6 +50,7 @@ class GoodNewsFaceNERMatchedReader(DatasetReader):
                  mongo_port: int = 27017,
                  eval_limit: int = 5120,
                  use_caption_names: bool = True,
+                 n_faces: int = None,
                  lazy: bool = True) -> None:
         super().__init__(lazy)
         self._tokenizer = tokenizer
@@ -63,6 +64,7 @@ class GoodNewsFaceNERMatchedReader(DatasetReader):
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
         self.eval_limit = eval_limit
         self.use_caption_names = use_caption_names
+        self.n_faces = n_faces
         random.seed(1234)
         self.rs = np.random.RandomState(1234)
 
@@ -102,7 +104,9 @@ class GoodNewsFaceNERMatchedReader(DatasetReader):
 
             named_entities = sorted(self._get_named_entities(article))
 
-            if self.use_caption_names:
+            if self.n_faces is not None:
+                n_persons = self.n_faces
+            elif self.use_caption_names:
                 n_persons = len(self._get_person_names(
                     article, sample['image_index']))
             else:

### 2019-11-06 newser/data/dataset_readers/nytimes_faces_ner_matched.py

@@ -56,6 +56,7 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
                  mongo_host: str = 'localhost',
                  mongo_port: int = 27017,
                  use_caption_names: bool = True,
+                 n_faces: int = None,
                  lazy: bool = True) -> None:
         super().__init__(lazy)
         self._tokenizer = tokenizer
@@ -67,13 +68,13 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
             ToTensor(),
             Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
         self.use_caption_names = use_caption_names
+        self.n_faces = n_faces
         random.seed(1234)
         self.rs = np.random.RandomState(1234)
 
         roberta = torch.hub.load('pytorch/fairseq', 'roberta.base')
         self.bpe = roberta.bpe
         self.indices = roberta.task.source_dictionary.indices
-
 
     @overrides
     def _read(self, split: str):
@@ -118,7 +119,9 @@ class NYTimesFacesNERMatchedReader(DatasetReader):
                 if not caption:
                     continue
 
-                if self.use_caption_names:
+                if self.n_faces is not None:
+                    n_persons = self.n_faces
+                elif self.use_caption_names:
                     n_persons = len(self._get_person_names(sections[pos]))
                 else:
                     n_persons = 4

### 2019-11-06 newser/models/transformer_pointer.py
Update pointer generator evaluation code

@@ -174,12 +174,25 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
         if not torch.isnan(copy_loss):
             self.batch_history['copy_loss'] += copy_loss.item()
 
+        output_dict = {
+            'loss': loss,
+            'sample_size': sample_size,
+        }
+
         # During evaluation, we will generate a caption and compute BLEU, etc.
         if not self.training and self.evaluate_mode:
-            log_probs, copy_probs, should_copy_probs, gen_ids = self._generate(
+            log_probs, copy_probs, should_copy_mask, gen_ids = self._generate(
                 caption_ids, contexts, X_sections_hiddens, article_padding_mask, context)
             gen_texts = [self.roberta.decode(x[x > 1]) for x in gen_ids.cpu()]
             captions = [m['caption'] for m in metadata]
+
+            copied_texts = [self.roberta.decode(x[should_copy_mask[i]])
+                            for i, x in enumerate(gen_ids.cpu())]
+
+            output_dict['captions'] = captions
+            output_dict['generations'] = gen_texts
+            output_dict['metadata'] = metadata
+            output_dict['copied_texts'] = copied_texts
 
             # Remove punctuation
             gen_texts = [re.sub(r'[^\w\s]', '', t) for t in gen_texts]
@@ -194,17 +207,12 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
                 self.sample_history['bleu-3'] += score[2] * 100
                 self.sample_history['bleu-4'] += score[3] * 100
 
-                rogue_scorer = Rouge()
-                score = rogue_scorer.calc_score([gen], [ref])
-                self.sample_history['rogue'] += score * 100
+                # rogue_scorer = Rouge()
+                # score = rogue_scorer.calc_score([gen], [ref])
+                # self.sample_history['rogue'] += score * 100
 
         self.n_samples += caption_ids.shape[0]
         self.n_batches += 1
-
-        output_dict = {
-            'loss': loss,
-            'sample_size': sample_size,
-        }
 
         return output_dict
 
@@ -483,6 +491,8 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
         X_article = X_article.transpose(0, 1)
         # X_article.shape == [seq_len, batch_size, embed_size]
 
+        Xs = []
+
         for i in range(gen_len):
             if i == 0:
[…]

### 2019-11-07 newser/commands/evaluate.py
Avoid taking log of 0

@@ -325,7 +325,7 @@ def summer(n_terms, n_words):
         w is the total number of words.
         (Summer 1966)
     """
-    if n_words <= 1:
+    if n_words <= 1 or n_terms == 0:
         return 0
     return math.log(math.log(n_terms)) / math.log(math.log(n_words))
 

### 2019-11-07 paper/paper.tex
Update results

@@
    describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
+   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
    outperforming the previous state-of-art CIDEr of 13. We also introduce the
@@
       RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      RoBERTa + Transformer & 22.7 & 13.7 & 8.93 & 6.17 & 21.4 & 10.3 & 53.9 \\
+      RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
 		\bottomrule
@@
       RoBERTa + LSTM & 23.4\% & 28.8\%  \\
-      RoBERTa + Transformer & 29.8\% & 34.4\%  \\
+      RoBERTa + Transformer & 29.5\% & 33.9\%  \\
 		\bottomrule
@@
       RoBERTa + LSTM & 14.7 & 12.7  \\
-      RoBERTa + Transformer & 15.7 & 13.8 \\
+      RoBERTa + Transformer & 15.5 & 13.7 \\
 		\bottomrule
@@
       RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
-      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
-      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
+      Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
+      Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
       \\
@@
       RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
-      Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
-      Transformer (location-aware) & 31.5\% & 36.8\% & 25.3\% & 33.2\% & 23.5\% & 25.3\%   \\
+      Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
+      Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
 		\bottomrule
@@
       RoBERTa + LSTM  & 15.6 & 13.4 \\
-      Transformer (first 512 tokens)  & 13.1 & 11.7 \\
-      Transformer (location-aware) & 13.0 & 11.7  \\
+      Transformer (first 512 tokens)  & 15.3 & 13.6 \\
+      Transformer (location-aware) & 15.1 & 13.5  \\
 		\bottomrule

### 2019-11-07 newser/commands/evaluate.py
fixup! Avoid taking log of 0

@@ -325,9 +325,10 @@ def summer(n_terms, n_words):
         w is the total number of words.
         (Summer 1966)
     """
-    if n_words <= 1 or n_terms == 0:
+    try:
+        math.log(math.log(n_terms)) / math.log(math.log(n_words))
+    except ValueError:
         return 0
-    return math.log(math.log(n_terms)) / math.log(math.log(n_words))
 
 
 def maas(n_terms, n_words):

### 2019-11-07 newser/models/transformer_pointer.py
Avoid optimizing generation loss

@@ -165,7 +165,7 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
         entity_loss = entity_loss / math.log(2)
         copy_loss = copy_loss / math.log(2)
 
-        loss = gen_loss + entity_loss + copy_loss
+        loss = entity_loss + copy_loss
 
         if not torch.isnan(gen_loss):
             self.batch_history['gen_loss'] += gen_loss.item()

### 2019-11-07 newser/commands/evaluate.py
Save copied texts during evaluation

@@ -178,6 +178,10 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix, cache):
     captions = output_dict['captions']
     generations = output_dict['generations']
     metadatas = output_dict['metadata']
+    if 'copied_texts' in output_dict:
+        copied_texts = output_dict['copied_texts']
+    else:
+        copied_texts = ['' for _ in range(len(captions))]
 
     out_path = os.path.join(
         serialization_dir, f'generations{eval_suffix}.jsonl')
@@ -192,6 +196,7 @@ def write_to_json(output_dict, serialization_dir, nlp, eval_suffix, cache):
                 'caption': caption,
                 'raw_caption': m['caption'],
                 'generation': generation,
+                'copied_texts': copied_texts[i],
                 'web_url': m['web_url'],
                 'image_path': m['image_path'],
                 'context': m['context'],

### 2019-11-07 paper/paper.tex
Add reference to transformer theory

@@
    source code are available from
-   \href{https://github.com}{https://anonymized}.
+   \href{https://github.com}{https://github.com/anonymized-link}.
 \end{abstract}
@@
 \cite{Biten2019GoodNews} include real-life captions written by professional
-journalists. To the best of our knowledge, all existing models that are trained
-on these news datasets use template-based methods to insert named entities.
+journalists. However, all existing models that are trained on these news
+datasets use template-based methods to insert named entities.
 
@@
 training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language modeling.
+sequence-to-sequence architectures and language representation learning.
 
-The most successful family of models in natural language understanding and
-generation are the transformer networks, which consist of layers of
+The most successful family of models in the field of natural language
+processing (NLP) are the transformer networks, which consist of layers of
 self-attention and feed-forward connections stacked on top of each other
@@
 \cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
+There are theoretical justifications that transformers could be universal
+approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
 
@@
 diverse data inputs. The most significant contribution is the use of byte-pair
-encoding \cite{Sennrich2015NeuralMT} to handle an open vocabulary. This is done
-by representing a rare word as a sequence of subword units.
+encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
+sequence of subword units, thus giving models the ability to handle an open
+vocabulary.
 
@@
    important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the popular metrics such as BLEU, ROUGE,
+   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
    METEOR, and CIDEr; but also to other linguistic measures like readability

### 2019-11-08 paper/paper.tex
Work on related works

@@
 \usepackage{booktabs}
+\usepackage[export]{adjustbox} % adds a frame around figures
 
@@
 Most existing captioning systems can only generate a generic description of an
-image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
-Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
-because these architectures cannot handle an open vocabulary and early
-captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
-Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
-only visual cues present in the image. More recently, datasets such as TIME
-\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
-\cite{Biten2019GoodNews} include real-life captions written by professional
-journalists. However, all existing models that are trained on these news
-datasets use template-based methods to insert named entities.
+image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
+Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
+Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
+cannot handle an open vocabulary and early captioning datasets such as MS COCO
+\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
+\cite{Young2014FromID} were annotated using only visual cues present in the
+image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
+\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
+real-life captions written by professional journalists. However, existing
+models that are trained on these news datasets still need to rely on either
+extractive methods or templates to insert named entities.
 
@@
    \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-      %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
    \end{center}
-      \caption{An example caption.}
+      \caption{Our transformer model attends over embeddings from three
+      different domains (image patches, faces, and article text). Using
+      byte-pair encoding, the model can then directly produce a caption
+      containing specific named entities without the use of templates.}
    \label{fig:long}
@@
 
-Recent image captioning systems are based mostly on ``Show, Attend, Tell"
-\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
-improvements include giving the model the option to not attend to any image
-region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
-optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
-bottom-up approach to propose a region to attend to
+Early image captioning systems mainly used an RNN architecture with a closed
+vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
+Attention over image patches was later introduced in ``Show, Attend and Tell"
+\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
+image embeddings and the previous hidden state of the RNN through a multilayer
+perception. Later improvements include giving the model the option to not
+attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
+to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and
+using a bottom-up approach to propose a region to attend to
 \cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
@@
 A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. There are non-neural approaches
-\cite{Feng2013AutomaticCG,Tariq2017ACE}. Neural approaches include using the
-word2vec representation of the article and and the VGG19 representation of the
-image as context to the LSTM generator \cite{Ramisa2016BreakingNewsAA}.
+need to be able to generate entity names. Early non-neural approaches include
+extractive methods that use n-gram models to combine existing phrases
+\cite{Feng2013AutomaticCG} or simply retrieving the most representative
+sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
+\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
+article and and the VGG19 representation of the image, and feed them as inputs
+to an LSTM generator. However the generator still cannot produce names not
+seen in training.
 
-Biten \etal~\cite{Biten2019GoodNews} further refined this approach by
-developing a two-stage architecture to handle entity names. In the first stage,
-the model generates a template with placeholders such as PERSON and
-ORGANIZATION. In the second stage, the model finds the best matched sentence in
-the article and replace the placeholder with an entity mentioned in that
-sentence. They also created the ``GoodNews" dataset, which contains more
-samples than MSCOCO and BreakingNews
-\cite{Ramisa2016BreakingNewsAA} datasets.
+To overcome the limitation of a fixed-size vocabulary, template-based methods
+have been used to insert named entities. This involves first generating a
+template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
+DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
+for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
+for each combination of entities and select the most likely combination.
+Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
+benchmark against, picked the sentence with the highest cosine similarity with
+the template and then found the first entity that matches the type of each
+placeholder for insertion. Our proposed model differs from
+\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
+generate a caption with named entities directly without using any intermediate
+template.
 
-Zhu \etal \cite{Zhu2018CaptioningTW} used transformers to achieve competitive
-results on the MSCOCO dataset. Li \etal \cite{Li2019Boosted} added attention
-over image regions and semantic concepts using Faster-RCNN
-\cite{Ren2015FasterRCNN}. Both of these works, however, used the MSCOCO dataset
-which contains generic captions with no named entities.
+Transformers are still scarcely used in image captioning. They have been shown
+to yield competitive results in generating generic MS COCO captions
+\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
+\cite{Zhao2019InformativeIC} have gone further and train transformers to
+produce named entities in the Conceptual Captions dataset
+\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
+context apart from the image itself, and the authors use web-entity labels,
+extracted using Google Cloud Vision API, as inputs to the model. In our work,
+we are more ambitious in that we do not explicitly give the model a list of
+entities that should appear in the caption. Instead the model has to determine
+which entities to generate on its own by scanning through and attending to the
+article.
 
-Wang \etal \cite{Wang2019Hierarchical} examined different strategies of
-combining embeddings from three modalities: concept terms, object regions,
-and image patches. These strategies include addition, concatenation, and
-multivariate residual modules.
+BPE offers an elegant solution to handle an open vocabulary. To date the only
+image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
+their data preprocessing step, they explicitly removed rare named entities from
+the captions. Thus no study has been done yet to see how well BPE used in
+transformers can generate rare names.
+
+In addition to attending to image patches, some captioning models attend to
+objects \cite{Wang2019Hierarchical} and concept terms
+\cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
+image itself. When attending to more than one modality, there are various
+strategies on how to combine embeddings such as addition, concatenation, and
+using multivariate residual modules \cite{Wang2019Hierarchical}.
 
 \section{Datasets}
-
-\begin{table}[t]
-	\caption {Summary of datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabular}{llll}
-		\toprule
-		  & GoodNews  & GoodNews+ &   NYTimes+ \\
-		\midrule
-      No. of articles & 241 808 & 241 808 & 445 828 \\
-      No. of images   & 462 642 & 440 112 & 794 085 \\
-      Article length & 451 & 963 & 974 \\
-      Caption length & 18 & 18 & 18 \\
-      Start month & Jan 10 & Jan 10 & Mar 05\\
-      End month & Jul 18 & Jul 18 & Sep 19 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning. As part of the quality check, we also
-reconstruct the same dataset on our own. We use the New York Times API and
-write a custom parser to recollect and extract all the articles and images in
-the same period as GoodNews from the original source. We call this GoodNews+.
-We were able to crawl all the original articles, but the number of images is
-slightly less, either due to dead links or not crawling images unrelated to the
-main article. GoodNews+ allows us to make the following observations about the
-original GoodNews dataset:
+dataset on news image captioning \cite{Biten2019GoodNews}. As part of the
+quality check, we also reconstruct the same dataset on our own. We use the New
+York Times API and write a custom parser to recollect and extract all the
+articles and images in the same period as GoodNews from the original source. We
+call this GoodNews+. We were able to crawl all the original articles, but the
+number of images is slightly less, either due to dead links or not crawling
+images unrelated to the main article. GoodNews+ allows us to make the following
+observations about the original GoodNews dataset:
 
@@
 A summary of the datasets is shown in Table \ref{tab:datasets}.
+
+\begin{table}[h]
+	\caption {Summary of datasets}
+	\label{tab:datasets}
+	\centering
+	\begin{tabular}{llll}
+		\toprule
+		  & GoodNews  & GoodNews+ &   NYTimes+ \\
+		\midrule
+      No. of articles & 241 808 & 241 808 & 445 828 \\
+      No. of images   & 462 642 & 440 112 & 794 085 \\
+      Article length & 451 & 963 & 974 \\
+      Caption length & 18 & 18 & 18 \\
+      Start month & Jan 10 & Jan 10 & Mar 05\\
+      End month & Jul 18 & Jul 18 & Sep 19 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 

### 2019-11-09 paper/paper.tex
Update NYTimes+ GloVe + LSTM results

@@
    \end{center}
-      \caption{Our transformer model attends over embeddings from three
-      different domains (image patches, faces, and article text). Using
-      byte-pair encoding, the model can then directly produce a caption
-      containing specific named entities without the use of templates.}
+      \caption{Our transformer model attends to embeddings from three different
+      domains (image patches, faces, and article text). Using byte-pair
+      encoding, the model can then directly produce a caption containing
+      specific named entities without the use of templates.}
    \label{fig:long}
@@
 
-BPE offers an elegant solution to handle an open vocabulary. To date the only
+BPE offers an elegant solution to handling an open vocabulary. To date the only
 image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
 their data preprocessing step, they explicitly removed rare named entities from
-the captions. Thus no study has been done yet to see how well BPE used in
-transformers can generate rare names.
+the captions. We attempt to fill this gap and in particular examine how much
+better BPE can generate rare names compared to template-based methods.
 
-In addition to attending to image patches, some captioning models attend to
-objects \cite{Wang2019Hierarchical} and concept terms
+In addition to attending to image patches, some captioning models also attend
+to objects \cite{Wang2019Hierarchical} and concept terms
 \cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
@@
 quality check, we also reconstruct the same dataset on our own. We use the New
-York Times API and write a custom parser to recollect and extract all the
-articles and images in the same period as GoodNews from the original source. We
-call this GoodNews+. We were able to crawl all the original articles, but the
-number of images is slightly less, either due to dead links or not crawling
-images unrelated to the main article. GoodNews+ allows us to make the following
+York Times
+API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}
+and write a custom parser to recollect and extract all the articles and images
+in the same period as GoodNews from the original source. We call this
+GoodNews+. We were able to crawl all the original articles, but the number of
+images is slightly less, either due to dead links or not crawling images
+unrelated to the main article. GoodNews+ allows us to make the following
 observations about the original GoodNews dataset:
@@
       \midrule
-      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
+      GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
       GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
@@
       \midrule
-      GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
+      GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
       GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
@@
       Ground Truths & 18.4 & 17.1 \\
-      GloVe + LSTM  & 15.3 & 12.3 \\
+      GloVe + LSTM  & 13.8 & 11.8 \\
       GloVe + Transformer  & 15.1 & 12.9 \\

### 2019-11-09 scripts/compute_data_statistics.py
Compute more data stats

@@ -8,13 +8,12 @@ Options:
 
 """
 import os
+import pickle
+from collections import defaultdict
 from datetime import datetime
-from glob import glob
 
 import ptvsd
-import torchvision.transforms.functional as F
 from docopt import docopt
-from PIL import Image
 from pymongo import MongoClient
 from schema import And, Or, Schema, Use
 from tqdm import tqdm
@@ -25,16 +24,27 @@ logger = setup_logger()
 
 
 def compute_nytimes_stats(nytimes):
-    cursor = nytimes.articles.find({
-        'parsed': True,  # article body is parsed into paragraphs
-        'n_images': {'$gt': 0},  # at least one image is present
-        'language': 'en',
-    })
+    projection = ['_id', 'parsed_section.type', 'pub_date',
+                  'parsed_section.parts_of_speech',
+                  'parsed_section.named_entities',
+                  'parsed_section.hash', 'parsed_section.text']
+    cursor = nytimes.articles.find({}, projection=projection)
 
     n_article_words = 0
     n_caption_words = 0
     n_captions = 0
     n_articles = 0
+
+    n_words = 0
+    n_nouns = 0
+    n_adjs = 0
+    n_verbs = 0
+    n_pnouns = 0
+    n_propers = 0
+    n_entity_words = 0
+    n_ent_sents = 0
+    n_person_names = 0
+    n_pers_sents = 0
 
     max_date = datetime(2000, 1, 1)
     min_date = datetime(2020, 1, 1)
@@ -49,8 +59,31 @@ def compute_nytimes_stats(nytimes):
             if s['type'] == 'caption':
                 image_path = os.path.join('data/nytimes/images_processed',
                                           f"{s['hash']}.jpg")
-                if os.path.exists(image_path):
-                    captions.append(s['text'])
+                if not os.path.exists(image_path):
+                    continue
+                captions.append(s['text'])
+
+                if 'parts_of_speech' in s:
+                    pos = s['parts_of_speech']
+                    n_words += len(pos)
+                    n_nouns += len([1 for p in pos if p['pos'] == 'NOUN'])
+                    n_verbs += len([1 for p in pos if p['pos'] == 'VERB'])
+                    n_adjs += len([1 for p in pos if p['pos'] == 'ADJ'])
+                    n_pnouns += len([1 for p in pos if p['pos'] == 'PRON'])
+                    n_propers += len([1 for p in pos if p['pos'] == 'PROPN'])
+
[…]

### 2019-11-09 paper/paper.tex
Work on datasets section

@@
    outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes+ dataset, the largest news image captioning dataset to date.
-   NYTimes+ is an extended version of GoodNews with higher-quality articles and
+   NYTimes800k dataset, the largest news image captioning dataset to date.
+   NYTimes800k is an extended version of GoodNews with higher-quality articles and
    metadata that allow us to study the importance of the image location within
-   the text. On NYTimes+, we achieve a CIDEr of 51. Pretrained models and
+   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
    source code are available from
@@
 \begin{enumerate}
-   \item We introduce NYTimes+, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from the New
-   York Times spanning 14 years. NYTimes+ is built upon the GoodNews dataset,
+   \item We introduce NYTimes800k, the largest news image captioning dataset to
+   date, containing 446K articles and 794K images with captions from The New
+   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
    but we write a custom parser to collect higher-quality articles and metadata
@@
 attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and
-using a bottom-up approach to propose a region to attend to
-\cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
-captions with a limited vocabulary.
+to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
+Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
+attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
+generic captions with a limited vocabulary.
 
@@
 \cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and train transformers to
+\cite{Zhao2019InformativeIC} have gone further and trained transformers to
 produce named entities in the Conceptual Captions dataset
 \cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors use web-entity labels,
+context apart from the image itself, and the authors used web-entity labels,
 extracted using Google Cloud Vision API, as inputs to the model. In our work,
@@
 entities that should appear in the caption. Instead the model has to determine
-which entities to generate on its own by scanning through and attending to the
+on its own which entities to generate by scanning through and attending to the
 article.
@@
 In addition to attending to image patches, some captioning models also attend
-to objects \cite{Wang2019Hierarchical} and concept terms
-\cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
-image itself. When attending to more than one modality, there are various
-strategies on how to combine embeddings such as addition, concatenation, and
-using multivariate residual modules \cite{Wang2019Hierarchical}.
+to object regions \cite{Wang2019Hierarchical} and visual concepts
+\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
+derived from the image itself. When attending to more than one modality, there
+are various strategies on how to combine embeddings such as addition,
+concatenation, and using multivariate residual modules (MRMs)
+\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
+more complex strategies such as MRMs have shown to yield only minor improvement
+\cite{Wang2019Hierarchical}.
 
@@
 
-\subsection{GoodNews and GoodNews+}
+\subsection{GoodNews}
 
 As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. As part of the
-quality check, we also reconstruct the same dataset on our own. We use the New
-York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}
-and write a custom parser to recollect and extract all the articles and images
-in the same period as GoodNews from the original source. We call this
-GoodNews+. We were able to crawl all the original articles, but the number of
-images is slightly less, either due to dead links or not crawling images
-unrelated to the main article. GoodNews+ allows us to make the following
-observations about the original GoodNews dataset:
+dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
+dataset is a triplet containing an article, an image, and a caption. Since only
+the article text and captions were publicly released, we had to crawl the
+images ourselves. Out of the 466K image URLs provided by
+\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
+original dataset. The remaining are broken links. As part of the quality check,
+we also wrote a custom parser to re-extract the articles in the same period
+from the original web pages, with the help of The New York Times
+API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
 
-\begin{itemize}
-   \item The average length of an article in GoodNews is 451 words, while it is
-         963 words in GoodNews+. Thus half of the article body is missing in
-         GoodNews. This includes the first few paragraphs that might contain
-         important information about the top caption. Looking through the
-         publicly released code, we found that this is because the original
-         parser used by \cite{Biten2019GoodNews} fails to recognize certain
-         HTML tags used in New York Times web pages.
-   \item GoodNews contains X Spanish articles, adding unwanted noise to the
-         training.
-   \item GoodNews sometimes include images from the recommendation sidebar,
-         which are not part of the main article.
-\end{itemize}
+From the recollection, we observe that the average length of an article in
+GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
+the article body is missing in GoodNews. This includes the first few paragraphs
+that might contain important information about the top caption. Looking through
+the publicly released code, we found that this is because the original parser
+used by \cite{Biten2019GoodNews} was designed to extract articles from a
+generic online news source and it fails to recognize certain HTML tags used
+specifically in New York Times web pages.
 
-Despite the above limitation, we will use the original GoodNews dataset in our
-experiments, along with the original train-validation-test split to make
+In addition, we also found some noisy samples in GoodNews. This includes a
+small number of non-English articles, and captioned images from the
+recommendation sidebar which are not related to the main article.
+
+Despite the above limitations, we still use the original GoodNews dataset in
+our experiments, along with the original train-validation-test split, to make
 comparison to previous works easier.
 
-\subsection{NYTimes+}
+% \begin{table}[t]
+% 	\caption {Summary of datasets}
+% 	\label{tab:datasets}
+% 	\centering
+% 	\begin{tabular}{llll}
+% 		\toprule
+% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
+% 		\midrule
+%       No. of articles & 241 808 & 241 808 & 445 828 \\
+%       No. of images   & 462 642 & 440 112 & 794 085 \\
+%       Article length & 451 & 963 & 974 \\
+%       Caption length & 18 & 18 & 18 \\
+%       Start month & Jan 10 & Jan 10 & Mar 05\\
+%       End month & Jul 18 & Jul 18 & Sep 19 \\
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table}
 
-At the same time, we also construct a new dataset, which we call NYTimes+.
-NYTimes+ exhibits several advantages over GoodNews:
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes+ contains 80\% more articles and images, thus
-   becoming the largest news captioning dataset.
-   \item NYTimes+ contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item In addition to having a more complete coverage, we also collect
-   information about the image position in each article. As shown in Figure
-   \ref{fig:dist}, about 40\% of the articles have two or more images.
-\end{itemize}
-
-A summary of the datasets is shown in Table \ref{tab:datasets}.
-
-\begin{table}[h]
-	\caption {Summary of datasets}
+\begin{table}[t]
+	\caption {Summary of news captioning datasets}
 	\label{tab:datasets}
 	\centering
-	\begin{tabular}{llll}
+	\begin{tabular}{lll}
 		\toprule
-		  & GoodNews  & GoodNews+ &   NYTimes+ \\
+		  & GoodNews  &   NYTimes800k \\
 		\midrule
-      No. of articles & 241 808 & 241 808 & 445 828 \\
-      No. of images   & 462 642 & 440 112 & 794 085 \\
-      Article length & 451 & 963 & 974 \\
-      Caption length & 18 & 18 & 18 \\
-      Start month & Jan 10 & Jan 10 & Mar 05\\
-      End month & Jul 18 & Jul 18 & Sep 19 \\
+      Number of articles & 257 033 & 445 828 \\
+      Number of images   & 462 642 & 794 085 \\
+      Average article length & 451 & 974 \\
+      Average caption length & 18 & 18 \\
+      Collection start month & Jan 10 & Mar 05\\
+      Collection end month & Mar 18 & Sep 19 \\
+      \midrule
+      \% of words that are \\
+      \quad -- nouns & 16\% & 16\% \\
+      \quad -- pronouns & 1\% & 1\% \\
+      \quad -- proper nouns & 23\% & 22\% \\
+      \quad -- verbs & 9\% & 9\%  \\
+      \quad -- adjectives & 4\% & 4\% \\
+      \quad -- named entities & 27\% & 26\% \\
+      \quad -- person names & 9\% & 9\% \\
+      \midrule
+      \% of captions with \\
+      \quad -- named entities & 97\% & 97\% \\
+      \quad -- person names & 68\% & 68\% \\
 		\bottomrule
@@
 
+\subsection{NYTimes800k}
+
+At the same time, we also constructed a bigger and higher-quality dataset,
+which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
+summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
+advantages:
+
+\begin{itemize}
+   \item By increasing the collection period to the last 14 years (March 2005
+   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
+   becoming the largest news image captioning dataset.
+   \item Using our custom parser, articles in NYTimes800k contain the full text
+   with no missing paragraphs.
+   \item NYTimes800k contains only English articles.
+   \item We are careful to include only images that are part of the main
+   article.
+   \item Unlike GoodNews, we also collect information about the image position
+   in each article. Most news articles have one image at the top that relates
+   to the key topic. However 39\% of the articles have at least one more image
+   somewhere in the middle of text. The image placement and hence the text
+   surrounding the image could be important information for captioning.
+\end{itemize}
+
+Named entities play an important role in the dataset, with 97\% of captions
+containing at least one named entity. As shown in Figure \ref{fig:entity_dist},
+the most popular entity type are person names, with 68\% of the captions
+mentioning at least one person.
+
+Rare names
+
 \begin{figure}[t]
    \begin{center}
-   \includegraphics[width=0.8\linewidth]{figures/caption_dist.png}
+   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
    \end{center}
-      \caption{Distribution of images across articles.}
-   \label{fig:dist}
+      \caption{Distribution of entity types in NYTimes800k training captions.}
+   \label{fig:entity_dist}
    \end{figure}
@@
 dataset. Table \ref{tab:results-nytimes} shows additional results done on
-our NYTimes+ dataset.
+our NYTimes800k dataset.
 
@@
 \begin{table*}[t]
-	\caption {Results on the NYTimes+ test set}
+	\caption {Results on the NYTimes800k test set}
 	\label{tab:results-nytimes}
@@
 \begin{table*}[t]
-	\caption {Proper name metrics on the NYTimes+ test set}
+	\caption {Proper name metrics on the NYTimes800k test set}
 	\label{tab:results-names}
@@
 \begin{table*}[t]
-	\caption {Word statistics on the NYTimes+ test set}
+	\caption {Word statistics on the NYTimes800k test set}
 	\label{tab:results-stats}

### 2019-11-10 scripts/compute_data_statistics.py
Compute face stats

@@ -285,6 +285,56 @@ def compute_goodnews_stats(goodnews):
     print()
 
 
+def compute_face_stats(nytimes):
+    projection = ['_id', 'n_images', 'n_images_with_faces', 'image_positions',
+                  'detected_face_positions', 'parsed_section.facenet_details',
+                  'parsed_section.named_entities']
+    cursor = nytimes.articles.find({'split': 'train'}, projection=projection)
+
+    n_images_with_faces = 0
+    n_images = 0
+    n_articles = 0
+    n_articles_with_faces = 0
+    face_count = defaultdict(int)
+    name_count = defaultdict(int)
+
+    for article in tqdm(cursor):
+        n_images += article['n_images']
+        n_articles += 1
+
+        if 'n_images_with_faces' in article and article['n_images_with_faces']:
+            n_images_with_faces += article['n_images_with_faces']
+            n_articles_with_faces += 1
+
+        if 'detected_face_positions' not in article:
+            continue
+
+        for pos in article['detected_face_positions']:
+            section = article['parsed_section'][pos]
+            if 'facenet_details' in section:
+                n_faces = section['facenet_details']['n_faces']
+                face_count[n_faces] += 1
+
+        for pos in article['image_positions']:
+            section = article['parsed_section'][pos]
+            if 'named_entities' in section:
+                c = 0
+                for ner in section['named_entities']:
+                    if ner['label'] == 'PERSON':
+                        c += 1
+                name_count[c] += 1
+
+    print('No of images with faces:', n_images_with_faces)
+    print('No of images:', n_images)
+    print('No of articles:', n_articles)
+    print('No of articles with faces:', n_articles_with_faces)
+    print('Face count:')
+    print(face_count)
+    print('Name count:')
+    print(name_count)
+    print()
+
+
 def validate(args):
     """Validate command line arguments."""
     args = {k.lstrip('-').lower().replace('-', '_'): v
@@ -309,9 +359,10 @@ def main():
     nytimes = client.nytimes
     goodnews = client.goodnews
 
-    compute_goodnews_stats(goodnews)
-    compute_nytimes_stats(nytimes)
-    compute_nytimes_exact_subset_statistics(nytimes, goodnews)
+    # compute_goodnews_stats(goodnews)
+    # compute_nytimes_stats(nytimes)
+    # compute_nytimes_exact_subset_statistics(nytimes, goodnews)
+    compute_face_stats(nytimes)
 
 
 if __name__ == '__main__':

### 2019-11-10 paper/paper.tex
Work on describing NYTimes800k

@@
 our experiments, along with the original train-validation-test split, to make
-comparison to previous works easier.
+comparison to previous works easier. In the original split, the dataset was
+randomly divided into...
 
@@
       \quad -- named entities & 27\% & 26\% \\
-      \quad -- person names & 9\% & 9\% \\
+      \quad -- personal names & 9\% & 9\% \\
       \midrule
@@
       \quad -- named entities & 97\% & 97\% \\
-      \quad -- person names & 68\% & 68\% \\
+      \quad -- personal names & 68\% & 68\% \\
 		\bottomrule
@@
 
+\begin{figure}[t]
+   \begin{center}
+   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
+   \end{center}
+      \caption{Entity distribution in NYTimes800k training captions. The four
+               most common entity types are personal names, geopolitical
+               entities, organizations, and dates.}
+   \label{fig:entities}
+\end{figure}
+
+\begin{figure}[t]
+   \begin{center}
+   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
+   \end{center}
+      \caption{Co-occurrence of faces and personal names in NYTimes800k
+               training data. The blue bars count how many images containing a
+               certain number of faces. The orange bars count how many captions
+               containing a certain number of personal names.}
+   \label{fig:faces}
+\end{figure}
+
 \begin{itemize}
@@
    article.
-   \item Unlike GoodNews, we also collect information about the image position
-   in each article. Most news articles have one image at the top that relates
-   to the key topic. However 39\% of the articles have at least one more image
-   somewhere in the middle of text. The image placement and hence the text
-   surrounding the image could be important information for captioning.
+   \item Unlike GoodNews, we also collect information about where an image is
+   located in the corresponding article. Most news articles have one image at
+   the top that relates to the key topic. However 39\% of the articles have at
+   least one more image somewhere in the middle of text. The image placement
+   and hence the text surrounding the image could be important information for
+   captioning.
 \end{itemize}
 
-Named entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entity_dist},
-the most popular entity type are person names, with 68\% of the captions
-mentioning at least one person.
+Entities play an important role in the dataset, with 97\% of captions
+containing at least one named entity. As shown in Figure \ref{fig:entities},
+the most popular entity type are personal names, comprising a third of all
+named entities. Furthermore, 71\% of training images contain at least one face
+and 68\% of training captions mention at least one personal name. Figure
+\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
+personal names. One important observation is that the majority of captions
+contain at most four names.
 
-Rare names
+\begin{table}[t]
+	\caption {NYTimes800k training, validation, and test splits}
+	\label{tab:splits}
+	\centering
+	\begin{tabular}{llll}
+		\toprule
+		  & Training  &   Validation & Test \\
+		\midrule
+      Number of articles & &  \\
+      Number of images   &  &  \\
+      Start month &  & \\
+      End month &  & \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Distribution of entity types in NYTimes800k training captions.}
-   \label{fig:entity_dist}
-   \end{figure}
+In order to study how rare names are generated, we split the training,
+validation, and test sets by time. The training set consists of 434K articles
 

### 2019-11-10 scripts/compute_data_statistics.py
Compute split statistics

@@ -24,16 +24,20 @@ logger = setup_logger()
 
 
 def compute_nytimes_stats(nytimes):
-    projection = ['_id', 'parsed_section.type', 'pub_date',
+    projection = ['_id', 'parsed_section.type', 'pub_date', 'split',
                   'parsed_section.parts_of_speech',
                   'parsed_section.named_entities',
                   'parsed_section.hash', 'parsed_section.text']
-    cursor = nytimes.articles.find({}, projection=projection)
+    cursor = nytimes.articles.find(
+        {'split': {'$in': ['train', 'valid', 'test']}},
+        projection=projection)
 
     n_article_words = 0
     n_caption_words = 0
     n_captions = 0
     n_articles = 0
+    article_splits = defaultdict(int)
+    caption_splits = defaultdict(int)
 
     n_words = 0
     n_nouns = 0
@@ -91,6 +95,8 @@ def compute_nytimes_stats(nytimes):
         n_articles += 1
         n_caption_words += len(' '.join(captions).split())
         n_captions += len(captions)
+        caption_splits[article['split']] += len(captions)
+        article_splits[article['split']] += 1
 
         if article['pub_date'] < min_date:
             min_date = article['pub_date']
@@ -114,6 +120,8 @@ def compute_nytimes_stats(nytimes):
     print(f'Entity sents: {n_ent_sents} ({n_ent_sents / n_captions:.2%})')
     print(f'Person names: {n_person_names} ({n_person_names / n_words:.2%})')
     print(f'Person sents: {n_pers_sents} ({n_pers_sents / n_captions:.2%})')
+    print('Caption splits:', caption_splits)
+    print('Article splits:', article_splits)
     print()
 
 
@@ -202,6 +210,7 @@ def compute_nytimes_exact_subset_statistics(nytimes, goodnews):
 def compute_goodnews_stats(goodnews):
     cursor = goodnews.splits.find({})
     article_ids = set({})
+    split_ids = defaultdict(set)
     n_article_words = 0
     n_caption_words = 0
     n_captions = 0
@@ -219,7 +228,9 @@ def compute_goodnews_stats(goodnews):
     n_person_names = 0
     n_pers_sents = 0
 
-    projection = ['_id', 'article', 'language', 'images',
+    caption_splits = defaultdict(int)
+
+    projection = ['_id', 'article', 'language', 'images', 'split',
                   'caption_parts_of_speech', 'caption_ner']
 
[…]

### 2019-11-10 scripts/compute_data_statistics.py
Compute rare noun statistics

@@ -358,6 +358,49 @@ def compute_face_stats(nytimes):
     print()
 
 
+def compute_rare_stats(nytimes):
+    projection = ['_id', 'parsed_section.type', 'parsed_section.hash',
+                  'parsed_section.parts_of_speech']
+    cursor = nytimes.articles.find({'split': 'test'}, projection=projection)
+
+    path = './data/nytimes/name_counters.pkl'
+    with open(path, 'rb') as f:
+        name_counters = pickle.load(f)
+
+    full_counter = name_counters['caption'] + name_counters['context']
+
+    n_words = 0
+    n_propers = 0
+    n_rare_propers = 0
+    n_very_rare_propers = 0
+
+    for article in tqdm(cursor):
+        sections = article['parsed_section']
+        for s in sections:
+            if s['type'] == 'caption':
+                image_path = os.path.join('data/nytimes/images_processed',
+                                          f"{s['hash']}.jpg")
+                if not os.path.exists(image_path):
+                    continue
+
+                if 'parts_of_speech' in s:
+                    pos = s['parts_of_speech']
+                    n_words += len(pos)
+                    for p in pos:
+                        if p['pos'] == 'PROPN':
+                            n_propers += 1
+                            if p['text'] not in name_counters['caption']:
+                                n_rare_propers += 1
+                            if p['text'] not in full_counter:
+                                n_very_rare_propers += 1
+
+    print('No of words', n_words)
+    print('No of proper nouns', n_propers)
+    print('No of rare proper nouns', n_rare_propers)
+    print('No of very rare proper nouns', n_very_rare_propers)
+    print()
+
+
 def validate(args):
     """Validate command line arguments."""
     args = {k.lstrip('-').lower().replace('-', '_'): v
@@ -383,9 +426,10 @@ def main():
     goodnews = client.goodnews
 
     # compute_goodnews_stats(goodnews)
-    compute_nytimes_stats(nytimes)
+    # compute_nytimes_stats(nytimes)
     # compute_nytimes_exact_subset_statistics(nytimes, goodnews)
     # compute_face_stats(nytimes)
+    compute_rare_stats(nytimes)
 
 
 if __name__ == '__main__':

### 2019-11-10 paper/paper.tex
Finish off datasets section

@@
 
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset in
-our experiments, along with the original train-validation-test split, to make
-comparison to previous works easier. In the original split, the dataset was
-randomly divided into...
-
 % \begin{table}[t]
@@
 		\midrule
-      Number of articles & 257 033 & 445 828 \\
-      Number of images   & 462 642 & 794 085 \\
+      Number of articles & 257 033 & 445 819 \\
+      Number of images   & 462 642 & 794 044 \\
       Average article length & 451 & 974 \\
@@
       \% of captions with \\
-      \quad -- named entities & 97\% & 97\% \\
+      \quad -- named entities & 97\% & 96\% \\
       \quad -- personal names & 68\% & 68\% \\
@@
 \end{table}
+
+From the recollection, we observe that the average length of an article in
+GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
+the article body is missing in GoodNews. This includes the first few paragraphs
+that might contain important information about the top caption. Looking through
+the publicly released code, we found that this is because the original parser
+used by \cite{Biten2019GoodNews} was designed to extract articles from a
+generic online news source and it fails to recognize certain HTML tags used
+specifically in New York Times web pages.
+
+In addition, we also found some noisy samples in GoodNews. This includes a
+small number of non-English articles, and captioned images from the
+recommendation sidebar which are not related to the main article.
+
+Despite the above limitations, we still use the original GoodNews dataset and
+train-validation-test split in our experiments, in order to make comparison to
+previous works easier. Using the original split, we have 421K training, 18K
+validation, and 23K test captions. Given that the random split was done at the
+caption level, it is possible for a training and test caption to share the same
+article text.
 
@@
 		\midrule
-      Number of articles & &  \\
-      Number of images   &  &  \\
-      Start month &  & \\
-      End month &  & \\
+      Number of articles & 434 272 & 3 052 & 8 495 \\
+      Number of images  & 764 049 & 7 852 & 22 143 \\
+      Start month & Mar 15 & May 19 & Jun 19 \\
+      End month & Apr 19 & May 19 & Aug 19 \\
 		\bottomrule
@@
 
-In order to study how rare names are generated, we split the training,
-validation, and test sets by time. The training set consists of 434K articles
+We split the training, validation, and test sets according to time, as shown in
+Table \ref{tab:splits}. For example, the test set consists of all captions and
+articles in the final three months of the collection period, from June to
+August 2019. This has two advantages over the random split used in GoodNews.
+Firstly, it prevents captions in the training and test sets from sharing the
+same context article, thus making it better to see how well the model can
+generalize. Secondly, due of the shift in the coverage of news over time, there
+will be events and people in the test data that have never covered by the news
+before. In particular, out of the 100K proper nouns in the test captions, 4\%
+never appear in any training captions. Half of these also never appear in any
+training article. Thus splitting by time allows us study how well the model can
+generate rare names.
 
-\section{Model}
+\section{Model Architectures}
+
+\subsection{Context Inputs}
+
+We propose a fully end-to-end model to generate news image captions. There
+are three inputs to the model: the image, the faces, and article text. Using
+ResNet-152, we obtain an embedding $X_I \in \mathbb{R}^{1024}$:
 

### 2019-11-10 paper/paper.tex
Work on image and text embeddings

@@
 \usepackage{amssymb}
+\usepackage{bm} % bold fonts for math symbols
 \usepackage{booktabs}
 \usepackage[export]{adjustbox} % adds a frame around figures
+\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
 
@@
 
+\begin{figure*}[t]
+   \begin{center}
+   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+   \end{center}
+      \caption{Overall architecture of the model.}
+   \label{fig:short}
+\end{figure*}
+
 \begin{itemize}
@@
 
-\section{Model Architectures}
-
-\subsection{Context Inputs}
-
-We propose a fully end-to-end model to generate news image captions. There
-are three inputs to the model: the image, the faces, and article text. Using
-ResNet-152, we obtain an embedding $X_I \in \mathbb{R}^{1024}$:
-
-Devlin \etal \cite{Devlin2019BERT} introduced BERT, a language representation
-model which provides pretrained contextual embeddings for text. We use
-RoBERTa \cite{Liu2019RoBERTaAR}, a more carefully trained BERT model, to
-embed the article text. There there two key advantages:
-
-\begin{itemize}
-   \item Unlike glove \cite{Pennington2014Glove} or word2vec
-   \cite{Mikolov2013DistributedRO} where each word has exactly one
-   representation, the bidirectional and attention mechanism in transformers
-   allow words to have different representation depending on the context.
-   \item RoBERTa uses Byte-Pair Encoding (BPE)
-   \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which allows us to
-   represent and generate potentially any word that can be written in
-   Unicode. The vocabulary size is 50,265.
-\end{itemize}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
-
-To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-We use ResNeXt-101 \cite{Xie2017AggregatedRT} to obtain an embedding for
-the images. For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
-the self-attention layer.
-
-We use MTCNN \cite{Zhang2016JointFD} to detect faces and FaceNet
-\cite{Schroff2015FaceNetAU} trained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}
-to classify the faces.
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-   \end{figure*}
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-dataset. Table \ref{tab:results-nytimes} shows additional results done on
-our NYTimes800k dataset.
-
 \begin{table*}[t]
@@
       Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
       Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
@@
       Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% \\
-      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
       Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% \\
@@
       Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
       Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
@@
       GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
+      RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
       Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
@@
       GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
+      RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
       Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
@@
       GloVe + Transformer  & 15.1 & 12.9 \\
-      RoBERTa + LSTM  & 15.6 & 13.4 \\
+      RoBERTa + LSTM  & 14.9 & 13.0 \\
       Transformer (first 512 tokens)  & 15.3 & 13.6 \\
@@
 
-\begin{table*}[t]
+\section{Model Architecture}
+
+\subsection{Model Inputs}
+
+Our proposed model takes three inputs: the image, the faces, and article text.
+Each of these inputs first goes through an encoder to give us a vector
+representation.
+
+\subsubsection{Image Embedding}
+
+For the image, we feed it through a pretrained ResNet-152 model
+\cite{He2016ResNet} and use the output of the final block, just before the
+pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
+\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
+attend to 49 different patches in the image.
+
+\subsubsection{Article Embedding}
+
+For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
+RoBERTa is a language representation model that provides pretrained contextual
+embeddings for text. It consists of 24 layers of bidirectional transformer
+blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
+
+Unlike GloVe \cite{Pennington2014Glove} and word2vec
+\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
+representation, the bidirectionality and the attention mechanism in the
+transformer allow a word to have different vector representations depending on
+the surrounding context.
+
+The largest GloVe model has a vocabulary size of 1.2 million. Although this is
+large, many rare names will still get mapped to the unknown token. In contrast,
+RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
+encode any word that can be written in Unicode characters.
+
+Given an input of length $S$, the pretrained RoBERTa encoder will return 25
+sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
+\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
+the output of each of the 24 layers. Inspired by Tenney \etal
+\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
+different steps in the traditional NLP pipeline, we take a weighted sum
+across all layers to obtain the article embedding:
+\begin{IEEEeqnarray*}{lCl}
+   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
+\end{IEEEeqnarray*}
+where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
+and $w_i$ are learnable weights.
+
+One limitation of RoBERTa is that the maximum length of the input sequence is
+512. For GoodNews, we simply encode the first 512 tokens of the article. For
+NYTimes800k, since we have the image position, we concatenate the title, the
+first paragraph, and as many paragraphs above and below the image as we can
+fit, until we reach the 512 token limit. Note that since we are using BPE, a
+token can be part of a word. On average, we can only encode ...... words of
+the article.
+
+\subsubsection{Face Embedding}
+
+\cite{Schroff2015FaceNetAU} trained on the VGGFace2 dataset
+\cite{Cao2017VGGFace2AD}
+to classify the faces.
+
+We use MTCNN \cite{Zhang2016JointFD} to detect faces and FaceNet
+
+\subsection{Decoder}
+
+\subsubsection{Dynamic Convolutions}
+
+Our decoder is a transformer architecture with dynamic convolutions
+\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
+found that using dynamic convolutions allows the training to converge faster
+than using the current state-of-the-art GPT-2 architecture
+\cite{Radford2019LanguageMA}. We don't have the computational resource to study
+the performance of GPT-2.
+
+\subsubsection{Adaptive Softmax}
+
+To make training more efficient, we use adaptive softmax
+\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
+15K, and 25K. We tie the adaptive weights and we share the decoder input and
+output embeddings. We use sinusoidal positional encoding
+\cite{Vaswani2017AttentionIA} to represent the position of each token.
+
+\subsubsection{Encoder Attention}
+
+For each generation step, we use the Scalar-Dot-Product attention
+\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
+The two attended representations are then concatenated and fed as input to
+the self-attention layer.
+
+\section{Experiments}
+
+The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
+the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
+dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
+will made public on GitHub.
+
+Table \ref{tab:results-goodnews} shows the results on the original GoodNews
+dataset. Table \ref{tab:results-nytimes} shows additional results done on
+our NYTimes800k dataset.
+
+\begin{table}[t]
 	\caption {Model complexity: Number of trainable parameters}
@@
 	\end{tabular}
-\end{table*}
+\end{table}
+
+\section{Discussion}
 

### 2019-11-11 paper/paper.tex
Merge tables

@@
 \usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
+\usepackage{multirow} % merge multiple rows
+\usepackage{tabularx} % for 'tabularx' environment
+\usepackage{caption} % controls spacing between caption and table
 
@@
 
-%%%%%%%%% TITLE
+%%%%%%%%% TITLE - suggestions and candidates
 \title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
+\title{Transforming Entities for News Image Captions}
 
-\author{Alasdair Tran, Alexander Matthews, Lexing Xie\\
+\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
 Australian National University\\
@@
 	\centering
-	\begin{tabular}{lll}
+	\begin{tabularx}{\linewidth}{lXX}
 		\toprule
@@
 		\bottomrule
-	\end{tabular}
+	\end{tabularx}
 \end{table}
@@
 	\centering
-	\begin{tabular}{llll}
+	\begin{tabularx}{\linewidth}{lXXX}
 		\toprule
@@
 \begin{table*}[t]
-	\caption {Results on the GoodNews dataset}
+   \caption {Results on the GoodNews and NYTimes800k dataset}
+
 	\label{tab:results-goodnews}
 	\centering
-	\begin{tabular}{llllllll}
+	\begin{tabularx}{\textwidth}{llXXXXXXX}
 		\toprule
-		 & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
+		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
       \midrule
-      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
       % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
@@
       % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
+      \cmidrule{2-9}
+      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
+      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
+      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
+      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
+      \\
+      \\
       \midrule
-      GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
+      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
+      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
+      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
+      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
+      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
+      & \\
+      \\
       \bottomrule
-	\end{tabular}
+	\end{tabularx}
 \end{table*}
@@
 	\centering
-	\begin{tabular}{lll}
+	\begin{tabularx}{\textwidth}{llXXXXXX}
 		\toprule
-        & \multicolumn{2}{c}{All names}  \\
-        & Recall  & Precision \\
+      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
+      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
       \midrule
-      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% \\
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
       % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
@@
       % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
+      \cmidrule{2-8}
+      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
+      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
+      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
+      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
+      \\
+      \\
       \midrule
-      GloVe + LSTM & 10.1\% & 14.9\%  \\
-      GloVe + Transformer & 16.6\% & 21.7\% \\
-      RoBERTa + LSTM & 23.4\% & 28.8\%  \\
-      RoBERTa + Transformer & 29.5\% & 33.9\%  \\
+      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
+      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
+      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
+      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
+      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
+      \\
+      \\
 		\bottomrule
-	\end{tabular}
+	\end{tabularx}
 \end{table*}
@@
 		\toprule
-        & Caption length  & Unique words \\
+       &  & Caption length  & Unique words \\
       \midrule
-      Ground Truths & 18.1 & 17.0 \\
-      \midrule
-      Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
+      \cmidrule{2-4}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
       % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
@@
       % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
+      \cmidrule{2-4}
+      & GloVe + LSTM & 13.9 & 11.4 \\
+      & GloVe + Transformer & 14.9 & 12.9 \\
+      & RoBERTa + LSTM & 14.7 & 12.7  \\
+      & RoBERTa + Transformer & 15.5 & 13.7 \\
+      \\
+      \\
       \midrule
-      GloVe + LSTM & 13.9 & 11.4 \\
-      GloVe + Transformer & 14.9 & 12.9 \\
-      RoBERTa + LSTM & 14.7 & 12.7  \\
-      RoBERTa + Transformer & 15.5 & 13.7 \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Results on the NYTimes800k test set}
-	\label{tab:results-nytimes}
-	\centering
-	\begin{tabular}{llllllll}
-		\toprule
-		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
-      \midrule
-      GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
+      & GloVe + LSTM  & 13.8 & 11.8 \\
+      & GloVe + Transformer  & 15.1 & 12.9 \\
+      & RoBERTa + LSTM  & 14.9 & 13.0 \\
+      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
+      & Transformer (location-aware) & 15.1 & 13.5  \\
       \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the NYTimes800k test set}
-	\label{tab:results-names}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the NYTimes800k test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Caption length  & Unique words \\
-      \midrule
-      Ground Truths & 18.4 & 17.1 \\
-      GloVe + LSTM  & 13.8 & 11.8 \\
-      GloVe + Transformer  & 15.1 & 12.9 \\
-      RoBERTa + LSTM  & 14.9 & 13.0 \\
-      Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      Transformer (location-aware) & 15.1 & 13.5  \\
+      \\
 		\bottomrule
@@
 
-\cite{Schroff2015FaceNetAU} trained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}
-to classify the faces.
-
-We use MTCNN \cite{Zhang2016JointFD} to detect faces and FaceNet
+To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
+face bounding boxes. We then select the top $M$ faces and feed them through a
+FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
+\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
+\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
 
@@
 Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-dataset. Table \ref{tab:results-nytimes} shows additional results done on
-our NYTimes800k dataset.
+and NYTimes800k datasets.
 

### 2019-11-11 scripts/compute_metrics.py
Compute TTR and Flesch reading ease

@@ -91,6 +91,9 @@ def main():
     lengths, gt_lengths = [], []
     n_uniques, gt_n_uniques = [], []
 
+    gen_ttrs, cap_ttrs = [], []
+    gen_flesch, cap_flesch = [], []
+
     with open(args['file']) as f:
         for line in tqdm(f):
             obj = json.loads(line)
@@ -150,6 +153,12 @@ def main():
             eval_line += ' ||| {}'.format(stat)
             count += 1
 
+            gen_ttrs.append(obj['gen_np']['basic_ttr'])
+            cap_ttrs.append(obj['caption_np']['basic_ttr'])
+            gen_flesch.append(obj['gen_readability']['flesch_reading_ease'])
+            cap_flesch.append(obj['caption_readability']
+                              ['flesch_reading_ease'])
+
     meteor_scorer.meteor_p.stdin.write('{}\n'.format(eval_line).encode())
     meteor_scorer.meteor_p.stdin.flush()
     for _ in range(count):
@@ -204,6 +213,10 @@ def main():
         'Length - reference': sum(gt_lengths) / len(gt_lengths),
         'Unique words - generation': sum(n_uniques) / len(n_uniques),
         'Unique words - reference': sum(gt_n_uniques) / len(gt_n_uniques),
+        'Caption TTR': sum(cap_ttrs) / len(cap_ttrs),
+        'Generation TTR': sum(gen_ttrs) / len(gen_ttrs),
+        'Caption Flesch Reading Ease': sum(cap_flesch) / len(cap_flesch),
+        'Generation Flesch Reading Ease': sum(gen_flesch) / len(gen_flesch),
     }
 
     serialization_dir = os.path.dirname(args['file'])

### 2019-11-11 scripts/compute_metrics.py
Compute exact entity matches

@@ -15,6 +15,7 @@ import os
 import pickle
 import re
 import types
+from collections import defaultdict
 
 import numpy as np
 import ptvsd
@@ -94,6 +95,8 @@ def main():
     gen_ttrs, cap_ttrs = [], []
     gen_flesch, cap_flesch = [], []
 
+    ent_counter = defaultdict(int)
+
     with open(args['file']) as f:
         for line in tqdm(f):
             obj = json.loads(line)
@@ -159,6 +162,8 @@ def main():
             cap_flesch.append(obj['caption_readability']
                               ['flesch_reading_ease'])
 
+            compute_entities(obj, ent_counter)
+
     meteor_scorer.meteor_p.stdin.write('{}\n'.format(eval_line).encode())
     meteor_scorer.meteor_p.stdin.flush()
     for _ in range(count):
@@ -217,6 +222,56 @@ def main():
         'Generation TTR': sum(gen_ttrs) / len(gen_ttrs),
         'Caption Flesch Reading Ease': sum(cap_flesch) / len(cap_flesch),
         'Generation Flesch Reading Ease': sum(gen_flesch) / len(gen_flesch),
+        'Entity all - recall': {
+            'count': ent_counter['n_caption_ent_matches'],
+            'total': ent_counter['n_caption_ents'],
+            'percentage': ent_counter['n_caption_ent_matches'] / ent_counter['n_caption_ents'],
+        },
+        'Entity all - precision': {
+            'count': ent_counter['n_gen_ent_matches'],
+            'total': ent_counter['n_gen_ents'],
+            'percentage': ent_counter['n_gen_ent_matches'] / ent_counter['n_gen_ents'],
+        },
+        'Entity person - recall': {
+            'count': ent_counter['n_caption_person_matches'],
+            'total': ent_counter['n_caption_persons'],
+            'percentage': ent_counter['n_caption_person_matches'] / ent_counter['n_caption_persons'],
+        },
+        'Entity person - precision': {
+            'count': ent_counter['n_gen_person_matches'],
+            'total': ent_counter['n_gen_persons'],
+            'percentage': ent_counter['n_gen_person_matches'] / ent_counter['n_gen_persons'],
+        },
+        'Entity GPE - recall': {
+            'count': ent_counter['n_caption_gpes_matches'],
+            'total': ent_counter['n_caption_gpes'],
[…]

### 2019-11-12 paper/paper.tex
Start working on Experiments section

@@
    describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
+   model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
    outperforming the previous state-of-art CIDEr of 13. We also introduce the
@@
    metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
+   the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
    source code are available from
@@
 \begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
+   \caption {BLEU, ROUGE, METEOR, and CIDEr metrics on GoodNews and
+             NYTimes800k.}
 
-	\label{tab:results-goodnews}
+	\label{tab:results}
 	\centering
@@
       \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.66 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
       % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
@@
       \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
+      % & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
+      % & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
+      % & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
+      & GloVe + LSTM &  &  &  &  &  &  &  \\
+      & GloVe + Transformer &  &  &  &  &  &  &  \\
+      & RoBERTa + LSTM &  &  &  &  &  &  &   \\
       & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
+      & \quad + faces & 22.4 & 13.6 & 8.84 & 6.10 & 21.3 & 10.3 & 53.9 \\ % Final
+      & \quad\quad + copying \\
       \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
+      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
       & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
       & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
+      & RoBERTa + Transformer & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
+      & \quad + location-aware & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
+      & \quad\quad + faces & 22.1 & 13.6 & 9.05 & 6.41 & 21.7 & 10.4 & 54.7 \\ % Final
+      & \quad\quad\quad + copying \\
       \bottomrule
@@
 \begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
+   \caption {Named entity, personal name, and rare proper noun recall \&
+             precision on GoodNews and NYTimes800k.}
 	\label{tab:results-names}
@@
 		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
+      &  & \multicolumn{2}{c}{Named entities} & \multicolumn{2}{c}{Personal names} & \multicolumn{2}{c}{Rare proper nouns} \\
       &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
@@
       \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 5.64\% & 8.87\% & 6.98\% & 11.9\% & -- & -- \\
       \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
+      & GloVe + LSTM & & &  &  & -- & --  \\
+      & GloVe + Transformer & & &  &  & -- & -- \\
+      & RoBERTa + LSTM & &  &  &  & -- & -- \\
+      & RoBERTa + Transformer & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
+      & \quad + faces & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
+      & \quad\quad + copying \\
       \midrule
       \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
+      & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
+      & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
+      & RoBERTa + LSTM & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
+      & RoBERTa + Transformer & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
+      & \quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
+      & \quad\quad + faces & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
+      & \quad\quad\quad + copying \\
 		\bottomrule
@@
 
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
+\begin{table}[t]
+   \caption {Linguistic measures on the generated captions: caption length (CL),
+             type-token ratio (TTR), and Flesch readability ease (FRE).}
 	\label{tab:results-stats}
 	\centering
-	\begin{tabular}{lllllll}
+	\begin{tabularx}{\linewidth}{llXXX}
 		\toprule
-       &  & Caption length  & Unique words \\
+       &  &  CL  & TTR & FRE \\
       \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Ground Truths & 18.1 & 94.9 & 65.4 \\
+      \cmidrule{2-5}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
+      \cmidrule{2-5}
+      & GloVe + LSTM &  &  \\
+      & GloVe + Transformer &  &  \\
+      & RoBERTa + LSTM &  &   \\
+      & RoBERTa + Transformer & 15.5 & 91.0 & 72.0 \\
+      & \quad + faces & 15.5 & 90.7 & 71.9 \\
+      & \quad\quad + copying \\
       \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & Ground Truths & 18.4 & 94.6 & 63.9 \\
+      & GloVe + LSTM  & 13.8 & 89.0 & 77.8 \\
+      & GloVe + Transformer  & 15.1 & 88.6 & 73.8 \\
+      & RoBERTa + LSTM  & 14.9 & 90.2 & 72.6 \\
+      & RoBERTa + Transformer  & 15.3 & 91.5 & 70.4 \\
+      & \quad + location-aware & 15.1 & 91.7 & 70.4  \\
+      & \quad\quad + faces & 15.2 & 91.6 & 70.5 \\
+      & \quad\quad\quad + copying \\
 		\bottomrule
-	\end{tabular}
-\end{table*}
+	\end{tabularx}
+\end{table}
 
@@
 
+\subsection{Training Details}
+
+In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
+\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
+parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
+decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
+number of training examples, which is 6.6 million. This is equivalent to 16
+epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
+learning rate in the first 5\% of the training steps to $10^{-4}$, and
+afterward decays it linearly. Training the full model takes 5 days on one Titan
+V.
+
 The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
 the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
+dynamic convolution code are adapted from fairseq \cite{Ott2019Fairseq}.
 
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
+\subsection{Results}
+
+Table \ref{tab:results} shows the results on GoodNews and NYTimes800k.
 
 \begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
+	\caption {Model complexity}
 	\label{tab:models}
 	\centering
-	\begin{tabular}{lllllll}
+	\begin{tabularx}{\linewidth}{Xc}
 		\toprule
-        & Parameters \\
+        & No. of Parameters \\
       \midrule
@@
       RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
+      \quad + faces & 171M \\
+      \quad\quad + copying & 207M \\
 		\bottomrule
-	\end{tabular}
+	\end{tabularx}
 \end{table}

### 2019-11-12 paper/paper.tex
Work on results section

@@
 
-\begin{table*}[t]
-   \caption {Named entity, personal name, and rare proper noun recall \&
-             precision on GoodNews and NYTimes800k.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{Named entities} & \multicolumn{2}{c}{Personal names} & \multicolumn{2}{c}{Rare proper nouns} \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 5.64\% & 8.87\% & 6.98\% & 11.9\% & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & & &  &  & -- & --  \\
-      & GloVe + Transformer & & &  &  & -- & -- \\
-      & RoBERTa + LSTM & &  &  &  & -- & -- \\
-      & RoBERTa + Transformer & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
-      & \quad + faces & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
-      & \quad\quad + copying \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
-      & RoBERTa + Transformer & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
-      & \quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
-      & \quad\quad + faces & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
-      & \quad\quad\quad + copying \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table}[t]
-   \caption {Linguistic measures on the generated captions: caption length (CL),
-             type-token ratio (TTR), and Flesch readability ease (FRE).}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabularx}{\linewidth}{llXXX}
-		\toprule
-       &  &  CL  & TTR & FRE \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Ground Truths & 18.1 & 94.9 & 65.4 \\
-      \cmidrule{2-5}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
-      \cmidrule{2-5}
-      & GloVe + LSTM &  &  \\
-      & GloVe + Transformer &  &  \\
-      & RoBERTa + LSTM &  &   \\
-      & RoBERTa + Transformer & 15.5 & 91.0 & 72.0 \\
-      & \quad + faces & 15.5 & 90.7 & 71.9 \\
-      & \quad\quad + copying \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & Ground Truths & 18.4 & 94.6 & 63.9 \\
-      & GloVe + LSTM  & 13.8 & 89.0 & 77.8 \\
-      & GloVe + Transformer  & 15.1 & 88.6 & 73.8 \\
-      & RoBERTa + LSTM  & 14.9 & 90.2 & 72.6 \\
-      & RoBERTa + Transformer  & 15.3 & 91.5 & 70.4 \\
-      & \quad + location-aware & 15.1 & 91.7 & 70.4  \\
-      & \quad\quad + faces & 15.2 & 91.6 & 70.5 \\
-      & \quad\quad\quad + copying \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
 \section{Model Architecture}
@@
 than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
+\cite{Radford2019LanguageMA}.
+
+In the standard self-attention module, the input embedding $\bm{x} \in
+\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
+$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
+weighted sum of the values, where the weights are obtained from the dot product
+between the key and value:
+\begin{IEEEeqnarray*}{lCl}
+   \text{Attention}(\bm{x}) &=&
+   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
+\end{IEEEeqnarray*}
+
+\begin{table*}[t]
+   \caption {Named entity, personal name, and rare proper noun recall \&
+             precision on GoodNews and NYTimes800k.}
+	\label{tab:names}
+	\centering
+	\begin{tabularx}{\textwidth}{llXXXXXX}
+		\toprule
+      &  & \multicolumn{2}{c}{Named entities} & \multicolumn{2}{c}{Personal names} & \multicolumn{2}{c}{Rare proper nouns} \\
+      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
+      \midrule
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 5.64\% & 8.87\% & 6.98\% & 11.9\% & -- & -- \\
+      \cmidrule{2-8}
+      & GloVe + LSTM & & &  &  & -- & --  \\
+      & GloVe + Transformer & & &  &  & -- & -- \\
+      & RoBERTa + LSTM & &  &  &  & -- & -- \\
+      & RoBERTa + Transformer & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
+      & \quad + faces & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
+      & \quad\quad + copying \\
+      \midrule
+      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
+      & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
+      & RoBERTa + LSTM & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
+      & RoBERTa + Transformer & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
+      & \quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
+      & \quad\quad + faces & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
+      & \quad\quad\quad + copying \\
+		\bottomrule
+	\end{tabularx}
+\end{table*}
 
@@
 
-To make training more efficient, we use adaptive softmax
+The BPE vocabulary size is 50265. To make training more efficient, we use adaptive softmax
 \cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
@@
 For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
+\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
+of the three attended representations are then concatenated and fed as input to
 the self-attention layer.
@@
 afterward decays it linearly. Training the full model takes 5 days on one Titan
-V.
+V GPU.
+
+As shown in Table \ref{tab:models}, all of our baselines are designed to have
+roughly the same number of trainable parameters. This allows us to attribute
+improvement to the individual model components rather than to simply having a
+bigger model.
 
@@
 dynamic convolution code are adapted from fairseq \cite{Ott2019Fairseq}.
-
-\subsection{Results}
-
-Table \ref{tab:results} shows the results on GoodNews and NYTimes800k.
 
@@
 
-\section{Discussion}
+\subsection{Results}
+
+Table \ref{tab:results} shows the BLEU \cite{Papineni2002Bleu}, ROUGE
+\cite{Lin2004ROUGE}, METEOR \cite{Denkowski2014Meteor}, and CIDEr
+\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
+results from the previous state-of-the-art \cite{Biten2019GoodNews}. Note that
+the numbers reported here are slightly different from the original paper since
+we had to remove a few samples from the test set where the image is no longer
+available. \cite{Biten2019GoodNews} also did some post-processing on the
+ground-truth captions such as removing contractions and non-ASCII characters,
+both of which we did not do. Despite these differences, the final metrics
+are the same if rounded to the nearest whole number.
+
+There is a strong correlation between of all these metrics, and in general, we
+mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
+(TF-IDF) to put more importance on less common words such as entity names.
+Table \ref{tab:names} shows the recall and precision of the named entities,
+personal names, and rare proper nouns.
+
+We can make the following observations:
+
+\begin{itemize}
+   \item Our baseline LSTM model with GloVe embeddings yields competitive
+   results to previous the state-of-the-art \cite{Biten2019GoodNews}. This
+   means that BPE offers a viable alternative to template-based methods.
+
+   \item Models with GloVe embeddings are unable to generate rare proper nouns.
+   This is expected since GloVe has a fixed vocabulary and if there is a
+   unknown word in the article, the encoder will simply skip it.
+
+   \item Switching from an LSTM to a transformer architecture improves the
+   CIDEr score on NYTimes800k by 8 points, from 12 to 20. If we then use the
+   contextualize RoBERTa embeddings instead of GloVe, CIDEr more than doubles
+   to 44.
+
+   \item Adding attention over the faces improves both the recall and precision
+   of personal names. It has no significant effect on other entity types (see
+   the supplementary materials for a detailed breakdown).
+\end{itemize}
+
+\begin{table}[t]
+   \caption {Linguistic measures on the generated captions: caption length (CL),
+             type-token ratio (TTR), and Flesch readability ease (FRE).}
+	\label{tab:caption}
+	\centering
+	\begin{tabularx}{\linewidth}{llXXX}
+		\toprule
+       &  &  CL  & TTR & FRE \\
+      \midrule
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Ground Truths & 18.1 & 94.9 & 65.4 \\
+      \cmidrule{2-5}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
+      \cmidrule{2-5}
+      & GloVe + LSTM &  &  \\
+      & GloVe + Transformer &  &  \\
+      & RoBERTa + LSTM &  &   \\
+      & RoBERTa + Transformer & 15.5 & 91.0 & 72.0 \\
+      & \quad + faces & 15.5 & 90.7 & 71.9 \\
+      & \quad\quad + copying \\
+      \midrule
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & Ground Truths & 18.4 & 94.6 & 63.9 \\
+      & GloVe + LSTM  & 13.8 & 89.0 & 77.8 \\
+      & GloVe + Transformer  & 15.1 & 88.6 & 73.8 \\
+      & RoBERTa + LSTM  & 14.9 & 90.2 & 72.6 \\
+      & RoBERTa + Transformer  & 15.3 & 91.5 & 70.4 \\
+      & \quad + location-aware & 15.1 & 91.7 & 70.4  \\
+      & \quad\quad + faces & 15.2 & 91.6 & 70.5 \\
+      & \quad\quad\quad + copying \\
+		\bottomrule
+	\end{tabularx}
+\end{table}
+
+Table \ref{tab:caption} look at the quality of the generated captions. We look
+at three metrics: caption length, type-token ratio (TTR), and Flesch reading
+ease. TTR is the ratio of the number of unique words to the total number of
+words in a caption. The Flesch reading ease takes into account the number of
+words and syllables and produces a score between 0 and 100, where higher means
+being easier to read.
+
+From these metrics, we see that our generated captions are in general still
+shorter than real-life captions, have lower lexical diversity (lower TTR)
+and still use simpler language (higher Flesch reading ease).
 

### 2019-11-12 paper/section_0_abstract.tex
Split paper into multiple files

--- 2019-11-11 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
+% !TEX root = main.tex
 
@@
     describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
+    model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
     outperforming the previous state-of-art CIDEr of 13. We also introduce the
@@
     metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
+    the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
     source code are available from
@@
  \end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
-Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
-
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
-
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
-
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
-results on many natural language understanding benchmarks including GLUE
-\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
-\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
-
-\begin{figure}[t]
-   \begin{center}
-      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-   \end{center}
-      \caption{Our transformer model attends to embeddings from three different
-      domains (image patches, faces, and article text). Using byte-pair
-      encoding, the model can then directly produce a caption containing
-      specific named entities without the use of templates.}
-   \label{fig:long}
-   \label{fig:onecol}
-\end{figure}
-
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
-
-The goal of this paper is to make use of these recent developments, along with
-their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
-
-\begin{enumerate}
-   \item We introduce NYTimes800k, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
-   but we write a custom parser to collect higher-quality articles and metadata
-   such as the location of an image within the page.
-
-   \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
-
-   \item We provide a detailed model analysis, deconstructing the most
-   important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
-   METEOR, and CIDEr; but also to other linguistic measures like readability
-   scores, caption length, and recall of rare names.
-\end{enumerate}
-
-\section{Related Works}
-
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
-\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
-image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
-Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
-
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
-extractive methods that use n-gram models to combine existing phrases
-\cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
-
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
-for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
-
-Transformers are still scarcely used in image captioning. They have been shown
-to yield competitive results in generating generic MS COCO captions
-\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
-extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
-
-BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
-
-In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
-\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
-derived from the image itself. When attending to more than one modality, there
-are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-
-% \begin{table}[t]
-% 	\caption {Summary of datasets}
-% 	\label{tab:datasets}
-% 	\centering
-% 	\begin{tabular}{llll}
-% 		\toprule
-% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
-% 		\midrule
-%       No. of articles & 241 808 & 241 808 & 445 828 \\
-%       No. of images   & 462 642 & 440 112 & 794 085 \\
-%       Article length & 451 & 963 & 974 \\
-%       Caption length & 18 & 18 & 18 \\
-%       Start month & Jan 10 & Jan 10 & Mar 05\\
-%       End month & Jul 18 & Jul 18 & Sep 19 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{table}[t]
-	\caption {Summary of news captioning datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabularx}{\linewidth}{lXX}
-		\toprule
-		  & GoodNews  &   NYTimes800k \\
-		\midrule
-      Number of articles & 257 033 & 445 819 \\
-      Number of images   & 462 642 & 794 044 \\
-      Average article length & 451 & 974 \\
-      Average caption length & 18 & 18 \\
-      Collection start month & Jan 10 & Mar 05\\
-      Collection end month & Mar 18 & Sep 19 \\
-      \midrule
-      \% of words that are \\
-      \quad -- nouns & 16\% & 16\% \\
-      \quad -- pronouns & 1\% & 1\% \\
-      \quad -- proper nouns & 23\% & 22\% \\
-      \quad -- verbs & 9\% & 9\%  \\
-      \quad -- adjectives & 4\% & 4\% \\
-      \quad -- named entities & 27\% & 26\% \\
-      \quad -- personal names & 9\% & 9\% \\
-      \midrule
-      \% of captions with \\
-      \quad -- named entities & 97\% & 96\% \\
-      \quad -- personal names & 68\% & 68\% \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
-   \end{center}
-      \caption{Co-occurrence of faces and personal names in NYTimes800k
-               training data. The blue bars count how many images containing a
-               certain number of faces. The orange bars count how many captions
-               containing a certain number of personal names.}
-   \label{fig:faces}
-\end{figure}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
-   becoming the largest news image captioning dataset.
-   \item Using our custom parser, articles in NYTimes800k contain the full text
-   with no missing paragraphs.
-   \item NYTimes800k contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item Unlike GoodNews, we also collect information about where an image is
-   located in the corresponding article. Most news articles have one image at
-   the top that relates to the key topic. However 39\% of the articles have at
-   least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
-\end{itemize}
-
-Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
-\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
-personal names. One important observation is that the majority of captions
-contain at most four names.
-
-\begin{table}[t]
-	\caption {NYTimes800k training, validation, and test splits}
-	\label{tab:splits}
-	\centering
-	\begin{tabularx}{\linewidth}{lXXX}
-		\toprule
-		  & Training  &   Validation & Test \\
-		\midrule
-      Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
-      Start month & Mar 15 & May 19 & Jun 19 \\
-      End month & Apr 19 & May 19 & Aug 19 \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
-articles in the final three months of the collection period, from June to
-August 2019. This has two advantages over the random split used in GoodNews.
-Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
-before. In particular, out of the 100K proper nouns in the test captions, 4\%
-never appear in any training captions. Half of these also never appear in any
-training article. Thus splitting by time allows us study how well the model can
-generate rare names.
-
-\begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
-
-	\label{tab:results-goodnews}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
-      \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-       &  & Caption length  & Unique words \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\section{Model Architecture}
-
-\subsection{Model Inputs}
-
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
-
-\subsubsection{Image Embedding}
-
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
-
-\subsubsection{Article Embedding}
-
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
-\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
-representation, the bidirectionality and the attention mechanism in the
-transformer allow a word to have different vector representations depending on
-the surrounding context.
-
-The largest GloVe model has a vocabulary size of 1.2 million. Although this is
-large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
-encode any word that can be written in Unicode characters.
-
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
-\end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
-
-One limitation of RoBERTa is that the maximum length of the input sequence is
-512. For GoodNews, we simply encode the first 512 tokens of the article. For
-NYTimes800k, since we have the image position, we concatenate the title, the
-first paragraph, and as many paragraphs above and below the image as we can
-fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
-
-\subsection{Decoder}
-
-\subsubsection{Dynamic Convolutions}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
-
-\subsubsection{Adaptive Softmax}
-
-To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
-the self-attention layer.
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
-
-\begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
-	\label{tab:models}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Parameters \\
-      \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 paper/section_1_intro.tex
Split paper into multiple files

--- 2019-11-11 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% !TEX root = main.tex
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, and
-   pretrained embeddings from three different modalities (RoBERTa for text,
-   ResNet-152 for images, and FaceNet for faces), our system is able to
-   describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
-   outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes800k dataset, the largest news image captioning dataset to date.
-   NYTimes800k is an extended version of GoodNews with higher-quality articles and
-   metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
-   source code are available from
-   \href{https://github.com}{https://github.com/anonymized-link}.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
 \section{Introduction}
@@
 \end{enumerate}
-
-\section{Related Works}
-
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
-\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
-image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
-Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
-
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
-extractive methods that use n-gram models to combine existing phrases
-\cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
-
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
-for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
-
-Transformers are still scarcely used in image captioning. They have been shown
-to yield competitive results in generating generic MS COCO captions
-\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
-extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
-
-BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
-
-In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
-\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
-derived from the image itself. When attending to more than one modality, there
-are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-
-% \begin{table}[t]
-% 	\caption {Summary of datasets}
-% 	\label{tab:datasets}
-% 	\centering
-% 	\begin{tabular}{llll}
-% 		\toprule
-% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
-% 		\midrule
-%       No. of articles & 241 808 & 241 808 & 445 828 \\
-%       No. of images   & 462 642 & 440 112 & 794 085 \\
-%       Article length & 451 & 963 & 974 \\
-%       Caption length & 18 & 18 & 18 \\
-%       Start month & Jan 10 & Jan 10 & Mar 05\\
-%       End month & Jul 18 & Jul 18 & Sep 19 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{table}[t]
-	\caption {Summary of news captioning datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabularx}{\linewidth}{lXX}
-		\toprule
-		  & GoodNews  &   NYTimes800k \\
-		\midrule
-      Number of articles & 257 033 & 445 819 \\
-      Number of images   & 462 642 & 794 044 \\
-      Average article length & 451 & 974 \\
-      Average caption length & 18 & 18 \\
-      Collection start month & Jan 10 & Mar 05\\
-      Collection end month & Mar 18 & Sep 19 \\
-      \midrule
-      \% of words that are \\
-      \quad -- nouns & 16\% & 16\% \\
-      \quad -- pronouns & 1\% & 1\% \\
-      \quad -- proper nouns & 23\% & 22\% \\
-      \quad -- verbs & 9\% & 9\%  \\
-      \quad -- adjectives & 4\% & 4\% \\
-      \quad -- named entities & 27\% & 26\% \\
-      \quad -- personal names & 9\% & 9\% \\
-      \midrule
-      \% of captions with \\
-      \quad -- named entities & 97\% & 96\% \\
-      \quad -- personal names & 68\% & 68\% \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
-   \end{center}
-      \caption{Co-occurrence of faces and personal names in NYTimes800k
-               training data. The blue bars count how many images containing a
-               certain number of faces. The orange bars count how many captions
-               containing a certain number of personal names.}
-   \label{fig:faces}
-\end{figure}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
-   becoming the largest news image captioning dataset.
-   \item Using our custom parser, articles in NYTimes800k contain the full text
-   with no missing paragraphs.
-   \item NYTimes800k contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item Unlike GoodNews, we also collect information about where an image is
-   located in the corresponding article. Most news articles have one image at
-   the top that relates to the key topic. However 39\% of the articles have at
-   least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
-\end{itemize}
-
-Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
-\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
-personal names. One important observation is that the majority of captions
-contain at most four names.
-
-\begin{table}[t]
-	\caption {NYTimes800k training, validation, and test splits}
-	\label{tab:splits}
-	\centering
-	\begin{tabularx}{\linewidth}{lXXX}
-		\toprule
-		  & Training  &   Validation & Test \\
-		\midrule
-      Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
-      Start month & Mar 15 & May 19 & Jun 19 \\
-      End month & Apr 19 & May 19 & Aug 19 \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
-articles in the final three months of the collection period, from June to
-August 2019. This has two advantages over the random split used in GoodNews.
-Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
-before. In particular, out of the 100K proper nouns in the test captions, 4\%
-never appear in any training captions. Half of these also never appear in any
-training article. Thus splitting by time allows us study how well the model can
-generate rare names.
-
-\begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
-
-	\label{tab:results-goodnews}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
-      \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-       &  & Caption length  & Unique words \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\section{Model Architecture}
-
-\subsection{Model Inputs}
-
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
-
-\subsubsection{Image Embedding}
-
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
-
-\subsubsection{Article Embedding}
-
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
-\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
-representation, the bidirectionality and the attention mechanism in the
-transformer allow a word to have different vector representations depending on
-the surrounding context.
-
-The largest GloVe model has a vocabulary size of 1.2 million. Although this is
-large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
-encode any word that can be written in Unicode characters.
-
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
-\end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
-
-One limitation of RoBERTa is that the maximum length of the input sequence is
-512. For GoodNews, we simply encode the first 512 tokens of the article. For
-NYTimes800k, since we have the image position, we concatenate the title, the
-first paragraph, and as many paragraphs above and below the image as we can
-fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
-
-\subsection{Decoder}
-
-\subsubsection{Dynamic Convolutions}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
-
-\subsubsection{Adaptive Softmax}
-
-To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
-the self-attention layer.
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
-
-\begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
-	\label{tab:models}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Parameters \\
-      \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 paper/section_2_literature.tex
Split paper into multiple files

--- 2019-11-11 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, and
-   pretrained embeddings from three different modalities (RoBERTa for text,
-   ResNet-152 for images, and FaceNet for faces), our system is able to
-   describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
-   outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes800k dataset, the largest news image captioning dataset to date.
-   NYTimes800k is an extended version of GoodNews with higher-quality articles and
-   metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
-   source code are available from
-   \href{https://github.com}{https://github.com/anonymized-link}.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
-Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
-
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
-
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
-
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
-results on many natural language understanding benchmarks including GLUE
-\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
-\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
-
-\begin{figure}[t]
-   \begin{center}
-      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-   \end{center}
-      \caption{Our transformer model attends to embeddings from three different
-      domains (image patches, faces, and article text). Using byte-pair
-      encoding, the model can then directly produce a caption containing
-      specific named entities without the use of templates.}
-   \label{fig:long}
-   \label{fig:onecol}
-\end{figure}
-
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
-
-The goal of this paper is to make use of these recent developments, along with
-their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
-
-\begin{enumerate}
-   \item We introduce NYTimes800k, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
-   but we write a custom parser to collect higher-quality articles and metadata
-   such as the location of an image within the page.
-
-   \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
-
-   \item We provide a detailed model analysis, deconstructing the most
-   important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
-   METEOR, and CIDEr; but also to other linguistic measures like readability
-   scores, caption length, and recall of rare names.
-\end{enumerate}
+% !TEX root = main.tex
 
@@
 \cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-
-% \begin{table}[t]
-% 	\caption {Summary of datasets}
-% 	\label{tab:datasets}
-% 	\centering
-% 	\begin{tabular}{llll}
-% 		\toprule
-% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
-% 		\midrule
-%       No. of articles & 241 808 & 241 808 & 445 828 \\
-%       No. of images   & 462 642 & 440 112 & 794 085 \\
-%       Article length & 451 & 963 & 974 \\
-%       Caption length & 18 & 18 & 18 \\
-%       Start month & Jan 10 & Jan 10 & Mar 05\\
-%       End month & Jul 18 & Jul 18 & Sep 19 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{table}[t]
-	\caption {Summary of news captioning datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabularx}{\linewidth}{lXX}
-		\toprule
-		  & GoodNews  &   NYTimes800k \\
-		\midrule
-      Number of articles & 257 033 & 445 819 \\
-      Number of images   & 462 642 & 794 044 \\
-      Average article length & 451 & 974 \\
-      Average caption length & 18 & 18 \\
-      Collection start month & Jan 10 & Mar 05\\
-      Collection end month & Mar 18 & Sep 19 \\
-      \midrule
-      \% of words that are \\
-      \quad -- nouns & 16\% & 16\% \\
-      \quad -- pronouns & 1\% & 1\% \\
-      \quad -- proper nouns & 23\% & 22\% \\
-      \quad -- verbs & 9\% & 9\%  \\
-      \quad -- adjectives & 4\% & 4\% \\
-      \quad -- named entities & 27\% & 26\% \\
-      \quad -- personal names & 9\% & 9\% \\
-      \midrule
-      \% of captions with \\
-      \quad -- named entities & 97\% & 96\% \\
-      \quad -- personal names & 68\% & 68\% \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
-   \end{center}
-      \caption{Co-occurrence of faces and personal names in NYTimes800k
-               training data. The blue bars count how many images containing a
-               certain number of faces. The orange bars count how many captions
-               containing a certain number of personal names.}
-   \label{fig:faces}
-\end{figure}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
-   becoming the largest news image captioning dataset.
-   \item Using our custom parser, articles in NYTimes800k contain the full text
-   with no missing paragraphs.
-   \item NYTimes800k contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item Unlike GoodNews, we also collect information about where an image is
-   located in the corresponding article. Most news articles have one image at
-   the top that relates to the key topic. However 39\% of the articles have at
-   least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
-\end{itemize}
-
-Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
-\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
-personal names. One important observation is that the majority of captions
-contain at most four names.
-
-\begin{table}[t]
-	\caption {NYTimes800k training, validation, and test splits}
-	\label{tab:splits}
-	\centering
-	\begin{tabularx}{\linewidth}{lXXX}
-		\toprule
-		  & Training  &   Validation & Test \\
-		\midrule
-      Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
-      Start month & Mar 15 & May 19 & Jun 19 \\
-      End month & Apr 19 & May 19 & Aug 19 \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
-articles in the final three months of the collection period, from June to
-August 2019. This has two advantages over the random split used in GoodNews.
-Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
-before. In particular, out of the 100K proper nouns in the test captions, 4\%
-never appear in any training captions. Half of these also never appear in any
-training article. Thus splitting by time allows us study how well the model can
-generate rare names.
-
-\begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
-
-	\label{tab:results-goodnews}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
-      \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-       &  & Caption length  & Unique words \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\section{Model Architecture}
-
-\subsection{Model Inputs}
-
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
-
-\subsubsection{Image Embedding}
-
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
-
-\subsubsection{Article Embedding}
-
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
-\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
-representation, the bidirectionality and the attention mechanism in the
-transformer allow a word to have different vector representations depending on
-the surrounding context.
-
-The largest GloVe model has a vocabulary size of 1.2 million. Although this is
-large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
-encode any word that can be written in Unicode characters.
-
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
-\end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
-
-One limitation of RoBERTa is that the maximum length of the input sequence is
-512. For GoodNews, we simply encode the first 512 tokens of the article. For
-NYTimes800k, since we have the image position, we concatenate the title, the
-first paragraph, and as many paragraphs above and below the image as we can
-fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
-
-\subsection{Decoder}
-
-\subsubsection{Dynamic Convolutions}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
-
-\subsubsection{Adaptive Softmax}
-
-To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
-the self-attention layer.
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
-
-\begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
-	\label{tab:models}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Parameters \\
-      \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 paper/section_3_model.tex
Split paper into multiple files

--- 2019-11-11 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+% !TEX root = main.tex
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, and
-   pretrained embeddings from three different modalities (RoBERTa for text,
-   ResNet-152 for images, and FaceNet for faces), our system is able to
-   describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
-   outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes800k dataset, the largest news image captioning dataset to date.
-   NYTimes800k is an extended version of GoodNews with higher-quality articles and
-   metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
-   source code are available from
-   \href{https://github.com}{https://github.com/anonymized-link}.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
-Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
-
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
-
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
-
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
-results on many natural language understanding benchmarks including GLUE
-\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
-\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
-
-\begin{figure}[t]
-   \begin{center}
-      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-   \end{center}
-      \caption{Our transformer model attends to embeddings from three different
-      domains (image patches, faces, and article text). Using byte-pair
-      encoding, the model can then directly produce a caption containing
-      specific named entities without the use of templates.}
-   \label{fig:long}
-   \label{fig:onecol}
-\end{figure}
-
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
-
-The goal of this paper is to make use of these recent developments, along with
-their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
-
-\begin{enumerate}
-   \item We introduce NYTimes800k, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
-   but we write a custom parser to collect higher-quality articles and metadata
-   such as the location of an image within the page.
-
-   \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
-
-   \item We provide a detailed model analysis, deconstructing the most
-   important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
-   METEOR, and CIDEr; but also to other linguistic measures like readability
-   scores, caption length, and recall of rare names.
-\end{enumerate}
-
-\section{Related Works}
-
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
-\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
-image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
-Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
-
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
-extractive methods that use n-gram models to combine existing phrases
-\cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
-
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
-for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
-
-Transformers are still scarcely used in image captioning. They have been shown
-to yield competitive results in generating generic MS COCO captions
-\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
-extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
-
-BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
-
-In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
-\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
-derived from the image itself. When attending to more than one modality, there
-are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-
-% \begin{table}[t]
-% 	\caption {Summary of datasets}
-% 	\label{tab:datasets}
-% 	\centering
-% 	\begin{tabular}{llll}
-% 		\toprule
-% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
-% 		\midrule
-%       No. of articles & 241 808 & 241 808 & 445 828 \\
-%       No. of images   & 462 642 & 440 112 & 794 085 \\
-%       Article length & 451 & 963 & 974 \\
-%       Caption length & 18 & 18 & 18 \\
-%       Start month & Jan 10 & Jan 10 & Mar 05\\
-%       End month & Jul 18 & Jul 18 & Sep 19 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{table}[t]
-	\caption {Summary of news captioning datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabularx}{\linewidth}{lXX}
-		\toprule
-		  & GoodNews  &   NYTimes800k \\
-		\midrule
-      Number of articles & 257 033 & 445 819 \\
-      Number of images   & 462 642 & 794 044 \\
-      Average article length & 451 & 974 \\
-      Average caption length & 18 & 18 \\
-      Collection start month & Jan 10 & Mar 05\\
-      Collection end month & Mar 18 & Sep 19 \\
-      \midrule
-      \% of words that are \\
-      \quad -- nouns & 16\% & 16\% \\
-      \quad -- pronouns & 1\% & 1\% \\
-      \quad -- proper nouns & 23\% & 22\% \\
-      \quad -- verbs & 9\% & 9\%  \\
-      \quad -- adjectives & 4\% & 4\% \\
-      \quad -- named entities & 27\% & 26\% \\
-      \quad -- personal names & 9\% & 9\% \\
-      \midrule
-      \% of captions with \\
-      \quad -- named entities & 97\% & 96\% \\
-      \quad -- personal names & 68\% & 68\% \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
-   \end{center}
-      \caption{Co-occurrence of faces and personal names in NYTimes800k
-               training data. The blue bars count how many images containing a
-               certain number of faces. The orange bars count how many captions
-               containing a certain number of personal names.}
-   \label{fig:faces}
-\end{figure}
+\section{Model Architecture}
 
@@
 \end{figure*}
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
-   becoming the largest news image captioning dataset.
-   \item Using our custom parser, articles in NYTimes800k contain the full text
-   with no missing paragraphs.
-   \item NYTimes800k contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item Unlike GoodNews, we also collect information about where an image is
-   located in the corresponding article. Most news articles have one image at
-   the top that relates to the key topic. However 39\% of the articles have at
-   least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
-\end{itemize}
-
-Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
-\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
-personal names. One important observation is that the majority of captions
-contain at most four names.
-
-\begin{table}[t]
-	\caption {NYTimes800k training, validation, and test splits}
-	\label{tab:splits}
-	\centering
-	\begin{tabularx}{\linewidth}{lXXX}
-		\toprule
-		  & Training  &   Validation & Test \\
-		\midrule
-      Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
-      Start month & Mar 15 & May 19 & Jun 19 \\
-      End month & Apr 19 & May 19 & Aug 19 \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
-articles in the final three months of the collection period, from June to
-August 2019. This has two advantages over the random split used in GoodNews.
-Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
-before. In particular, out of the 100K proper nouns in the test captions, 4\%
-never appear in any training captions. Half of these also never appear in any
-training article. Thus splitting by time allows us study how well the model can
-generate rare names.
-
-\begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
-
-	\label{tab:results-goodnews}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
-      \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-       &  & Caption length  & Unique words \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\section{Model Architecture}
 
@@
 than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
+\cite{Radford2019LanguageMA}.
+
+In the standard self-attention module, the input embedding $\bm{x} \in
+\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
+$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
+weighted sum of the values, where the weights are obtained from the dot product
+between the key and value:
+\begin{IEEEeqnarray*}{lCl}
+   \text{Attention}(\bm{x}) &=&
+   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
+\end{IEEEeqnarray*}
 
@@
 For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
+\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
+of the three attended representations are then concatenated and fed as input to
 the self-attention layer.
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
-
-\begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
-	\label{tab:models}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Parameters \\
-      \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 paper/section_4_datasets.tex
Split paper into multiple files

--- 2019-11-11 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, and
-   pretrained embeddings from three different modalities (RoBERTa for text,
-   ResNet-152 for images, and FaceNet for faces), our system is able to
-   describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 53 on the GoodNews dataset, significantly
-   outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes800k dataset, the largest news image captioning dataset to date.
-   NYTimes800k is an extended version of GoodNews with higher-quality articles and
-   metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 51. Pretrained models and
-   source code are available from
-   \href{https://github.com}{https://github.com/anonymized-link}.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
-Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
-
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
-
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
-
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
-results on many natural language understanding benchmarks including GLUE
-\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
-\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
-
-\begin{figure}[t]
-   \begin{center}
-      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-   \end{center}
-      \caption{Our transformer model attends to embeddings from three different
-      domains (image patches, faces, and article text). Using byte-pair
-      encoding, the model can then directly produce a caption containing
-      specific named entities without the use of templates.}
-   \label{fig:long}
-   \label{fig:onecol}
-\end{figure}
-
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
-
-The goal of this paper is to make use of these recent developments, along with
-their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
-
-\begin{enumerate}
-   \item We introduce NYTimes800k, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
-   but we write a custom parser to collect higher-quality articles and metadata
-   such as the location of an image within the page.
-
-   \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
-
-   \item We provide a detailed model analysis, deconstructing the most
-   important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
-   METEOR, and CIDEr; but also to other linguistic measures like readability
-   scores, caption length, and recall of rare names.
-\end{enumerate}
-
-\section{Related Works}
-
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
-\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
-image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
-Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
-
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
-extractive methods that use n-gram models to combine existing phrases
-\cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
-
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
-for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
-
-Transformers are still scarcely used in image captioning. They have been shown
-to yield competitive results in generating generic MS COCO captions
-\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
-extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
-
-BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
-
-In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
-\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
-derived from the image itself. When attending to more than one modality, there
-are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
+% !TEX root = main.tex
 
@@
 
+\section{Datasets}
+
+\subsection{GoodNews}
+
+As a starting point, we use the GoodNews dataset, previously the largest
+dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
+dataset is a triplet containing an article, an image, and a caption. Since only
+the article text and captions were publicly released, we had to crawl the
+images ourselves. Out of the 466K image URLs provided by
+\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
+original dataset. The remaining are broken links. As part of the quality check,
+we also wrote a custom parser to re-extract the articles in the same period
+from the original web pages, with the help of The New York Times
+API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
+
 From the recollection, we observe that the average length of an article in
@@
 article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
 
@@
 
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
+\subsection{NYTimes800k}
+
+At the same time, we also constructed a bigger and higher-quality dataset,
+which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
+summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
+advantages:
 
@@
 generate rare names.
-
-\begin{table*}[t]
-   \caption {Results on the GoodNews and NYTimes800k dataset}
-
-	\label{tab:results-goodnews}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}} & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.65 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
-      & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      \\
-      \\
-      \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \\
-      \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
-   since train-test split were created using a random shuffle.}
-	\label{tab:results-names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% & -- & -- & -- & -- \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% & -- & -- & -- & -- \\
-      \cmidrule{2-8}
-      & GloVe + LSTM & 10.1\% & 14.9\% & -- & -- & -- & --  \\
-      & GloVe + Transformer & 16.6\% & 21.7\% & -- & -- & -- & -- \\
-      & RoBERTa + LSTM & 23.4\% & 28.8\%  & -- & -- & -- & -- \\
-      & RoBERTa + Transformer & 29.5\% & 33.9\%  & -- & -- & -- & -- \\
-      \\
-      \\
-      \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 24.8\% & 27.0\% & 15.1\% & 15.2\% & 13.1\% & 8.93\%  \\
-      & Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
-      & Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
-      \\
-      \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-	\caption {Word statistics on the GoodNews test set}
-	\label{tab:results-stats}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-       &  & Caption length  & Unique words \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}  & Ground Truths & 18.1 & 17.0 \\
-      \cmidrule{2-4}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
-      \cmidrule{2-4}
-      & GloVe + LSTM & 13.9 & 11.4 \\
-      & GloVe + Transformer & 14.9 & 12.9 \\
-      & RoBERTa + LSTM & 14.7 & 12.7  \\
-      & RoBERTa + Transformer & 15.5 & 13.7 \\
-      \\
-      \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}} & Ground Truths & 18.4 & 17.1 \\
-      & GloVe + LSTM  & 13.8 & 11.8 \\
-      & GloVe + Transformer  & 15.1 & 12.9 \\
-      & RoBERTa + LSTM  & 14.9 & 13.0 \\
-      & Transformer (first 512 tokens)  & 15.3 & 13.6 \\
-      & Transformer (location-aware) & 15.1 & 13.5  \\
-      \\
-      \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\section{Model Architecture}
-
-\subsection{Model Inputs}
-
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
-
-\subsubsection{Image Embedding}
-
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
-
-\subsubsection{Article Embedding}
-
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
-\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
-representation, the bidirectionality and the attention mechanism in the
-transformer allow a word to have different vector representations depending on
-the surrounding context.
-
-The largest GloVe model has a vocabulary size of 1.2 million. Although this is
-large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
-encode any word that can be written in Unicode characters.
-
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
-\end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
-
-One limitation of RoBERTa is that the maximum length of the input sequence is
-512. For GoodNews, we simply encode the first 512 tokens of the article. For
-NYTimes800k, since we have the image position, we concatenate the title, the
-first paragraph, and as many paragraphs above and below the image as we can
-fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
-
-\subsection{Decoder}
-
-\subsubsection{Dynamic Convolutions}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}. We don't have the computational resource to study
-the performance of GPT-2.
-
-\subsubsection{Adaptive Softmax}
-
-To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
-The two attended representations are then concatenated and fed as input to
-the self-attention layer.
-
-\section{Experiments}
-
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
-will made public on GitHub.
-
-Table \ref{tab:results-goodnews} shows the results on the original GoodNews
-and NYTimes800k datasets.
-
-\begin{table}[t]
-	\caption {Model complexity: Number of trainable parameters}
-	\label{tab:models}
-	\centering
-	\begin{tabular}{lllllll}
-		\toprule
-        & Parameters \\
-      \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-        + faces & 171M \\
-      %   + names & 175M \\
-      %   + faces + names & 192M \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 paper/section_5_experiments.tex
Split paper into multiple files

--- 2019-11-12 paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{multirow} % creates cells that span multiple rows in a table
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm} % bold fonts for math symbols
-\usepackage{booktabs}
-\usepackage[export]{adjustbox} % adds a frame around figures
-\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
-\usepackage{multirow} % merge multiple rows
-\usepackage{tabularx} % for 'tabularx' environment
-\usepackage{caption} % controls spacing between caption and table
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-
-%%%%%%%%% TITLE - suggestions and candidates
-\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
-\title{Transforming Entities for News Image Captions}
-
-\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
-Australian National University\\
-{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-   We propose an end-to-end model to generate image captions in news articles.
-   By combining the transformer architecture, byte-pair encoding, and
-   pretrained embeddings from three different modalities (RoBERTa for text,
-   ResNet-152 for images, and FaceNet for faces), our system is able to
-   describe an image with specific named entities mentioned in the article. Our
-   model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
-   outperforming the previous state-of-art CIDEr of 13. We also introduce the
-   NYTimes800k dataset, the largest news image captioning dataset to date.
-   NYTimes800k is an extended version of GoodNews with higher-quality articles and
-   metadata that allow us to study the importance of the image location within
-   the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
-   source code are available from
-   \href{https://github.com}{https://github.com/anonymized-link}.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
-Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
-
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
-
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
-
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
-results on many natural language understanding benchmarks including GLUE
-\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
-\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
-
-\begin{figure}[t]
-   \begin{center}
-      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-   \end{center}
-      \caption{Our transformer model attends to embeddings from three different
-      domains (image patches, faces, and article text). Using byte-pair
-      encoding, the model can then directly produce a caption containing
-      specific named entities without the use of templates.}
-   \label{fig:long}
-   \label{fig:onecol}
-\end{figure}
-
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
-
-The goal of this paper is to make use of these recent developments, along with
-their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
-
-\begin{enumerate}
-   \item We introduce NYTimes800k, the largest news image captioning dataset to
-   date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
-   but we write a custom parser to collect higher-quality articles and metadata
-   such as the location of an image within the page.
-
-   \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
-
-   \item We provide a detailed model analysis, deconstructing the most
-   important modeling components and quantifying the incremental contribution
-   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
-   METEOR, and CIDEr; but also to other linguistic measures like readability
-   scores, caption length, and recall of rare names.
-\end{enumerate}
-
-\section{Related Works}
-
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
-\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
-image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
-Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
-
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
-extractive methods that use n-gram models to combine existing phrases
-\cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
-
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
-for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
-
-Transformers are still scarcely used in image captioning. They have been shown
-to yield competitive results in generating generic MS COCO captions
-\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
-\cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
-extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
-
-BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
-
-In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
-\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
-derived from the image itself. When attending to more than one modality, there
-are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
-
-\section{Datasets}
-
-\subsection{GoodNews}
-
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
-dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-
-% \begin{table}[t]
-% 	\caption {Summary of datasets}
-% 	\label{tab:datasets}
-% 	\centering
-% 	\begin{tabular}{llll}
-% 		\toprule
-% 		  & GoodNews  & GoodNews+ &   NYTimes800k \\
-% 		\midrule
-%       No. of articles & 241 808 & 241 808 & 445 828 \\
-%       No. of images   & 462 642 & 440 112 & 794 085 \\
-%       Article length & 451 & 963 & 974 \\
-%       Caption length & 18 & 18 & 18 \\
-%       Start month & Jan 10 & Jan 10 & Mar 05\\
-%       End month & Jul 18 & Jul 18 & Sep 19 \\
-% 		\bottomrule
-% 	\end{tabular}
-% \end{table}
-
-\begin{table}[t]
-	\caption {Summary of news captioning datasets}
-	\label{tab:datasets}
-	\centering
-	\begin{tabularx}{\linewidth}{lXX}
-		\toprule
-		  & GoodNews  &   NYTimes800k \\
-		\midrule
-      Number of articles & 257 033 & 445 819 \\
-      Number of images   & 462 642 & 794 044 \\
-      Average article length & 451 & 974 \\
-      Average caption length & 18 & 18 \\
-      Collection start month & Jan 10 & Mar 05\\
-      Collection end month & Mar 18 & Sep 19 \\
-      \midrule
-      \% of words that are \\
-      \quad -- nouns & 16\% & 16\% \\
-      \quad -- pronouns & 1\% & 1\% \\
-      \quad -- proper nouns & 23\% & 22\% \\
-      \quad -- verbs & 9\% & 9\%  \\
-      \quad -- adjectives & 4\% & 4\% \\
-      \quad -- named entities & 27\% & 26\% \\
-      \quad -- personal names & 9\% & 9\% \\
-      \midrule
-      \% of captions with \\
-      \quad -- named entities & 97\% & 96\% \\
-      \quad -- personal names & 68\% & 68\% \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
-
-\subsection{NYTimes800k}
-
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
-   \end{center}
-      \caption{Co-occurrence of faces and personal names in NYTimes800k
-               training data. The blue bars count how many images containing a
-               certain number of faces. The orange bars count how many captions
-               containing a certain number of personal names.}
-   \label{fig:faces}
-\end{figure}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
-
-\begin{itemize}
-   \item By increasing the collection period to the last 14 years (March 2005
-   -- September 2019), NYTimes800k contains 80\% more articles and images, thus
-   becoming the largest news image captioning dataset.
-   \item Using our custom parser, articles in NYTimes800k contain the full text
-   with no missing paragraphs.
-   \item NYTimes800k contains only English articles.
-   \item We are careful to include only images that are part of the main
-   article.
-   \item Unlike GoodNews, we also collect information about where an image is
-   located in the corresponding article. Most news articles have one image at
-   the top that relates to the key topic. However 39\% of the articles have at
-   least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
-\end{itemize}
-
-Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
-\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
-personal names. One important observation is that the majority of captions
-contain at most four names.
-
-\begin{table}[t]
-	\caption {NYTimes800k training, validation, and test splits}
-	\label{tab:splits}
-	\centering
-	\begin{tabularx}{\linewidth}{lXXX}
-		\toprule
-		  & Training  &   Validation & Test \\
-		\midrule
-      Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
-      Start month & Mar 15 & May 19 & Jun 19 \\
-      End month & Apr 19 & May 19 & Aug 19 \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
-articles in the final three months of the collection period, from June to
-August 2019. This has two advantages over the random split used in GoodNews.
-Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
-before. In particular, out of the 100K proper nouns in the test captions, 4\%
-never appear in any training captions. Half of these also never appear in any
-training article. Thus splitting by time allows us study how well the model can
-generate rare names.
+% !TEX root = main.tex
 
@@
 
-\section{Model Architecture}
-
-\subsection{Model Inputs}
-
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
-
-\subsubsection{Image Embedding}
-
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
-
-\subsubsection{Article Embedding}
-
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
-\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
-representation, the bidirectionality and the attention mechanism in the
-transformer allow a word to have different vector representations depending on
-the surrounding context.
-
-The largest GloVe model has a vocabulary size of 1.2 million. Although this is
-large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
-encode any word that can be written in Unicode characters.
-
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
-\end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
-
-One limitation of RoBERTa is that the maximum length of the input sequence is
-512. For GoodNews, we simply encode the first 512 tokens of the article. For
-NYTimes800k, since we have the image position, we concatenate the title, the
-first paragraph, and as many paragraphs above and below the image as we can
-fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
-
-\subsection{Decoder}
-
-\subsubsection{Dynamic Convolutions}
-
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}.
-
-In the standard self-attention module, the input embedding $\bm{x} \in
-\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
-$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
-weighted sum of the values, where the weights are obtained from the dot product
-between the key and value:
-\begin{IEEEeqnarray*}{lCl}
-   \text{Attention}(\bm{x}) &=&
-   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
-\end{IEEEeqnarray*}
-
 \begin{table*}[t]
@@
 \end{table*}
-
-\subsubsection{Adaptive Softmax}
-
-The BPE vocabulary size is 50265. To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
-\cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
-of the three attended representations are then concatenated and fed as input to
-the self-attention layer.
 
@@
 and still use simpler language (higher Flesch reading ease).
-
-\section{Conclusion}
-
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{paper}
-}
-
-\end{document}

### 2019-11-12 newser/models/decoder_flattened.py
Restore DynamicConvDecoder

@@ -504,12 +504,7 @@ class DynamicConvDecoderLayer(DecoderLayer):
             dropout=attention_dropout)
         self.context_attn_lns['article'] = nn.LayerNorm(self.embed_dim)
 
-        self.context_attns['faces'] = MultiHeadAttention(
-            self.embed_dim, decoder_attention_heads, kdim=512, vdim=512,
-            dropout=attention_dropout)
-        self.context_attn_lns['faces'] = nn.LayerNorm(self.embed_dim)
-
-        context_size = self.embed_dim * 3
+        context_size = self.embed_dim * 2
 
         self.context_fc = GehringLinear(context_size, self.embed_dim)
 
@@ -581,25 +576,6 @@ class DynamicConvDecoderLayer(DecoderLayer):
             self.context_attn_lns['article'], X_article, after=True)
 
         X_contexts.append(X_article)
-
-        # Face attention
-        residual = X
-        X_faces = self.maybe_layer_norm(
-            self.context_attn_lns['faces'], X, before=True)
-        X_faces, attn = self.context_attns['faces'](
-            query=X_faces,
-            key=contexts['faces'],
-            value=contexts['faces'],
-            key_padding_mask=contexts['faces_mask'],
-            incremental_state=None,
-            static_kv=True,
-            need_weights=(not self.training and self.need_attn))
-        X_faces = F.dropout(X_faces, p=self.dropout,
-                            training=self.training)
-        X_faces = residual + X_faces
-        X_faces = self.maybe_layer_norm(
-            self.context_attn_lns['faces'], X_faces, after=True)
-        X_contexts.append(X_faces)
 
         X_context = torch.cat(X_contexts, dim=-1)
         X = self.context_fc(X_context)

### 2019-11-12 paper/section_5_experiments.tex
Update results

@@
       \cmidrule{2-9}
-      % & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
       % & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
       % & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & GloVe + LSTM &  &  &  &  &  &  &  \\
-      & GloVe + Transformer &  &  &  &  &  &  &  \\
+      & GloVe + LSTM & 14.0 & 6.52 & 3.41 & 2.03 & 13.7 & 5.57 & 14.3 \\
+      & GloVe + Transformer & 18.3 & 9.49 & 5.45 & 3.43 & 17.0 & 7.52 & 25.7 \\
       & RoBERTa + LSTM &  &  &  &  &  &  &   \\
@@
       \cmidrule{2-8}
-      & GloVe + LSTM & & &  &  & -- & --  \\
-      & GloVe + Transformer & & &  &  & -- & -- \\
+      & GloVe + LSTM & 7.26\% & 11.1\% & 5.76\% & 9.48\%  & -- & --  \\
+      & GloVe + Transformer & 10.9\% & 14.4\% & 10.7\% & 14.7\% & -- & -- \\
       & RoBERTa + LSTM &  &  &  &  & -- & -- \\
@@
       \cmidrule{2-5}
-      & GloVe + LSTM &  &  \\
-      & GloVe + Transformer &  &  \\
+      & GloVe + LSTM & 13.8 & 89.6 & 77.5 \\
+      & GloVe + Transformer & 15.5 & 88.5 & 73.9 \\
       & RoBERTa + LSTM &  &   \\

### 2019-11-13 newser/models/transformer_pointer.py
Check for no loss

@@ -167,6 +167,9 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
 
         loss = entity_loss + copy_loss
 
+        if not loss.requires_grad:
+            loss = None
+
         if not torch.isnan(gen_loss):
             self.batch_history['gen_loss'] += gen_loss.item()
         if not torch.isnan(entity_loss):

### 2019-11-13 paper/section_1_intro.tex
Add placeholder for unweighted BERT

@@
 
-Most existing captioning systems can only generate a generic description of an
+Most existing \rev{captioning systems can only generate a} \eat{ generic}
+ description
+of an
 image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,

### 2019-11-13 paper/section_5_experiments.tex
Add a placeholder for example captions
Add placeholder for unweighted BERT

--- 2019-11-12 paper/section_5_experiments.tex
@@
       \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
       & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.66 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
@@
       \cmidrule{2-9}
-      % & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
       % & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
       % & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & GloVe + LSTM &  &  &  &  &  &  &  \\
-      & GloVe + Transformer &  &  &  &  &  &  &  \\
-      & RoBERTa + LSTM &  &  &  &  &  &  &   \\
-      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      & \quad + faces & 22.4 & 13.6 & 8.84 & 6.10 & 21.3 & 10.3 & 53.9 \\ % Final
-      & \quad\quad + copying \\
+      & LSTM + GloVe & 14.0 & 6.52 & 3.41 & 2.03 & 13.7 & 5.57 & 14.3 \\
+      & Transformer + GloVe & 18.3 & 9.49 & 5.45 & 3.43 & 17.0 & 7.52 & 25.7 \\
+      & LSTM + weighted RoBERTa &  &  &  &  &  &  &   \\
+      \cmidrule{2-9}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
+      & \quad\quad + face attention & 22.4 & 13.6 & 8.84 & 6.10 & 21.3 & 10.3 & 53.9 \\ % Final
+      & \quad\quad\quad + copy mechanism \\
       \midrule
-      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      & RoBERTa + Transformer & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & \quad + location-aware & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \quad\quad + faces & 22.1 & 13.6 & 9.05 & 6.41 & 21.7 & 10.4 & 54.7 \\ % Final
-      & \quad\quad\quad + copying \\
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & LSTM + GloVe & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
+      & Transformer + GloVe & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
+      & LSTM + weighted RoBERTa & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
+      \cmidrule{2-9}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
+      & \quad\quad + location-aware & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
+      & \quad\quad\quad + face attention & 22.1 & 13.6 & 9.05 & 6.41 & 21.7 & 10.4 & 54.7 \\ % Final
+      & \quad\quad\quad\quad + copy mechanism \\
       \bottomrule
@@
       \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
       & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
@@
       \cmidrule{2-8}
-      & GloVe + LSTM & & &  &  & -- & --  \\
-      & GloVe + Transformer & & &  &  & -- & -- \\
-      & RoBERTa + LSTM & &  &  &  & -- & -- \\
-      & RoBERTa + Transformer & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
-      & \quad + faces & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
-      & \quad\quad + copying \\
+      & LSTM + GloVe & 7.26\% & 11.1\% & 5.76\% & 9.48\%  & -- & --  \\
+      & Transformer + GloVe & 10.9\% & 14.4\% & 10.7\% & 14.7\% & -- & -- \\
+      & LSTM + weighted RoBERTa &  &  &  &  & -- & -- \\
+      \cmidrule{2-8}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
+      & \quad\quad + face attention & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
+      & \quad\quad\quad + copy mechanism \\
       \midrule
-      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
       & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
       & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
-      & RoBERTa + LSTM & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
-      & RoBERTa + Transformer & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
-      & \quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
-      & \quad\quad + faces & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
-      & \quad\quad\quad + copying \\
+      & LSTM + weighted RoBERTa & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
+      \cmidrule{2-8}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
+      & \quad\quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
+      & \quad\quad\quad + face attention & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
+      & \quad\quad\quad\quad + copy mechanism \\
 		\bottomrule
@@
       \midrule
-      GloVe + LSTM & 157M \\
-      GloVe + Transformer & 148M \\
-      RoBERTa + LSTM & 159M \\
-      RoBERTa + Transformer & 154M \\
-      \quad + faces & 171M \\
-      \quad\quad + copying & 207M \\
+      LSTM + GloVe & 157M \\
+      Transformer + GloVe & 148M \\
+      LSTM + weighted RoBERTa & 159M \\
+      \midrule
+      Transformer + RoBERTa & 154M \\
+      \quad + weighted RoBERTa & 154M \\
+      \quad\quad + face attention & 171M \\
+      \quad\quad\quad + copy mechanism & 207M \\
 		\bottomrule
@@
 \subsection{Results}
+
+\begin{figure*}[t]
+   \begin{center}
+   \fbox{\rule{0pt}{3in} \rule{.9\linewidth}{0pt}}
+   \end{center}
+      \caption{Example captions with success and failure cases.}
+   \label{fig:short}
+\end{figure*}
 
@@
       \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      \multirow{10}{*}{\rotatebox[origin=c]{90}{GoodNews}}
       & Ground Truths & 18.1 & 94.9 & 65.4 \\
@@
       \cmidrule{2-5}
-      & GloVe + LSTM &  &  \\
-      & GloVe + Transformer &  &  \\
-      & RoBERTa + LSTM &  &   \\
-      & RoBERTa + Transformer & 15.5 & 91.0 & 72.0 \\
-      & \quad + faces & 15.5 & 90.7 & 71.9 \\
-      & \quad\quad + copying \\
+      & Transformer + RoBERTa \\
+      & LSTM + GloVe & 13.8 & 89.6 & 77.5 \\
+      & Transformer + GloVe & 15.5 & 88.5 & 73.9 \\
+      & LSTM + weighted RoBERTa &  &   \\
+      \cmidrule{2-5}
+      & \quad + weighted RoBERTa & 15.5 & 91.0 & 72.0 \\
+      & \quad\quad + face attention & 15.5 & 90.7 & 71.9 \\
+      & \quad\quad\quad + copy mechanism \\
       \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
       & Ground Truths & 18.4 & 94.6 & 63.9 \\
-      & GloVe + LSTM  & 13.8 & 89.0 & 77.8 \\
-      & GloVe + Transformer  & 15.1 & 88.6 & 73.8 \\
-      & RoBERTa + LSTM  & 14.9 & 90.2 & 72.6 \\
-      & RoBERTa + Transformer  & 15.3 & 91.5 & 70.4 \\
-      & \quad + location-aware & 15.1 & 91.7 & 70.4  \\
-      & \quad\quad + faces & 15.2 & 91.6 & 70.5 \\
-      & \quad\quad\quad + copying \\
+      & LSTM + GloVe  & 13.8 & 89.0 & 77.8 \\
+      & Transformer + GloVe  & 15.1 & 88.6 & 73.8 \\
+      & LSTM + weighted RoBERTa  & 14.9 & 90.2 & 72.6 \\
+      \cmidrule{2-5}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa  & 15.3 & 91.5 & 70.4 \\
+      & \quad\quad + location-aware & 15.1 & 91.7 & 70.4  \\
+      & \quad\quad\quad + face attention & 15.2 & 91.6 & 70.5 \\
+      & \quad\quad\quad\quad + copy mechanism \\
 		\bottomrule

### 2019-11-13 newser/models/transformer_pointer.py
Avoid repeated copying

@@ -503,6 +503,8 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
 
         Xs = []
 
+        copied_indices_full = caption_ids.new_full((B, 1), -1)
+
         for i in range(gen_len):
             if i == 0:
                 prev_target = {self.index: seed_input}
@@ -651,6 +653,23 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
 
             selected_copy_index = selected_copy_index.unsqueeze(1)
             # selected_copy_index.shape == [batch_size, 1]
+
+            selection = selected_copy_index.expand_as(
+                copied_indices_full[full_active_idx])
+            # selected_copy_index.shape == [batch_size_i, 1]
+
+            has_copied = (
+                selection == copied_indices_full[full_active_idx]).any(dim=1)
+            # has_copied.shape == [batch_size_i]
+
+            should_copy = should_copy & (~has_copied)
+            # should_copy.shape == [batch_size_i]
+
+            copied_indices = selected_copy_index.new_full((B, 1), -1)
+            copied_indices[full_active_idx.nonzero().squeeze(1)[should_copy]] = \
+                selected_copy_index[should_copy]
+            copied_indices_full = torch.cat(
+                [copied_indices_full, copied_indices], dim=1)
 
             copy_prob = selected_copy_prob.new_zeros(B, 1)
             copy_prob[full_active_idx] = selected_copy_prob

### 2019-11-13 paper/section_1_intro.tex
Add intro changes from Alex

--- 2019-11-12 paper/section_1_intro.tex
@@
 
-Most existing captioning systems can only generate a generic description of an
-image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
+The internet is home to a huge number of images, many of which lack useful
+captions. A growing body of work seeks to automatically generate captions that
+describe the objects and relationships using only visual cues extracted from
+the image itself~\cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
 Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
-Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
-cannot handle an open vocabulary and early captioning datasets such as MS COCO
-\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
-\cite{Young2014FromID} were annotated using only visual cues present in the
-image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
-real-life captions written by professional journalists. However, existing
-models that are trained on these news datasets still need to rely on either
-extractive methods or templates to insert named entities.
+Anderson2017BottomUpAT, Cornia2019ShowCT}. While generic image descriptions
+have their uses, such as for individuals with vision impairments, they are
+often of less benefit to the average user. To produce more useful image
+captions we need to go beyond generic descriptions and introduce information
+that cannot be gleaned directly from the image alone. Fortunately, many images
+have an associated context such as a news article, web page, or social
+media post, which give the image greater meaning than can be extracted from its
+pixels. To generate captions that go beyond generic description and actually
+add information that could not be gleaned from the image alone we must take
+this context into account. We focus on the news image captioning task in order
+to design practical methods for exploiting contextual information.
 
-This motivates us to ask whether it is possible to design a fully end-to-end
-model for news image captioning. The model would need to 1) attend to
-contextual cues from different modalities and 2) generate captions that contain
-specific information including rare proper names that have not been seen in the
-training data. To answer this, we look at the recent development in
-sequence-to-sequence architectures and language representation learning.
+\eat{However, images on the internet are
+often associated with a context such as a news article, web page, or social
+media post, which give the image greater meaning than can be extracted from its
+pixels. To generate captions that go beyond generic description and actually
+add information that could not be gleaned from the image alone we must take
+this context into account.}
 
-The most successful family of models in the field of natural language
-processing (NLP) are the transformer networks, which consist of layers of
-self-attention and feed-forward connections stacked on top of each other
-\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
-outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
+News image captioning is an interesting instance of contextual captioning
+where news articles provide context to images.
+
+Captions for news images, such as the example in Figure~\ref{fig:teaser},
+typically contain details which cannot be derived from the image alone. They
+also frequently contain proper nouns such as names of people, places, and
+organisations -- in many cases these proper nouns are rare (most people and
+places do not have many news articles written about them). A system capable of
+generating high quality news captions should therefor make extensive use of the
+provided context and be tuned for generating rare proper nouns. Existing
+approaches to news image captioning~\cite{Tariq2017ACE,
+Ramisa2016BreakingNewsAA,
+	Biten2019GoodNews}  rely on text extraction or
+template filling to deal with rare contextual terms such as names of people and
+organisations. This makes them relatively inflexibility and means they cannot
+be trained end-to-end. Moreover, existing approaches do not include specialised
+visual models for frequent nouns -- experiments on the MSCOCO dataset have
+shown
+that pre-trained object detectors tuned for frequent nouns
+lead to more accurate captions~\cite{}.
+
+One tool that has had seen recent successes in many natural language processing
+tasks is the transformer neural network.
+%\sout{processing, which consist of layers of
+%	self-attention and feed-forward connections stacked on top of each other
+%	\cite{Vaswani2017AttentionIA}. Transformers have}
+Transformers have been show to consistently
+outperforming Recurrent Neural Network architectures in language modeling
+\cite{Radford2019LanguageMA},
 story generation \cite{Fan2018HierarchicalNS}, summarization
 \cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-There are theoretical justifications that transformers could be universal
-approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.
+%\sout{There are theoretical justifications that transformers could be universal
+%	approximations of sequence-to-sequence functions
+%\cite{Anonymous2020AreTU}.}
+Furthermore, transformer based models such as BERT \cite{Devlin2019BERT}, XLM
+\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
+\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT} have been shown to
+produce high level text representations suitable for transfer learning.
+Furthermore, using byte-pair
+encoding (BPE) \cite{Sennrich2015NeuralMT} to represent uncommon words as a
+sequence of subword units can enable the transformer function in an open
+vocabulary setting.
 
-Furthermore, transformers have led to the rise of unsupervised language
-representation learning such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
-embeddings provided by these methods have helped establish new state-of-the-art
+\eat{The contextual word
+	embeddings provided by these methods have helped establish new
+	state-of-the-art
 	results on many natural language understanding benchmarks including GLUE
@@
 	\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
-baselines in many cases.
+	baselines in many cases.}
+
+\eat{In parallel to the development of these pre-training methods, many novel
+techniques have been proposed to improve training convergence and handle more
+diverse data inputs. The most significant contribution is the use of byte-pair
+encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
+sequence of subword units, thus giving models the ability to handle an open
+vocabulary.}
 
@@
 	\label{fig:long}
-   \label{fig:onecol}
+	\label{fig:teaser}
 \end{figure}
 
-In parallel to the development of these pre-training methods, many novel
-techniques have been proposed to improve training convergence and handle more
-diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
-sequence of subword units, thus giving models the ability to handle an open
-vocabulary.
+This motivates our novel fully end-to-end
+model for news image captioning that 1) combines specialised modules for
+incorporating and selectively attending to image features, human faces, and
+news article text and
+2) applies a state-of-the-art sequence generation model which is able to
+generate rare tokens, such as proper names, even when they do not form part of
+the
+training data. Our model relies on a novel combination of sequence-to-sequence
+architectures, language representation learning, and
+vision systems.
 
-The goal of this paper is to make use of these recent developments, along with
+%The key components of our approach are selectively attending to different
+%aspects of the two modalities: image
+%regions, faces, and text sequences.
+%Using powerful pre-trained contextual language models to represent news
+%articles -- allowing articles with text not see during training  tuples
+%required for training.
+%Using sub-word units, which when combined with pre-training, allow for the
+%generation of tokens not seen during training.
+
+%\sout{
+%Most existing captioning systems can only generate a generic description
+%of an
+%image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
+%Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
+%Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
+%cannot handle an open vocabulary and early captioning datasets such as MS COCO
+%\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
+%\cite{Young2014FromID} were annotated using only visual cues present in the
+%image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
+%\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
+%real-life captions written by professional journalists. However, existing
+%models that are trained on these news datasets still need to rely on either
+%extractive methods or templates to insert named entities.}
+
+In this paper we carefully consider the news image captioning problem and
+select a set of modelling tools which we combine into a novel architecture that
+sets a new state-of-the-art result. Our main contributions are threefold:
+
+\eat{The goal of this paper is to make use of these recent developments, along
+with
 their bags of tricks, to carefully design a captioning system most appropriate
-for news images. Our main contributions are thus threefold:
+for news images.}
 
@@
    date, containing 446K articles and 794K images with captions from The New
-   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
+   York Times spanning 14 years. NYTimes800k builds on the GoodNews dataset;
    but we write a custom parser to collect higher-quality articles and metadata

### 2019-11-13 paper/section_4_datasets.tex
Add dataset changes from Alex

@@
 As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning \cite{Biten2019GoodNews}. Each sample in the
+dataset on news image captioning~\cite{Biten2019GoodNews}. Each example in the
 dataset is a triplet containing an article, an image, and a caption. Since only
-the article text and captions were publicly released, we had to crawl the
-images ourselves. Out of the 466K image URLs provided by
-\cite{Biten2019GoodNews}, we were able to crawl 463K images, or 99.2\% of the
-original dataset. The remaining are broken links. As part of the quality check,
-we also wrote a custom parser to re-extract the articles in the same period
-from the original web pages, with the help of The New York Times
-API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
+the article text, captions, and image URLs were publicly released
+the images had to be downloaded from the original source. Out of the 466K image
+URLs provided by
+\cite{Biten2019GoodNews}, we were able to download 463K images, or 99.2\% of the
+original dataset -- the remaining are broken links.
 
-From the recollection, we observe that the average length of an article in
-GoodNews is 451 words, while it is 963 in our recollected dataset. Thus half of
-the article body is missing in GoodNews. This includes the first few paragraphs
-that might contain important information about the top caption. Looking through
-the publicly released code, we found that this is because the original parser
-used by \cite{Biten2019GoodNews} was designed to extract articles from a
-generic online news source and it fails to recognize certain HTML tags used
-specifically in New York Times web pages.
-
-In addition, we also found some noisy samples in GoodNews. This includes a
-small number of non-English articles, and captioned images from the
-recommendation sidebar which are not related to the main article.
-
-Despite the above limitations, we still use the original GoodNews dataset and
-train-validation-test split in our experiments, in order to make comparison to
-previous works easier. Using the original split, we have 421K training, 18K
-validation, and 23K test captions. Given that the random split was done at the
-caption level, it is possible for a training and test caption to share the same
-article text.
+We use this 99.2\% sample of the GoodNews dataset and the
+train-validation-test split provided by~\cite{Biten2019GoodNews}. This split
+consists of 421K training, 18K validation, and 23K test captions. Note that
+this split was done on captions, so it is possible for a training and test
+caption to share the same article text (since articles have multiple images).
 
@@
 
-At the same time, we also constructed a bigger and higher-quality dataset,
-which we call NYTimes800k. A comparison between GoodNews and NYTimes800k is
+We also constructed the NYTimes800k which is a larger and more complete dataset
+of New York Times articles, images, and captions. The construction of this
+dataset was motivated by the desire to clean up data quality issues in the
+GoodNews dataset, collect a larger dataset, and include fine grained context
+such as the images location in the article.
+
+We observed that many of the articles that constitute the GoodNews dataset had
+only been partially extracted since the generic article extractor employed
+failed to recognise certain HTML tags used
+specifically by the New York Times. To collect the full articles we
+implemented a custom parser using The New York Times public
+API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
+After this recollection, we observe that the average article is 963 words while
+the the average length of an article in
+GoodNews is 451 words. Importantly the missing text may include the first few
+paragraphs
+which often contain important information for captioning images.
+
+In addition, we also found that GoodNews contained a
+small number of non-English articles, and captioned images from the
+recommendation sidebar which are not related to the main article. These were
+filtered out in the construction of NYTimes880k.
+
+A comparison between GoodNews and NYTimes800k is
 summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several

### 2019-11-13 paper/section_3_model.tex
Add placeholder for unweighted BERT
Add decoder equation

@@
 
-\subsection{Model Inputs}
+\subsection{Encoders}
 
@@
 \cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
+pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 7
 \times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
@@
 \begin{IEEEeqnarray*}{lCl}
-   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
+   \bx_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
 \end{IEEEeqnarray*}
-where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
+where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
 and $w_i$ are learnable weights.
@@
 fit, until we reach the 512 token limit. Note that since we are using BPE, a
-token can be part of a word. On average, we can only encode ...... words of
-the article.
+word might consist of many tokens. On average, we can only encode ...... words
+of the article.
 
@@
 FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
+\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_F \in
 \mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
@@
 \subsection{Decoder}
+
+The decoder is a function that estimates $p(y_t)$, the probability of the next
+token, conditional on the past and the context embeddings $\bx_I$, $\bx_T$, and
+$\bx_F$:
+\begin{IEEEeqnarray*}{lCl}
+   p(y_t) &=& \mathbb{P}(Y_t = y_t | y_{<t}, \bx_I, \bx_T, \bx_F)
+\end{IEEEeqnarray*}
 
@@
 
-In the standard self-attention module, the input embedding $\bm{x} \in
+In the standard self-attention module, the input embedding $\bx \in
 \mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
@@
 \begin{IEEEeqnarray*}{lCl}
-   \text{Attention}(\bm{x}) &=&
+   \text{Attention}(\bx) &=&
    \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
 \end{IEEEeqnarray*}
+
+\subsubsection{Encoder Attention}
+
+For each generation step, we use the Scalar-Dot-Product attention
+\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
+of the three attended representations are then concatenated and fed as input to
+the self-attention layer.
+
+\subsection{Bag of Tricks}
 
@@
 \cite{Vaswani2017AttentionIA} to represent the position of each token.
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
-of the three attended representations are then concatenated and fed as input to
-the self-attention layer.

### 2019-11-13 paper/section_3_model.tex
Work on attention section

@@
 Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
+sequences of embeddings, $\bg_i \in \mathbb{R}^{2048 \times S}$ for $i \in
 \{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
@@
 \begin{IEEEeqnarray*}{lCl}
-   \bx_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
+   \bx_T &=& \sum_{i=0}^{24} \alpha_i \bg_i
 \end{IEEEeqnarray*}
 where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $w_i$ are learnable weights.
+and $\alpha_i$ are learnable weights.
 
@@
 \begin{IEEEeqnarray*}{lCl}
-   p(y_t) &=& \mathbb{P}(Y_t = y_t | y_{<t}, \bx_I, \bx_T, \bx_F)
+   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bx_I, \bx_T, \bx_F)
 \end{IEEEeqnarray*}
+In our architecture, the decoder consists of four layers of transformer blocks.
+In each block, the conditioning on past tokens is computed using dynamic
+convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
+computed using Scalar-Dot-Product attention \cite{Vaswani2017AttentionIA}.
+
+\subsubsection{Scalar-Dot-Product Attention}
+
+Let $\bh_t$ be the current hidden state. We first do a linear projection of
+$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
+all three have the same dimension:
+\begin{IEEEeqnarray*}{lCl}
+   \bq_T &=& W_{Iq} \, \bh_t \\
+   \bk_T &=& W_{Ik} \, \bx_I \\
+   \bv_T &=& W_{Iv} \, \bx_I
+\end{IEEEeqnarray*}
+Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
+obtained from the dot product between the key and value:
+\begin{IEEEeqnarray*}{lCl}
+   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
+\end{IEEEeqnarray*}
+We use the same attention mechanism to obtain the attended article $\bx_T'$
+and the attended face $\bx_F'$. These three are then concatenated and fed
+through a feedforward layer:
+\begin{IEEEeqnarray*}{lCl}
+   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
+   \bx_O &=& \text{LayerNorm}(X_C + W_O \, \text{ReLU}(W_C \, \bx_C' + \bb_C) + \bb_O)
+\end{IEEEeqnarray*}
+
+For each generation step, we use the Scalar-Dot-Product attention
+\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
+of the three attended representations are then concatenated and fed as input to
+the self-attention layer.
 
@@
 \mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
-$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
-weighted sum of the values, where the weights are obtained from the dot product
-between the key and value:
-\begin{IEEEeqnarray*}{lCl}
-   \text{Attention}(\bx) &=&
-   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
-\end{IEEEeqnarray*}
-
-\subsubsection{Encoder Attention}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
-of the three attended representations are then concatenated and fed as input to
-the self-attention layer.
+$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$.
 

### 2019-11-13 paper/section_5_experiments.tex
Move big tables to last page

@@
 % !TEX root = main.tex
-
-\begin{table*}[t]
-   \caption {BLEU, ROUGE, METEOR, and CIDEr metrics on GoodNews and
-             NYTimes800k.}
-
-	\label{tab:results}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXXX}
-		\toprule
-		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.66 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
-      \cmidrule{2-9}
-      % & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
-      % & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
-      & LSTM + GloVe & 14.0 & 6.52 & 3.41 & 2.03 & 13.7 & 5.57 & 14.3 \\
-      & Transformer + GloVe & 18.3 & 9.49 & 5.45 & 3.43 & 17.0 & 7.52 & 25.7 \\
-      & LSTM + weighted RoBERTa &  &  &  &  &  &  &   \\
-      \cmidrule{2-9}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
-      & \quad\quad + face attention & 22.4 & 13.6 & 8.84 & 6.10 & 21.3 & 10.3 & 53.9 \\ % Final
-      & \quad\quad\quad + copy mechanism \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & LSTM + GloVe & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
-      & Transformer + GloVe & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
-      & LSTM + weighted RoBERTa & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
-      \cmidrule{2-9}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
-      & \quad\quad + location-aware & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
-      & \quad\quad\quad + face attention & 22.1 & 13.6 & 9.05 & 6.41 & 21.7 & 10.4 & 54.7 \\ % Final
-      & \quad\quad\quad\quad + copy mechanism \\
-      \bottomrule
-	\end{tabularx}
-\end{table*}
-
-\begin{table*}[t]
-   \caption {Named entity, personal name, and rare proper noun recall \&
-             precision on GoodNews and NYTimes800k.}
-	\label{tab:names}
-	\centering
-	\begin{tabularx}{\textwidth}{llXXXXXX}
-		\toprule
-      &  & \multicolumn{2}{c}{Named entities} & \multicolumn{2}{c}{Personal names} & \multicolumn{2}{c}{Rare proper nouns} \\
-      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 5.64\% & 8.87\% & 6.98\% & 11.9\% & -- & -- \\
-      \cmidrule{2-8}
-      & LSTM + GloVe & 7.26\% & 11.1\% & 5.76\% & 9.48\%  & -- & --  \\
-      & Transformer + GloVe & 10.9\% & 14.4\% & 10.7\% & 14.7\% & -- & -- \\
-      & LSTM + weighted RoBERTa &  &  &  &  & -- & -- \\
-      \cmidrule{2-8}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
-      & \quad\quad + face attention & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
-      & \quad\quad\quad + copy mechanism \\
-      \midrule
-      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
-      & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
-      & LSTM + weighted RoBERTa & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
-      \cmidrule{2-8}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
-      & \quad\quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
-      & \quad\quad\quad + face attention & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
-      & \quad\quad\quad\quad + copy mechanism \\
-		\bottomrule
-	\end{tabularx}
-\end{table*}
 
@@
 \subsection{Results}
+
+\begin{table}[t]
+   \caption {Linguistic measures on the generated captions: caption length (CL),
+             type-token ratio (TTR), and Flesch readability ease (FRE).}
+	\label{tab:caption}
+	\centering
+	\begin{tabularx}{\linewidth}{llXXX}
+		\toprule
+       &  &  CL  & TTR & FRE \\
+      \midrule
+      \multirow{10}{*}{\rotatebox[origin=c]{90}{GoodNews}}
+      & Ground Truths & 18.1 & 94.9 & 65.4 \\
+      \cmidrule{2-5}
+      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
+      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
+      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
+      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
+      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
+      \cmidrule{2-5}
+      & Transformer + RoBERTa \\
+      & LSTM + GloVe & 13.8 & 89.6 & 77.5 \\
+      & Transformer + GloVe & 15.5 & 88.5 & 73.9 \\
+      & LSTM + weighted RoBERTa &  &   \\
+      \cmidrule{2-5}
+      & \quad + weighted RoBERTa & 15.5 & 91.0 & 72.0 \\
+      & \quad\quad + face attention & 15.5 & 90.7 & 71.9 \\
+      & \quad\quad\quad + copy mechanism \\
+      \midrule
+      \multirow{9}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
+      & Ground Truths & 18.4 & 94.6 & 63.9 \\
+      & LSTM + GloVe  & 13.8 & 89.0 & 77.8 \\
+      & Transformer + GloVe  & 15.1 & 88.6 & 73.8 \\
+      & LSTM + weighted RoBERTa  & 14.9 & 90.2 & 72.6 \\
+      \cmidrule{2-5}
+      & Transformer + RoBERTa \\
+      & \quad + weighted RoBERTa  & 15.3 & 91.5 & 70.4 \\
+      & \quad\quad + location-aware & 15.1 & 91.7 & 70.4  \\
+      & \quad\quad\quad + face attention & 15.2 & 91.6 & 70.5 \\
+      & \quad\quad\quad\quad + copy mechanism \\
+		\bottomrule
+	\end{tabularx}
+\end{table}
 
@@
 
-\begin{table}[t]
-   \caption {Linguistic measures on the generated captions: caption length (CL),
-             type-token ratio (TTR), and Flesch readability ease (FRE).}
-	\label{tab:caption}
-	\centering
-	\begin{tabularx}{\linewidth}{llXXX}
-		\toprule
-       &  &  CL  & TTR & FRE \\
-      \midrule
-      \multirow{10}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Ground Truths & 18.1 & 94.9 & 65.4 \\
-      \cmidrule{2-5}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
-      \cmidrule{2-5}
-      & Transformer + RoBERTa \\
-      & LSTM + GloVe & 13.8 & 89.6 & 77.5 \\
-      & Transformer + GloVe & 15.5 & 88.5 & 73.9 \\
-      & LSTM + weighted RoBERTa &  &   \\
-      \cmidrule{2-5}
-      & \quad + weighted RoBERTa & 15.5 & 91.0 & 72.0 \\
-      & \quad\quad + face attention & 15.5 & 90.7 & 71.9 \\
-      & \quad\quad\quad + copy mechanism \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & Ground Truths & 18.4 & 94.6 & 63.9 \\
-      & LSTM + GloVe  & 13.8 & 89.0 & 77.8 \\
-      & Transformer + GloVe  & 15.1 & 88.6 & 73.8 \\
-      & LSTM + weighted RoBERTa  & 14.9 & 90.2 & 72.6 \\
-      \cmidrule{2-5}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa  & 15.3 & 91.5 & 70.4 \\
-      & \quad\quad + location-aware & 15.1 & 91.7 & 70.4  \\
-      & \quad\quad\quad + face attention & 15.2 & 91.6 & 70.5 \\
-      & \quad\quad\quad\quad + copy mechanism \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
 Table \ref{tab:caption} look at the quality of the generated captions. We look

### 2019-11-13 paper/section_0_abstract.tex
Cite pointer-generator paper

@@
     We propose an end-to-end model to generate image captions in news articles.
-    By combining the transformer architecture, byte-pair encoding, and
-    pretrained embeddings from three different modalities (RoBERTa for text,
-    ResNet-152 for images, and FaceNet for faces), our system is able to
-    describe an image with specific named entities mentioned in the article. Our
-    model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
-    outperforming the previous state-of-art CIDEr of 13. We also introduce the
-    NYTimes800k dataset, the largest news image captioning dataset to date.
-    NYTimes800k is an extended version of GoodNews with higher-quality articles and
-    metadata that allow us to study the importance of the image location within
-    the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
-    source code are available from
+    By combining the transformer architecture, byte-pair encoding, copying with
+    multi-headed attention, and pretrained embeddings from three different
+    modalities (RoBERTa for text, ResNet-152 for images, and FaceNet for
+    faces), our system is able to describe an image with specific named
+    entities mentioned in the article. Our model achieves a CIDEr score of 54
+    on the GoodNews dataset, significantly outperforming the previous
+    state-of-art CIDEr of 13. We also introduce the NYTimes800k dataset, the
+    largest news image captioning dataset to date. NYTimes800k is an extended
+    version of GoodNews with higher-quality articles and metadata that allow us
+    to study the importance of the image location within the text. On
+    NYTimes800k, we achieve a CIDEr of 55. Pretrained models and source code
+    are available from
     \href{https://github.com}{https://github.com/anonymized-link}.

### 2019-11-13 paper/section_1_intro.tex
Rearrange figures
Cite pointer-generator paper

@@
 also frequently contain proper nouns such as names of people, places, and
-organisations -- in many cases these proper nouns are rare (most people and
+organizations -- in many cases these proper nouns are rare (most people and
 places do not have many news articles written about them). A system capable of
@@
 template filling to deal with rare contextual terms such as names of people and
-organisations. This makes them relatively inflexibility and means they cannot
-be trained end-to-end. Moreover, existing approaches do not include specialised
+organizations. This makes them relatively inflexibility and means they cannot
+be trained end-to-end. Moreover, existing approaches do not include specialized
 visual models for frequent nouns -- experiments on the MSCOCO dataset have
@@
 lead to more accurate captions~\cite{}.
+
+\begin{figure}[t]
+	\begin{center}
+		\includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
+	\end{center}
+	\caption{Our transformer model attends to embeddings from three different
+		domains (image patches, faces, and article text). Using byte-pair
+		encoding, the model can then directly produce a caption containing
+		specific named entities without the use of templates.}
+	\label{fig:long}
+	\label{fig:teaser}
+\end{figure}
 
@@
 
-\begin{figure}[t]
-	\begin{center}
-		\includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
-	\end{center}
-	\caption{Our transformer model attends to embeddings from three different
-		domains (image patches, faces, and article text). Using byte-pair
-		encoding, the model can then directly produce a caption containing
-		specific named entities without the use of templates.}
-	\label{fig:long}
-	\label{fig:teaser}
-\end{figure}
-
 This motivates our novel fully end-to-end
@@
 In this paper we carefully consider the news image captioning problem and
-select a set of modelling tools which we combine into a novel architecture that
+select a set of modeling tools which we combine into a novel architecture that
 sets a new state-of-the-art result. Our main contributions are threefold:
@@
    \item We build a captioning model that combines the power of transformers,
-   byte-pair encoding, and attention over three different modalities (text,
-   images, and faces). We show that our model achieves state-of-the-art results
-   with a significant margin over previous methods, and in particular, it can
-   generate names not seen during training without the use of templates.
+   byte-pair encoding, copying via multi-headed attention, and attention over
+   three different modalities (text, images, and faces). We show that our model
+   achieves state-of-the-art results with a significant margin over previous
+   methods, and in particular, it can generate names not seen during training
+   without the use of templates.
 

### 2019-11-13 paper/section_5_experiments.tex
Merge linguistic and name metric tables

@@
 
-\begin{table}[t]
-   \caption {Linguistic measures on the generated captions: caption length (CL),
-             type-token ratio (TTR), and Flesch readability ease (FRE).}
-	\label{tab:caption}
-	\centering
-	\begin{tabularx}{\linewidth}{llXXX}
-		\toprule
-       &  &  CL  & TTR & FRE \\
-      \midrule
-      \multirow{10}{*}{\rotatebox[origin=c]{90}{GoodNews}}
-      & Ground Truths & 18.1 & 94.9 & 65.4 \\
-      \cmidrule{2-5}
-      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
-      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
-      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
-      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
-      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
-      \cmidrule{2-5}
-      & Transformer + RoBERTa \\
-      & LSTM + GloVe & 13.8 & 89.6 & 77.5 \\
-      & Transformer + GloVe & 15.5 & 88.5 & 73.9 \\
-      & LSTM + weighted RoBERTa &  &   \\
-      \cmidrule{2-5}
-      & \quad + weighted RoBERTa & 15.5 & 91.0 & 72.0 \\
-      & \quad\quad + face attention & 15.5 & 90.7 & 71.9 \\
-      & \quad\quad\quad + copy mechanism \\
-      \midrule
-      \multirow{9}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
-      & Ground Truths & 18.4 & 94.6 & 63.9 \\
-      & LSTM + GloVe  & 13.8 & 89.0 & 77.8 \\
-      & Transformer + GloVe  & 15.1 & 88.6 & 73.8 \\
-      & LSTM + weighted RoBERTa  & 14.9 & 90.2 & 72.6 \\
-      \cmidrule{2-5}
-      & Transformer + RoBERTa \\
-      & \quad + weighted RoBERTa  & 15.3 & 91.5 & 70.4 \\
-      & \quad\quad + location-aware & 15.1 & 91.7 & 70.4  \\
-      & \quad\quad\quad + face attention & 15.2 & 91.6 & 70.5 \\
-      & \quad\quad\quad\quad + copy mechanism \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
 \begin{figure*}[t]
@@
 
-Table \ref{tab:caption} look at the quality of the generated captions. We look
-at three metrics: caption length, type-token ratio (TTR), and Flesch reading
-ease. TTR is the ratio of the number of unique words to the total number of
-words in a caption. The Flesch reading ease takes into account the number of
-words and syllables and produces a score between 0 and 100, where higher means
-being easier to read.
+Table \ref{tab:names} also looks at the quality of the generated captions. We
+look at three metrics: caption length, type-token ratio (TTR), and Flesch
+reading ease. TTR is the ratio of the number of unique words to the total
+number of words in a caption. The Flesch reading ease takes into account the
+number of words and syllables and produces a score between 0 and 100, where
+higher means being easier to read.
 

### 2019-11-13 paper/section_3_model.tex
Rearrange figures
Cite pointer-generator paper
Rename copying mechanism

@@
 \section{Model Architecture}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Overall architecture of the model.}
-   \label{fig:short}
-\end{figure*}
 
@@
 \cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 7
-\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
-attend to 49 different patches in the image.
+pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 49}$.
+The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
+different patches in the image.
 
@@
 \begin{IEEEeqnarray*}{lCl}
-   \bq_T &=& W_{Iq} \, \bh_t \\
-   \bk_T &=& W_{Ik} \, \bx_I \\
-   \bv_T &=& W_{Iv} \, \bx_I
+   \bq_T &=& \bW_{Iq} \, \bh_t \\
+   \bk_T &=& \bW_{Ik} \, \bx_I \\
+   \bv_T &=& \bW_{Iv} \, \bx_I
 \end{IEEEeqnarray*}
@@
    \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
-   \bx_O &=& \text{LayerNorm}(X_C + W_O \, \text{ReLU}(W_C \, \bx_C' + \bb_C) + \bb_O)
+   \bx_O &=& \text{LayerNorm}(X_C + \bW_O \, \text{ReLU}(\bW_C \, \bx_C' + \bb_C) + \bb_O)
 \end{IEEEeqnarray*}
@@
 
+\subsubsection{Copying with Multi-headed Attention}
+
+Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce
+a copying mechanism using multi-headed attention.
+
 \subsubsection{Adaptive Softmax}

### 2019-11-13 paper/section_5_experiments.tex
Rename copying mechanism

@@
 epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
-learning rate in the first 5\% of the training steps to $10^{-4}$, and
-afterward decays it linearly. Training the full model takes 5 days on one Titan
-V GPU.
+learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
+it linearly afterwards. Training is done with mixed precision to reduce the
+memory footprint. The full model takes 5 days to train on one Titan V GPU.
 
@@
       \quad\quad + face attention & 171M \\
-      \quad\quad\quad + copy mechanism & 207M \\
+      \quad\quad\quad + copying & 207M \\
 		\bottomrule

### 2019-11-13 newser/models/transformer_pointer.py
Report correct loss during evaluation

@@ -167,7 +167,7 @@ class TransformerPointerModel(LoadStateDictWithPrefix, Model):
 
         loss = entity_loss + copy_loss
 
-        if not loss.requires_grad:
+        if self.training and not loss.requires_grad:
             loss = None
 
         if not torch.isnan(gen_loss):

### 2019-11-13 paper/section_4_datasets.tex
Add changes from Alex on datasets

@@
 
-As a starting point, we use the GoodNews dataset, previously the largest
-dataset on news image captioning~\cite{Biten2019GoodNews}. Each example in the
+To compare to existing approaches we use the GoodNews dataset, which until now
+was largest
+dataset for news image captioning~\cite{Biten2019GoodNews}. Each example in the
 dataset is a triplet containing an article, an image, and a caption. Since only
-the article text, captions, and image URLs were publicly released
-the images had to be downloaded from the original source. Out of the 466K image
+the article text, captions, and image URLs are publicly released
+the images need to be downloaded from the original source. Out of the 466K
+image
 URLs provided by
@@
 We use this 99.2\% sample of the GoodNews dataset and the
-train-validation-test split provided by~\cite{Biten2019GoodNews}. This split
-consists of 421K training, 18K validation, and 23K test captions. Note that
-this split was done on captions, so it is possible for a training and test
+train-validation-test split provided by~\cite{Biten2019GoodNews}. There are
+421K training, 18K validation, and 23K test captions. Note that
+this split was performed at the level of captions, so it is possible for a
+training and test
 caption to share the same article text (since articles have multiple images).
@@
 
-We also constructed the NYTimes800k which is a larger and more complete dataset
+We constructed the NYTimes800k which is an 80\% larger and more complete
+dataset
 of New York Times articles, images, and captions. The construction of this
 dataset was motivated by the desire to clean up data quality issues in the
-GoodNews dataset, collect a larger dataset, and include fine grained context
+GoodNews dataset (as described below), collect a larger dataset, and include
+fine grained context
 such as the images location in the article.
 
-We observed that many of the articles that constitute the GoodNews dataset had
-only been partially extracted since the generic article extractor employed
-failed to recognise certain HTML tags used
-specifically by the New York Times. To collect the full articles we
+We observed that many of the articles in the GoodNews dataset had
+been partially extracted when the generic article extractor used
+failed to recognise some of the HTML tags used
+specifically by the New York Times. Importantly, the missing text often
+included the first few
+paragraphs
+which frequently contain important information for captioning images. To
+collect the full articles for the NYTimes800k dataset we
 implemented a custom parser using The New York Times public
 API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}.
-After this recollection, we observe that the average article is 963 words while
-the the average length of an article in
-GoodNews is 451 words. Importantly the missing text may include the first few
-paragraphs
-which often contain important information for captioning images.
-
-In addition, we also found that GoodNews contained a
+After this recollection, we observe that the average article is 963 words in
+comparison to GoodNews where the average length is 451 words. In addition, we
+found that GoodNews contains a
 small number of non-English articles, and captioned images from the
@@
 
-A comparison between GoodNews and NYTimes800k is
-summarized in Table \ref{tab:datasets}. NYTimes800k exhibits several
-advantages:
+Table \ref{tab:datasets} presents a comparison between GoodNews and
+NYTimes800k. NYTimes800k exhibits several advantages:
 
@@
    least one more image somewhere in the middle of text. The image placement
-   and hence the text surrounding the image could be important information for
-   captioning.
+   and hence the text surrounding the image is important information for
+   captioning as we show in our evaluations.
 \end{itemize}
@@
 containing at least one named entity. As shown in Figure \ref{fig:entities},
-the most popular entity type are personal names, comprising a third of all
+the most popular entity type are names of people, comprising a third of all
 named entities. Furthermore, 71\% of training images contain at least one face
-and 68\% of training captions mention at least one personal name. Figure
+and 68\% of training captions mention at least one persons name. Figure
 \ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
@@
 Firstly, it prevents captions in the training and test sets from sharing the
-same context article, thus making it better to see how well the model can
-generalize. Secondly, due of the shift in the coverage of news over time, there
-will be events and people in the test data that have never covered by the news
+same context article, which allows us to evaluate how well the model can
+generalize to new articles. Secondly, due of the shift in the coverage of news
+over time, there
+will be events and people in the test data that have never been covered by the
+news
 before. In particular, out of the 100K proper nouns in the test captions, 4\%

### 2019-11-13 paper/section_3_model.tex
Add new shortcut commands

@@
 \cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 49}$.
+pooling layer, as the image embedding $\bX_I \in \mathbb{R}^{2048 \times 49}$.
 The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
@@
 For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa is a language representation model that provides pretrained contextual
-embeddings for text. It consists of 24 layers of bidirectional transformer
-blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.
-
+RoBERTa, a more carefully trained BERT \cite{Devlin2019BERT}, is a language
+representation model that provides pretrained contextual embeddings for text.
 Unlike GloVe \cite{Pennington2014Glove} and word2vec
@@
 
-Given an input of length $S$, the pretrained RoBERTa encoder will return 25
-sequences of embeddings, $\bg_i \in \mathbb{R}^{2048 \times S}$ for $i \in
-\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
-the output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum
-across all layers to obtain the article embedding:
-\begin{IEEEeqnarray*}{lCl}
-   \bx_T &=& \sum_{i=0}^{24} \alpha_i \bg_i
-\end{IEEEeqnarray*}
-where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $\alpha_i$ are learnable weights.
-
 One limitation of RoBERTa is that the maximum length of the input sequence is
@@
 
+The RoBERTa encoder provides gives us the article embedding $\bX_T \in
+\mathbb{R}^{1024 \times S}$ where $S$ is the number of tokens.
+
 \subsubsection{Face Embedding}
@@
 FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_F \in
+\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bX_F \in
 \mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
@@
 
+\subsubsection{Mixing RoBERTa layers}
+RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
+input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
+embeddings, $\bG_i \in \mathbb{R}^{2048 \times S}$ for $i \in \{0,1,
+2,...,24\}$. This includes the initial uncontextualized embeddings and the
+output of each of the 24 layers. Inspired by Tenney \etal
+\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
+different steps in the traditional NLP pipeline, we take a weighted sum across
+all layers to obtain the article embedding:
+\begin{IEEEeqnarray*}{lCl}
+   \bX_T &=& \sum_{i=0}^{24} \alpha_i \bG_i
+\end{IEEEeqnarray*}
+where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
+and $\alpha_i$ are learnable weights.
+
 \subsubsection{Copying with Multi-headed Attention}

### 2019-11-14 paper/section_3_model.tex
Work on Multi-Head Attention section

@@
 The decoder is a function that estimates $p(y_t)$, the probability of the next
-token, conditional on the past and the context embeddings $\bx_I$, $\bx_T$, and
-$\bx_F$:
+token, conditional on the past $\by_{<t}$ and the context embeddings $\bX_I$,
+$\bX_T$, and $\bX_F$:
 \begin{IEEEeqnarray*}{lCl}
-   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bx_I, \bx_T, \bx_F)
+   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
 \end{IEEEeqnarray*}
@@
 convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
-computed using Scalar-Dot-Product attention \cite{Vaswani2017AttentionIA}.
+computed using multi-head attention \cite{Vaswani2017AttentionIA}.
 
-\subsubsection{Scalar-Dot-Product Attention}
+\subsubsection{Multi-Head Attention}
 
-Let $\bh_t$ be the current hidden state. We first do a linear projection of
-$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
-all three have the same dimension:
+Let $\bh_t \in \mathbb{R}^{1024}$ be the current hidden state when decoding the
+$t$th token. We divide the embedding dimension into 16 attention heads, each
+with size 64. For each head $i \in \{1, 2, ..., 16\}$, we first do a linear
+projection of $\bh_t$ and the image embedding $\bX_I$ into a query $\bq_{It}
+\in \mathbb{R}^{64}$, key $\bK_I \in \mathbb{R}^{64 \times 49}$, and value
+$\bV_I \in \mathbb{R}^{64 \times 49}$:
 \begin{IEEEeqnarray*}{lCl}
-   \bq_T &=& \bW_{Iq} \, \bh_t \\
-   \bk_T &=& \bW_{Ik} \, \bx_I \\
-   \bv_T &=& \bW_{Iv} \, \bx_I
+   \bq_{Iit} &=& \bW_{Iiq} \, \bh_t \\
+   \bK_{Ii} &=& \bW_{Iik} \, \bX_I \\
+   \bV_{Ii} &=& \bW_{Iiv} \, \bX_I
 \end{IEEEeqnarray*}
-Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
-obtained from the dot product between the key and value:
+Then the attended image for each head $\bx'_{Ii} \in \mathbb{R}^{64}$ is the
+weighted sum of the values, where the weights are obtained from the dot product
+between the query and key:
 \begin{IEEEeqnarray*}{lCl}
-   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
+   \bx'_{Ii} &=& \text{softmax}\left(\bK_{Ii}^T \bq_{Iit} \right) \bV_{Ii}
 \end{IEEEeqnarray*}
-We use the same attention mechanism to obtain the attended article $\bx_T'$
-and the attended face $\bx_F'$. These three are then concatenated and fed
-through a feedforward layer:
+The attention from each head is then concatenated into $\bx'_{I} \in
+\mathbb{R}^{1024}$:
 \begin{IEEEeqnarray*}{lCl}
-   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
-   \bx_O &=& \text{LayerNorm}(X_C + \bW_O \, \text{ReLU}(\bW_C \, \bx_C' + \bb_C) + \bb_O)
+   \bx'_{I} &=& [\tx_{I1}, \tx_{I2}, ..., \tx_{I16}]
 \end{IEEEeqnarray*}
-
-For each generation step, we use the Scalar-Dot-Product attention
-\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
-of the three attended representations are then concatenated and fed as input to
-the self-attention layer.
+and the overall image attention $\tx_{I} \in \mathbb{R}^{1024}$ is obtained
+after adding a residual connection and layer normalization:
+\begin{IEEEeqnarray*}{lCl}
+   \tx_{I} &=& \text{LayerNorm}(\bh_t + \bx'_{I})
+\end{IEEEeqnarray*}
+We use the same attention mechanism (with different weight matrices) to obtain
+the attended article $\tx_T$ and the attended face $\tx_F$. These three are
+then concatenated and fed through a feedforward layer:
+\begin{IEEEeqnarray*}{lCl}
+   \tx_C &=& [\tx_I, \tx_T, \tx_F] \\
+   \tx_R &=& \bW_C \, \tx_C + \bb_C \\
+   \tx_D &=& \text{ReLU}(\bW_R \, \tx_R + \bb_R )\\
+   \tx_E &=& \text{LayerNorm}(\tx_R + \bW_D \, \tx_D + \bb_D)
+\end{IEEEeqnarray*}
+The final output $\tx_E \in \mathbb{R}^{1024}$ is used as the input to the
+next transformer block.
 
@@
 
-Our decoder is a transformer architecture with dynamic convolutions
-\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
-found that using dynamic convolutions allows the training to converge faster
-than using the current state-of-the-art GPT-2 architecture
-\cite{Radford2019LanguageMA}.
+Instead of using the standard self-attention module as in current
+state-of-the-art GPT-2 architecture \cite{Radford2019LanguageMA}, we find that
+dynamic convolutions \cite{Wu2018PayLA} are more efficient to train, especially
+when there is limited GPU compute power.
 
-In the standard self-attention module, the input embedding $\bx \in
-\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
-$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$.
+Given an input $\bz_t \in \mathbb{R}^{1024}$, which can either be the input
+embedding of the previous token, or the output from the previous transformer
+block, we first use a feedforward layer with a gated linear unit (GLU)
+\cite{Dauphin2017GLU} as the activation function:
+\begin{IEEEeqnarray*}{lCl}
+   \bz_t' &=& \text{GLU}(\bW_Z \, \bz_t + \bb_Z)
+\end{IEEEeqnarray*}
 

### 2019-11-14 paper/section_3_model.tex
Merge changes to model from Alex

@@
 
+Conceptually our model can be broken into two parts: encoding and decoding. The
+encoding part consists of a set of domain specific encoders for producing high
+level vector representations of images, faces and article text. The output of
+each encoder is a, potentially arbitrary, length set of fixed size vectors that
+represent the input. The decoder sequentially generates captions at the
+sub-word level by applying
+multi-headed attention over the sets of vectors from the encoders, and over a
+representation of the previously generated sub-word units. In
+practice there are a number details which allow us to train this large
+multi-faceted model on a single machine and achieve state-of-the-art
+performance. We have included some these details where appropriate and
+collected together those that do not fit elsewhere into
+Section~\ref{ssec:bag_of_tricks}.
+
 \subsection{Encoders}
 
-Our proposed model takes three inputs: the image, the faces, and article text.
-Each of these inputs first goes through an encoder to give us a vector
-representation.
+Our proposed model takes three types of inputs: image, faces, and article text.
+Each of these inputs is encoded into a set of vectors by domain specific
+encoders pre-trained on data from the matching domain.
 
-\subsubsection{Image Embedding}
+\subsubsection{Image Encoder}
 
-For the image, we feed it through a pretrained ResNet-152 model
-\cite{He2016ResNet} and use the output of the final block, just before the
-pooling layer, as the image embedding $\bX_I \in \mathbb{R}^{2048 \times 49}$.
-The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
-different patches in the image.
+A high level image representation is obtained with a
+ResNet-152~\cite{He2016ResNet} model pre-trained on ImageNet. We use the output
+of the final block before the
+pooling layer as the image representation.
+This is set of 49 different vectors $x_{I,i} \in \mathbb{R}^{2048}$ where each
+vector corresponds to a separate image patch after the image is divided into
+equal size 7 by 7 patches. Using this representation $\bx_I = \{x_{I,i} \in
+\mathbb{R}^{2048}\}_{i=0}^{49}$ allows the decoder to attend different regions
+in the
+image -- a modelling choice that has proven useful in other image captioning
+tasks~\cite{Xu2015ShowAA}.
 
-\subsubsection{Article Embedding}
+\subsubsection{Face Encoder}
 
-For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
-RoBERTa, a more carefully trained BERT \cite{Devlin2019BERT}, is a language
-representation model that provides pretrained contextual embeddings for text.
+We use MTCNN \cite{Zhang2016JointFD} to detect face bounding boxes in the
+image. We then select the largest $M$ faces. A vector representation of each
+face is obtained by passing the bounding boxes to
+FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
+dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
+image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.
+
+Even though the faces are extracted from the image it is useful to consider
+them as an input domain that is separate to the image. This is because
+specialised models are needed to make full use of them.
+
+%them to be a separate
+%input domain since face bounding boxes are extracted as a pre-processing step
+%and we use a specialised model to encode features from each bounding box.
+
+\eat{We then select the top $M$ faces and feed them through a
+FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
+\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_{F} =
+\{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.}
+
+\subsubsection{Article Encoder}
+
+To encode the article text we use RoBERTa~\cite{Liu2019RoBERTaAR} which is a
+recent improvement over the popular BERT~\cite{Devlin2019BERT} model.
+RoBERTa is a language representation model that provides pretrained contextual
+embeddings for text. It consists of 24 layers of bidirectional transformer
+blocks.
+% It is a more carefully trained BERT \cite{Devlin2019BERT} model.
+
 Unlike GloVe \cite{Pennington2014Glove} and word2vec
@@
 Let $\bh_t \in \mathbb{R}^{1024}$ be the current hidden state when decoding the
-$t$th token. We divide the embedding dimension into 16 attention heads, each
-with size 64. For each head $i \in \{1, 2, ..., 16\}$, we first do a linear
-projection of $\bh_t$ and the image embedding $\bX_I$ into a query $\bq_{It}
-\in \mathbb{R}^{64}$, key $\bK_I \in \mathbb{R}^{64 \times 49}$, and value
-$\bV_I \in \mathbb{R}^{64 \times 49}$:
+$t$th token. We use 16 attention heads, each with size 64. For each head $i \in
+\{1, 2, ..., 16\}$, we first do a linear projection of $\bh_t$ and the image
+embedding $\bX_I$ into a query $\bq_{It} \in \mathbb{R}^{64}$, key $\bK_I \in
+\mathbb{R}^{64 \times 49}$, and value $\bV_I \in \mathbb{R}^{64 \times 49}$:
 \begin{IEEEeqnarray*}{lCl}
@@
 state-of-the-art GPT-2 architecture \cite{Radford2019LanguageMA}, we find that
-dynamic convolutions \cite{Wu2018PayLA} are more efficient to train, especially
-when there is limited GPU compute power.
+dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
+when decoding the $t$th token, we have an input $\bz_t \in \mathbb{R}^{1024}$,
+which can either be the input embedding of the previous token, or the output
+from the previous transformer block. Given kernel size $K$, we first do a
+projection of the last $K$ steps using a feedforward layer with a gated linear
+unit (GLU) \cite{Dauphin2017GLU} as the activation function:
+\begin{IEEEeqnarray*}{lCl}
+   \bz_{t-j}' &=& \text{GLU}(\bW_Z \, \bz_{t-j} + \bb_Z) \qquad \forall j \in \{0,1,...,K-1\}
+\end{IEEEeqnarray*}
+the output of the dynamic convolution is simply the weighted sum of these
+projected values:
+\begin{IEEEeqnarray*}{lCl}
+   \tz_t &=& \sum_0^{K-1}
+\end{IEEEeqnarray*}
 
-Given an input $\bz_t \in \mathbb{R}^{1024}$, which can either be the input
-embedding of the previous token, or the output from the previous transformer
-block, we first use a feedforward layer with a gated linear unit (GLU)
-\cite{Dauphin2017GLU} as the activation function:
+We use 16 attention heads, each with size 64. For each head $i \in
+\{1, 2, ..., 16\}$, we first do a linear projection to get the kernel weight
 \begin{IEEEeqnarray*}{lCl}
-   \bz_t' &=& \text{GLU}(\bW_Z \, \bz_t + \bb_Z)
+   \bW \, \bz_t'
 \end{IEEEeqnarray*}

### 2019-11-14 paper/section_3_model.tex
Work on dynamic convolution section

@@
 ResNet-152~\cite{He2016ResNet} model pre-trained on ImageNet. We use the output
-of the final block before the
-pooling layer as the image representation.
-This is set of 49 different vectors $x_{I,i} \in \mathbb{R}^{2048}$ where each
+of the final block before the pooling layer as the image representation. This
+is a set of 49 different vectors $\bx_{I,i} \in \mathbb{R}^{2048}$ where each
 vector corresponds to a separate image patch after the image is divided into
-equal size 7 by 7 patches. Using this representation $\bx_I = \{x_{I,i} \in
-\mathbb{R}^{2048}\}_{i=0}^{49}$ allows the decoder to attend different regions
-in the
-image -- a modelling choice that has proven useful in other image captioning
-tasks~\cite{Xu2015ShowAA}.
+equal size 7 by 7 patches. Using this representation $\bX_I = \{\bx_{I,i} \in
+\mathbb{R}^{2048}\}_{i=1}^{49}$ allows the decoder to attend different regions
+in the image---a modeling choice that has proven useful in other image
+captioning tasks~\cite{Xu2015ShowAA}.
 
@@
 
-We use MTCNN \cite{Zhang2016JointFD} to detect face bounding boxes in the
-image. We then select the largest $M$ faces. A vector representation of each
-face is obtained by passing the bounding boxes to
+We use MTCNN~\cite{Zhang2016JointFD} to detect face bounding boxes in the
+image. We then select the largest four faces (see \ref{ssec:nytimes800k}). A
+vector representation of each face is obtained by passing the bounding boxes to
 FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
 dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
-image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.
+image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=1}^4$.
 
@@
 fit, until we reach the 512 token limit. Note that since we are using BPE, a
-word might consist of many tokens. On average, we can only encode ...... words
-of the article.
+word might consist of many tokens. On average, \verify{we can only encode
+...... words of the article.}
 
-The RoBERTa encoder provides gives us the article embedding $\bX_T \in
-\mathbb{R}^{1024 \times S}$ where $S$ is the number of tokens.
-
-\subsubsection{Face Embedding}
-
-To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
-face bounding boxes. We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
-\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bX_F \in
-\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.
+The RoBERTa encoder provides gives us the set of token embeddings $\bX_{T} =
+\{\bx_{T,i} \in \mathbb{R}^{1024}\}_{i=1}^S$, where $S$ is the number of
+tokens.
 
@@
 
-The decoder is a function that estimates $p(y_t)$, the probability of the next
-token, conditional on the past $\by_{<t}$ and the context embeddings $\bX_I$,
-$\bX_T$, and $\bX_F$:
+The decoder is a function that estimates $p(y_t)$, the probability of the $t$th
+token in the caption, conditional on the past $\by_{<t}$ and the context
+embeddings $\bX_I$, $\bX_T$, and $\bX_F$:
 \begin{IEEEeqnarray*}{lCl}
@@
 
-\subsubsection{Multi-Head Attention}
-
-Let $\bh_t \in \mathbb{R}^{1024}$ be the current hidden state when decoding the
-$t$th token. We use 16 attention heads, each with size 64. For each head $i \in
-\{1, 2, ..., 16\}$, we first do a linear projection of $\bh_t$ and the image
-embedding $\bX_I$ into a query $\bq_{It} \in \mathbb{R}^{64}$, key $\bK_I \in
-\mathbb{R}^{64 \times 49}$, and value $\bV_I \in \mathbb{R}^{64 \times 49}$:
-\begin{IEEEeqnarray*}{lCl}
-   \bq_{Iit} &=& \bW_{Iiq} \, \bh_t \\
-   \bK_{Ii} &=& \bW_{Iik} \, \bX_I \\
-   \bV_{Ii} &=& \bW_{Iiv} \, \bX_I
-\end{IEEEeqnarray*}
-Then the attended image for each head $\bx'_{Ii} \in \mathbb{R}^{64}$ is the
-weighted sum of the values, where the weights are obtained from the dot product
-between the query and key:
-\begin{IEEEeqnarray*}{lCl}
-   \bx'_{Ii} &=& \text{softmax}\left(\bK_{Ii}^T \bq_{Iit} \right) \bV_{Ii}
-\end{IEEEeqnarray*}
-The attention from each head is then concatenated into $\bx'_{I} \in
-\mathbb{R}^{1024}$:
-\begin{IEEEeqnarray*}{lCl}
-   \bx'_{I} &=& [\tx_{I1}, \tx_{I2}, ..., \tx_{I16}]
-\end{IEEEeqnarray*}
-and the overall image attention $\tx_{I} \in \mathbb{R}^{1024}$ is obtained
-after adding a residual connection and layer normalization:
-\begin{IEEEeqnarray*}{lCl}
-   \tx_{I} &=& \text{LayerNorm}(\bh_t + \bx'_{I})
-\end{IEEEeqnarray*}
-We use the same attention mechanism (with different weight matrices) to obtain
-the attended article $\tx_T$ and the attended face $\tx_F$. These three are
-then concatenated and fed through a feedforward layer:
-\begin{IEEEeqnarray*}{lCl}
-   \tx_C &=& [\tx_I, \tx_T, \tx_F] \\
-   \tx_R &=& \bW_C \, \tx_C + \bb_C \\
-   \tx_D &=& \text{ReLU}(\bW_R \, \tx_R + \bb_R )\\
-   \tx_E &=& \text{LayerNorm}(\tx_R + \bW_D \, \tx_D + \bb_D)
-\end{IEEEeqnarray*}
-The final output $\tx_E \in \mathbb{R}^{1024}$ is used as the input to the
-next transformer block.
-
 \subsubsection{Dynamic Convolutions}
@@
 Instead of using the standard self-attention module as in current
-state-of-the-art GPT-2 architecture \cite{Radford2019LanguageMA}, we find that
+state-of-the-art GPT-2 decoder \cite{Radford2019LanguageMA}, we find that
 dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
-when decoding the $t$th token, we have an input $\bz_t \in \mathbb{R}^{1024}$,
-which can either be the input embedding of the previous token, or the output
-from the previous transformer block. Given kernel size $K$, we first do a
-projection of the last $K$ steps using a feedforward layer with a gated linear
-unit (GLU) \cite{Dauphin2017GLU} as the activation function:
+when decoding the $t$th token, we have at the $\ell$th block the input
+$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
+embedding of the previous token. Otherwise it is the output from the previous
+transformer block. Given kernel size $K$ and 16 attention heads, for each head
+$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
+using a feedforward layer:
 \begin{IEEEeqnarray*}{lCl}
-   \bz_{t-j}' &=& \text{GLU}(\bW_Z \, \bz_{t-j} + \bb_Z) \qquad \forall j \in \{0,1,...,K-1\}
+   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
 \end{IEEEeqnarray*}
-the output of the dynamic convolution is simply the weighted sum of these
-projected values:
+where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
+function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
+The output of the dynamic convolution of each head is simply the weighted sum
+of these projected values:
 \begin{IEEEeqnarray*}{lCl}
-   \tz_t &=& \sum_0^{K-1}
+   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
 \end{IEEEeqnarray*}
+where the weights $\gamma_{\ell hj}$ is a linear projection of the input,
+followed by a softmax over the kernel window:
+\begin{IEEEeqnarray*}{lCl}
+   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
+      \bz_{\ell,h,t-j} \right)
+\end{IEEEeqnarray*}
+The overall output is the concatenation of all the head outputs, followed by
+a feedforward with a residual connection and layer normalization:
+\begin{IEEEeqnarray*}{lCl}
+   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
+   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
+             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
+\end{IEEEeqnarray*}
+Note that given kernel size $K$, we can attend to the current time step and the
+last $K-1$ steps. Following closely to \cite{Wu2018PayLA}, our decoder has 4
+layers with kernel sizes 3, 7, 15, and 31, respectively. Thus the final layer
+output will have collected information from the last 51 tokens.
 
-We use 16 attention heads, each with size 64. For each head $i \in
-\{1, 2, ..., 16\}$, we first do a linear projection to get the kernel weight
+\subsubsection{Multi-Head Attention}
+
+Let $\bd_{\ell t} \in \mathbb{R}^{1024}$ be the output of the dynamic
+convolution. We now attend over the image context using multi-head attention,
+also with 16 heads. For each head $h \in \{1, 2, ..., 16\}$, we first do a
+linear projection of $\bd_{\ell t}$ and the image embeddings $\bX_I$ into a
+query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set of keys $\bK_{I \ell h t} =
+\{\bk_{I \ell h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$, and the corresponding
+values $\bV_{I \ell h t} = \{ \bv_{I \ell h t i} \in \mathbb{R}^{64}
+\}_{i=1}^{49}$:
 \begin{IEEEeqnarray*}{lCl}
-   \bW \, \bz_t'
+   \bq_{I\ell ht} &=& \bW_{I \ell h q} \, \bd_{\ell t} \\
+   \bk_{I\ell h i} &=& \bW_{I \ell h k} \, \bx_{I i}
+      \qquad \forall i \in \{1, 2, ..., 49\}\\
+   \bv_{I \ell h i} &=& \bW_{I \ell h v} \, \bx_{I i}
+      \qquad \forall i \in \{1, 2, ..., 49\}
 \end{IEEEeqnarray*}
+Then the attended image for each head is the weighted sum of the values, where
+the weights are obtained from the dot product between the query and key:
+\begin{IEEEeqnarray*}{lCl}
+   \bx'_{I \ell h t} &=& \sum_{i = 1}^{49}
+      \text{softmax}\left(\bk_{I\ell h i}^T \, \bq_{I \ell ht} \right)
+      \bv_{I \ell h i}
+\end{IEEEeqnarray*}
+The attention from each head is then concatenated into $\bx'_{I\ell t} \in
+\mathbb{R}^{1024}$:
+\begin{IEEEeqnarray*}{lCl}
+   \bx'_{I\ell t} &=& [\tx_{I\ell 1 t}, \tx_{I\ell 2 t}, ..., \tx_{I\ell 16 t}]
+\end{IEEEeqnarray*}
+and the overall image attention $\tx_{I\ell t} \in \mathbb{R}^{1024}$ is obtained
+after adding a residual connection and layer normalization:
+\begin{IEEEeqnarray*}{lCl}
+   \tx_{I \ell t} &=& \text{LayerNorm}(\bd_{\ell t} + \bx'_{I\ell t})
+\end{IEEEeqnarray*}
+We use the same attention mechanism (with different weight matrices) to obtain
+the attended article $\tx_{T \ell}$ and the attended face $\tx_{F \ell}$. These
+three are finally concatenated and fed through a feedforward layer:
+\begin{IEEEeqnarray*}{lCl}
+   \tx_{C \ell t} &=& [\tx_{I \ell}, \tx_{T \ell t}, \tx_{F \ell}] \\
+   \tx_{R \ell t} &=& \bW_{C \ell} \, \tx_{C \ell t} + \bb_{C \ell} \\
+   \tx_{D \ell t} &=& \text{ReLU}(\bW_{R \ell} \, \tx_{R \ell t} + \bb_{R \ell} )\\
+   \bz_{\ell + 1,t} &=& \text{LayerNorm}(\tx_{R \ell t} + \bW_{D \ell} \,
+      \tx_{D \ell t} + \bb_{D \ell})
+\end{IEEEeqnarray*}
+The final output $\bz_{\ell + 1,t} \in \mathbb{R}^{1024}$ is used as the input
+to the next transformer block, or if we are in the last block, it is used
+to compute the logits over the token vocabulary.
 
 \subsection{Bag of Tricks}
+\label{ssec:bag_of_tricks}
 

### 2019-11-14 paper/section_2_literature.tex
Rearrange figures
Add Alex' changes on releated works

@@
 
-Early image captioning systems mainly used an RNN architecture with a closed
-vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
-Attention over image patches was later introduced in ``Show, Attend and Tell"
+A large number of methods exist for generating generic image captions that
+describe objects and relationships using only image information. Many of these
+captioning systems use some combination of a Convolutional Neural Network
+encoder and a RNN with a closed
+vocabulary as a decoder~\cite{Karpathy2015DeepVA, Donahue2015LongTR,
+Vinyals2015ShowAT}.
+Attention over image patches was introduced in ``Show, Attend and Tell"
 \cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
 image embeddings and the previous hidden state of the RNN through a multilayer
-perception. Later improvements include giving the model the option to not
-attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
-to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
+perception. Many extensions to these models have been proposed such as giving
+the model the option to not
+attend to any image region~\cite{Lu2017KnowingWT}, using reinforcement learning
+to directly optimise for the CIDEr metric~\cite{Rennie2017SelfCriticalST,
 Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
-generic captions with a limited vocabulary.
+attend to \cite{Anderson2017BottomUpAT}. All of these systems generate
+restricted vocabulary generic captions without considering context external to
+the image.
 
-A more challenging task is to produce captions for news images, in which we
-need to be able to generate entity names. Early non-neural approaches include
+A related task which does consider image context is news image captioning,
+where the image caption is generated using the article text as context.
+One key challenge of news image captioning is generating rare entity names, for
+example the names of people who do not make many media appearances. Early
+non-neural approaches include
 extractive methods that use n-gram models to combine existing phrases
@@
 template.
+
+\begin{figure*}[t]
+    \begin{center}
+    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+    \end{center}
+       \caption{Overall architecture of the model.}
+    \label{fig:short}
+ \end{figure*}
 

### 2019-11-14 paper/section_3_model.tex
Update bag of tricks section

@@
 of the final block before the pooling layer as the image representation. This
-is a set of 49 different vectors $\bx_{I,i} \in \mathbb{R}^{2048}$ where each
+is a set of 49 different vectors $\bx_{Ii} \in \mathbb{R}^{2048}$ where each
 vector corresponds to a separate image patch after the image is divided into
-equal size 7 by 7 patches. Using this representation $\bX_I = \{\bx_{I,i} \in
+equal size 7 by 7 patches. Using this representation $\bX_I = \{\bx_{Ii} \in
 \mathbb{R}^{2048}\}_{i=1}^{49}$ allows the decoder to attend different regions
@@
 We use MTCNN~\cite{Zhang2016JointFD} to detect face bounding boxes in the
-image. We then select the largest four faces (see \ref{ssec:nytimes800k}). A
-vector representation of each face is obtained by passing the bounding boxes to
+image. We then select the largest four faces since the majority of captions
+have at most four personal names (see \ref{ssec:nytimes800k}). A vector
+representation of each face is obtained by passing the bounding boxes to
 FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
 dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
-image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=1}^4$.
+image is $\bx_{F} = \{\bx_{Fi} \in \mathbb{R}^{512}\}_{i=1}^4$.
 
@@
 The RoBERTa encoder provides gives us the set of token embeddings $\bX_{T} =
-\{\bx_{T,i} \in \mathbb{R}^{1024}\}_{i=1}^S$, where $S$ is the number of
-tokens.
+\{\bx_{Ti} \in \mathbb{R}^{1024}\}_{i=1}^S$, where $S$ is the number of tokens.
 
@@
 \end{IEEEeqnarray*}
-In our architecture, the decoder consists of four layers of transformer blocks.
-In each block, the conditioning on past tokens is computed using dynamic
-convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
-computed using multi-head attention \cite{Vaswani2017AttentionIA}.
+In our architecture, the decoder consists of four transformer blocks. In each
+block, the conditioning on past tokens is computed using dynamic convolutions
+\cite{Wu2018PayLA}, and the conditioning on the contexts is computed using
+multi-head attention \cite{Vaswani2017AttentionIA}.
 
@@
 function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
-The output of the dynamic convolution of each head is simply the weighted sum
-of these projected values:
+The output of each head's dynamic convolution is the weighted sum of these
+projected values:
 \begin{IEEEeqnarray*}{lCl}
@@
 \end{IEEEeqnarray*}
-where the weights $\gamma_{\ell hj}$ is a linear projection of the input,
+where the weight $\gamma_{\ell hj}$ is a linear projection of the input,
 followed by a softmax over the kernel window:
@@
 last $K-1$ steps. Following closely to \cite{Wu2018PayLA}, our decoder has 4
-layers with kernel sizes 3, 7, 15, and 31, respectively. Thus the final layer
-output will have collected information from the last 51 tokens.
+transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
+final block output will have collected information from the last 51 tokens.
 
 \subsubsection{Multi-Head Attention}
+\label{ssection:attn}
 
-Let $\bd_{\ell t} \in \mathbb{R}^{1024}$ be the output of the dynamic
-convolution. We now attend over the image context using multi-head attention,
-also with 16 heads. For each head $h \in \{1, 2, ..., 16\}$, we first do a
-linear projection of $\bd_{\ell t}$ and the image embeddings $\bX_I$ into a
-query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set of keys $\bK_{I \ell h t} =
-\{\bk_{I \ell h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$, and the corresponding
-values $\bV_{I \ell h t} = \{ \bv_{I \ell h t i} \in \mathbb{R}^{64}
-\}_{i=1}^{49}$:
+Given $\bd_{\ell t} \in \mathbb{R}^{1024}$, the output of the dynamic
+convolution at layer $\ell$, we can now attend over the image context using
+multi-head attention, also with 16 heads. For each head $h \in \{1, 2, ...,
+16\}$, we first do a linear projection of $\bd_{\ell t}$ and the image
+embeddings $\bX_I$ into a query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set
+of keys $\bK_{I \ell h t} = \{\bk_{I \ell h t i} \in \mathbb{R}^{64}
+\}_{i=1}^{49}$, and the corresponding values $\bV_{I \ell h t} = \{ \bv_{I \ell
+h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$:
 \begin{IEEEeqnarray*}{lCl}
@@
 \begin{IEEEeqnarray*}{lCl}
+   \lambda_{I \ell h i} &=&\text{softmax}\left(\bk_{I\ell h i}^T \bq_{I \ell ht} \right)\\
    \bx'_{I \ell h t} &=& \sum_{i = 1}^{49}
-      \text{softmax}\left(\bk_{I\ell h i}^T \, \bq_{I \ell ht} \right)
-      \bv_{I \ell h i}
+      \lambda_{I \ell h i} \, \bv_{I \ell h i}
 \end{IEEEeqnarray*}
@@
 \end{IEEEeqnarray*}
-We use the same attention mechanism (with different weight matrices) to obtain
-the attended article $\tx_{T \ell}$ and the attended face $\tx_{F \ell}$. These
-three are finally concatenated and fed through a feedforward layer:
+We use the same multi-head attention mechanism (with different weight matrices)
+to obtain the attended article $\tx_{T \ell}$ and the attended face $\tx_{F
+\ell}$. These three are finally concatenated and fed through a feedforward
+layer:
 \begin{IEEEeqnarray*}{lCl}
@@
 
-Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce
-a copying mechanism using multi-headed attention.
+Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce a
+copying mechanism using multi-head attention. We use the final layer output
+$\bz_{5t}$ and the article embeddings $\bX_T$ as inputs to the multi-head
+attention module. Unlike \ref{ssection:attn}, we only need to compute the
+softmax weights $\lambda_i$ (and not the weighted sum of the values). We
+interpret each $\lambda_i$ as the probability of copying $i$th token in the
+article.
 
@@
 
-The BPE vocabulary size is 50265. To make training more efficient, we use adaptive softmax
-\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
-15K, and 25K. We tie the adaptive weights and we share the decoder input and
-output embeddings. We use sinusoidal positional encoding
+The decoder BPE vocabulary size is 50265. To make training more efficient, we
+use adaptive softmax \cite{Grave2016EfficientSA} and divide the vocabulary into
+three clusters: 5K, 15K, and 25K. We tie the adaptive weights and we share the
+decoder input and output embeddings. We use sinusoidal positional encoding
 \cite{Vaswani2017AttentionIA} to represent the position of each token.

### 2019-11-14 paper/section_1_intro.tex
Add Alex's changes to intro and related works

@@
 \end{figure}
-
-One tool that has had seen recent successes in many natural language processing
-tasks is the transformer neural network.
-%\sout{processing, which consist of layers of
-%	self-attention and feed-forward connections stacked on top of each other
-%	\cite{Vaswani2017AttentionIA}. Transformers have}
-Transformers have been show to consistently
-outperforming Recurrent Neural Network architectures in language modeling
-\cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
-%\sout{There are theoretical justifications that transformers could be universal
-%	approximations of sequence-to-sequence functions
-%\cite{Anonymous2020AreTU}.}
-Furthermore, transformer based models such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT} have been shown to
-produce high level text representations suitable for transfer learning.
-Furthermore, using byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent uncommon words as a
-sequence of subword units can enable the transformer function in an open
-vocabulary setting.
 

### 2019-11-14 paper/section_2_literature.tex
Add Alex's changes to intro and related works

@@
 A large number of methods exist for generating generic image captions that
-describe objects and relationships using only image information. Many of these
+describe objects and relationships using only the image as input. Many of these
 captioning systems use some combination of a Convolutional Neural Network
-encoder and a RNN with a closed
+encoder and an RNN with a closed
 vocabulary as a decoder~\cite{Karpathy2015DeepVA, Donahue2015LongTR,
@@
 \cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
-\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
-article and and the VGG19 representation of the image, and feed them as inputs
-to an LSTM generator. However the generator still cannot produce names not
-seen in training.
+sentence \cite{Tariq2017ACE} in the article. The neural network approach taken
+by Ramisa \etal
+\cite{Ramisa2016BreakingNewsAA} was able to generate entirely new text with an
+LSTM decoder that took as input a word2vec representation of the
+article concatenated with a CNN representation of the image. Even so this
+approach was unable produce names that were not seen during training.
 
-To overcome the limitation of a fixed-size vocabulary, template-based methods
-have been used to insert named entities. This involves first generating a
-template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
-DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
-for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
+To overcome the limitation of a fixed-size vocabulary caption templates can be
+used. This involves first generating a
+template sentence with placeholders for named entities, e.g. ``PERSON speaks at
+BUILDING in
+DATE.''. This template can be generated using an LSTM or other sequence
+generation model~\cite{Biten2019GoodNews}. Afterwards, a selection algorithm
+picks the best candidate
+for each placeholder. For example, Lu \etal \cite{Lu2018EntityAI} built a
+knowledge graph
 for each combination of entities and select the most likely combination.
-Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
-benchmark against, picked the sentence with the highest cosine similarity with
-the template and then found the first entity that matches the type of each
-placeholder for insertion. Our proposed model differs from
-\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
-generate a caption with named entities directly without using any intermediate
-template.
+Meanwhile, Biten \etal~\cite{Biten2019GoodNews} filled the template by
+extracting entities from the sentence in the article which had the highest
+cosine similarity to
+the template. One key difference between our proposed model and that of
+previous approaches\cite{Biten2019GoodNews,Lu2018EntityAI} is that our model can
+generate a captions with named entities directly -- without using an
+intermediate template.
+
+%, whose GoodNews dataset we will
+%benchmark against,
 
@@
 
-Transformers are still scarcely used in image captioning. They have been shown
+One tool that has had seen recent successes in many natural language processing
+tasks is the transformer neural network.
+%\sout{processing, which consist of layers of
+%	self-attention and feed-forward connections stacked on top of each other
+%	\cite{Vaswani2017AttentionIA}. Transformers have}
+Transformers have been show to consistently
+outperforming Recurrent Neural Network architectures in language modeling
+\cite{Radford2019LanguageMA},
+story generation \cite{Fan2018HierarchicalNS}, summarization
+\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
+%\sout{There are theoretical justifications that transformers could be universal
+%	approximations of sequence-to-sequence functions
+%\cite{Anonymous2020AreTU}.}
+Furthermore, transformer based models such as BERT \cite{Devlin2019BERT}, XLM
+\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
+\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT} have been shown to
+produce high level text representations suitable for transfer learning.
+Furthermore, using byte-pair
+encoding (BPE) \cite{Sennrich2015NeuralMT} to represent uncommon words as a
+sequence of subword units can enable the transformer function in an open
+vocabulary setting.
+
+Transformers have been shown
 to yield competitive results in generating generic MS COCO captions
@@
 \cite{Zhao2019InformativeIC} have gone further and trained transformers to
-produce named entities in the Conceptual Captions dataset
-\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
-context apart from the image itself, and the authors used web-entity labels,
+produce some named entities in the Conceptual Captions dataset
+\cite{Sharma2018ConceptualCA}. However, this dataset provides no additional
+context to the image, making it a different problem to news image captioning.
+Moreover, the authors used web-entity labels,
 extracted using Google Cloud Vision API, as inputs to the model. In our work,
-we are more ambitious in that we do not explicitly give the model a list of
-entities that should appear in the caption. Instead the model has to determine
-on its own which entities to generate by scanning through and attending to the
-article.
+we do not explicitly give the model a list of
+entities to appear in the caption, instead our model automatically identifies
+relevant entities from the provided news article.
 
 BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
-their data preprocessing step, they explicitly removed rare named entities from
-the captions. We attempt to fill this gap and in particular examine how much
-better BPE can generate rare names compared to template-based methods.
+image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but they
+did not use it for rare named entities as these were removed from
+the captions during pre-processing. In contrast we explicitly examine the use
+of BPE for generating rare names and evaluate it in comparison to
+template-based methods.
+
+%We fill this gap and in particular examine how much
+%better BPE can generate rare names compared to template-based methods.
 
@@
 are various strategies on how to combine embeddings such as addition,
-concatenation, and using multivariate residual modules (MRMs)
-\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
-more complex strategies such as MRMs have shown to yield only minor improvement
-\cite{Wang2019Hierarchical}.
+concatenation, and multivariate residual modules (MRMs)
+\cite{Kim2016MultimodalRL}. In our model we use the vector concatenation
+strategy and leave investigation of the more complex strategies, such as MMRs,
+to future work as they typically only yield minor performance
+improvements~\cite{Wang2019Hierarchical}.

### 2019-11-14 paper/section_0_abstract.tex
Add copying results

@@
     faces), our system is able to describe an image with specific named
-    entities mentioned in the article. Our model achieves a CIDEr score of 54
+    entities mentioned in the article. Our model achieves a CIDEr score of 61
     on the GoodNews dataset, significantly outperforming the previous
@@
     to study the importance of the image location within the text. On
-    NYTimes800k, we achieve a CIDEr of 55. Pretrained models and source code
+    NYTimes800k, we achieve a CIDEr of 65. Pretrained models and source code
     are available from

### 2019-11-14 paper/section_3_model.tex
Fix RoBERTa mixing section

@@
 input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
-embeddings, $\bG_i \in \mathbb{R}^{2048 \times S}$ for $i \in \{0,1,
-2,...,24\}$. This includes the initial uncontextualized embeddings and the
-output of each of the 24 layers. Inspired by Tenney \etal
-\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
-different steps in the traditional NLP pipeline, we take a weighted sum across
-all layers to obtain the article embedding:
+embeddings, $\bG = \{\bg_{\ell i} \in \mathbb{R}^{2048} : i \in \{1, 2,...,
+49\}, \ell \in \{ 0, 1,..., 24 \}\}$. This includes the initial
+uncontextualized embeddings and the output of each of the 24 layers. Inspired
+by Tenney \etal \cite{Tenney2019BertRT}, who showed that different layers in
+BERT represent different steps in the traditional NLP pipeline, we take a
+weighted sum across all layers to obtain the article embedding $\bx_{Ti}$:
 \begin{IEEEeqnarray*}{lCl}
-   \bX_T &=& \sum_{i=0}^{24} \alpha_i \bG_i
+   \bx_{Ti} &=& \sum_{\ell=0}^{24} \alpha_\ell \, \bg_{\ell i}
 \end{IEEEeqnarray*}
-where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
-and $\alpha_i$ are learnable weights.
+where  $\alpha_\ell$ are learnable weights.
 

### 2019-11-14 paper/section_1_intro.tex
Add tilde

@@
 	results on many natural language understanding benchmarks including GLUE
-	\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
+	\cite{Wang2019GLUE}, SuperGLUE~\cite{Wang2019SuperGLUEAS}, and SQuAD
 	\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
@@
 diverse data inputs. The most significant contribution is the use of byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
+encoding (BPE)~\cite{Sennrich2015NeuralMT} to represent a rare word as a
 sequence of subword units, thus giving models the ability to handle an open
@@
 %of an
-%image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
+%image~\cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
 %Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
@@
 %\cite{Young2014FromID} were annotated using only visual cues present in the
-%image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
-%\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
+%image. More recently, datasets such as TIME~\cite{Tariq2017ACE}, BreakingNews
+%\cite{Ramisa2016BreakingNewsAA}, and GoodNews~\cite{Biten2019GoodNews} include
 %real-life captions written by professional journalists. However, existing

### 2019-11-14 paper/section_2_literature.tex
Add tilde

@@
 Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
-attend to \cite{Anderson2017BottomUpAT}. All of these systems generate
+attend to~\cite{Anderson2017BottomUpAT}. All of these systems generate
 restricted vocabulary generic captions without considering context external to
@@
 \cite{Feng2013AutomaticCG} or simply retrieving the most representative
-sentence \cite{Tariq2017ACE} in the article. The neural network approach taken
+sentence~\cite{Tariq2017ACE} in the article. The neural network approach taken
 by Ramisa \etal
@@
 picks the best candidate
-for each placeholder. For example, Lu \etal \cite{Lu2018EntityAI} built a
+for each placeholder. For example, Lu \etal~\cite{Lu2018EntityAI} built a
 knowledge graph
@@
 \cite{Radford2019LanguageMA},
-story generation \cite{Fan2018HierarchicalNS}, summarization
-\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
+story generation~\cite{Fan2018HierarchicalNS}, summarization
+\cite{Subramanian2019OnEA}, and machine translation~\cite{Bojar2018Findings}.
 %\sout{There are theoretical justifications that transformers could be universal
@@
 %\cite{Anonymous2020AreTU}.}
-Furthermore, transformer based models such as BERT \cite{Devlin2019BERT}, XLM
-\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
-\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT} have been shown to
+Furthermore, transformer based models such as BERT~\cite{Devlin2019BERT}, XLM
+\cite{Lample2019CrosslingualLM}, XLNet~\cite{Yang2019XLNetGA}, RoBERTa
+\cite{Liu2019RoBERTaAR}, and ALBERT~\cite{Lan2019ALBERT} have been shown to
 produce high level text representations suitable for transfer learning.
 Furthermore, using byte-pair
-encoding (BPE) \cite{Sennrich2015NeuralMT} to represent uncommon words as a
+encoding (BPE)~\cite{Sennrich2015NeuralMT} to represent uncommon words as a
 sequence of subword units can enable the transformer function in an open
@@
 BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but they
+image captioning work that uses BPE is~\cite{Sharma2018ConceptualCA}, but they
 did not use it for rare named entities as these were removed from
@@
 In addition to attending to image patches, some captioning models also attend
-to object regions \cite{Wang2019Hierarchical} and visual concepts
+to object regions~\cite{Wang2019Hierarchical} and visual concepts
 \cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are

### 2019-11-14 paper/section_3_model.tex
Add tilde

@@
 image. We then select the largest four faces since the majority of captions
-have at most four personal names (see \ref{ssec:nytimes800k}). A vector
+have at most four personal names (see~\ref{ssec:nytimes800k}). A vector
 representation of each face is obtained by passing the bounding boxes to
@@
 \eat{We then select the top $M$ faces and feed them through a
-FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
+FaceNet model~\cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
 \cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_{F} =
@@
 blocks.
-% It is a more carefully trained BERT \cite{Devlin2019BERT} model.
+% It is a more carefully trained BERT~\cite{Devlin2019BERT} model.
 
-Unlike GloVe \cite{Pennington2014Glove} and word2vec
+Unlike GloVe~\cite{Pennington2014Glove} and word2vec
 \cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
@@
 large, many rare names will still get mapped to the unknown token. In contrast,
-RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
+RoBERTa uses BPE~\cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
 encode any word that can be written in Unicode characters.
@@
 \cite{Wu2018PayLA}, and the conditioning on the contexts is computed using
-multi-head attention \cite{Vaswani2017AttentionIA}.
+multi-head attention~\cite{Vaswani2017AttentionIA}.
 
@@
 Instead of using the standard self-attention module as in current
-state-of-the-art GPT-2 decoder \cite{Radford2019LanguageMA}, we find that
-dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
+state-of-the-art GPT-2 decoder~\cite{Radford2019LanguageMA}, we find that
+dynamic convolutions~\cite{Wu2018PayLA} are more efficient to train. Suppose
 when decoding the $t$th token, we have at the $\ell$th block the input
@@
 Note that given kernel size $K$, we can attend to the current time step and the
-last $K-1$ steps. Following closely to \cite{Wu2018PayLA}, our decoder has 4
+last $K-1$ steps. Following closely to~\cite{Wu2018PayLA}, our decoder has 4
 transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
@@
 uncontextualized embeddings and the output of each of the 24 layers. Inspired
-by Tenney \etal \cite{Tenney2019BertRT}, who showed that different layers in
+by Tenney \etal~\cite{Tenney2019BertRT}, who showed that different layers in
 BERT represent different steps in the traditional NLP pipeline, we take a
@@
 
-Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce a
+Inspired by pointer-generator networks~\cite{See2017GetTT}, we introduce a
 copying mechanism using multi-head attention. We use the final layer output
 $\bz_{5t}$ and the article embeddings $\bX_T$ as inputs to the multi-head
-attention module. Unlike \ref{ssection:attn}, we only need to compute the
+attention module. Unlike~\ref{ssection:attn}, we only need to compute the
 softmax weights $\lambda_i$ (and not the weighted sum of the values). We
@@
 The decoder BPE vocabulary size is 50265. To make training more efficient, we
-use adaptive softmax \cite{Grave2016EfficientSA} and divide the vocabulary into
+use adaptive softmax~\cite{Grave2016EfficientSA} and divide the vocabulary into
 three clusters: 5K, 15K, and 25K. We tie the adaptive weights and we share the

### 2019-11-14 paper/section_4_datasets.tex
Work on dynamic convolution section
Add tilde

@@
 \subsection{NYTimes800k}
+\label{ssec:nytimes800k}
 
@@
 
-Table \ref{tab:datasets} presents a comparison between GoodNews and
+Table~\ref{tab:datasets} presents a comparison between GoodNews and
 NYTimes800k. NYTimes800k exhibits several advantages:
@@
 Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure \ref{fig:entities},
+containing at least one named entity. As shown in Figure~\ref{fig:entities},
 the most popular entity type are names of people, comprising a third of all
@@
 We split the training, validation, and test sets according to time, as shown in
-Table \ref{tab:splits}. For example, the test set consists of all captions and
+Table~\ref{tab:splits}. For example, the test set consists of all captions and
 articles in the final three months of the collection period, from June to

### 2019-11-14 paper/section_5_experiments.tex
Add tilde

@@
 
-In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
+In all experiments, we use Adam~\cite{Kingma2015Adam} with the weight decay fix
 \cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
@@
 
-As shown in Table \ref{tab:models}, all of our baselines are designed to have
+As shown in Table~\ref{tab:models}, all of our baselines are designed to have
 roughly the same number of trainable parameters. This allows us to attribute
@@
 
-The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
-the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
-dynamic convolution code are adapted from fairseq \cite{Ott2019Fairseq}.
+The training pipeline is written in PyTorch~\cite{Paszke2017Automatic} using
+the AllenNLP framework~\cite{Gardner2017AllenNLP}. The RoBERTa model and
+dynamic convolution code are adapted from fairseq~\cite{Ott2019Fairseq}.
 
@@
 
-Table \ref{tab:results} shows the BLEU \cite{Papineni2002Bleu}, ROUGE
-\cite{Lin2004ROUGE}, METEOR \cite{Denkowski2014Meteor}, and CIDEr
+Table~\ref{tab:results} shows the BLEU~\cite{Papineni2002Bleu}, ROUGE
+\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
 \cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
-results from the previous state-of-the-art \cite{Biten2019GoodNews}. Note that
+results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
 the numbers reported here are slightly different from the original paper since
 we had to remove a few samples from the test set where the image is no longer
-available. \cite{Biten2019GoodNews} also did some post-processing on the
+available.~\cite{Biten2019GoodNews} also did some post-processing on the
 ground-truth captions such as removing contractions and non-ASCII characters,
@@
 (TF-IDF) to put more importance on less common words such as entity names.
-Table \ref{tab:names} shows the recall and precision of the named entities,
+Table~\ref{tab:names} shows the recall and precision of the named entities,
 personal names, and rare proper nouns.
@@
    \item Our baseline LSTM model with GloVe embeddings yields competitive
-   results to previous the state-of-the-art \cite{Biten2019GoodNews}. This
+   results to previous the state-of-the-art~\cite{Biten2019GoodNews}. This
    means that BPE offers a viable alternative to template-based methods.
@@
 
-Table \ref{tab:names} also looks at the quality of the generated captions. We
+Table~\ref{tab:names} also looks at the quality of the generated captions. We
 look at three metrics: caption length, type-token ratio (TTR), and Flesch

### 2019-11-14 paper/section_3_model.tex
Fix notations

@@
    \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
-      \bz_{\ell,h,t-j} \right)
+      \bz'_{\ell,h,t-j} \right)
 \end{IEEEeqnarray*}
@@
 We use the same multi-head attention mechanism (with different weight matrices)
-to obtain the attended article $\tx_{T \ell}$ and the attended face $\tx_{F
-\ell}$. These three are finally concatenated and fed through a feedforward
+to obtain the attended article $\tx_{T \ell t}$ and the attended face $\tx_{F
+\ell t}$. These three are finally concatenated and fed through a feedforward
 layer:
 \begin{IEEEeqnarray*}{lCl}
-   \tx_{C \ell t} &=& [\tx_{I \ell}, \tx_{T \ell t}, \tx_{F \ell}] \\
+   \tx_{C \ell t} &=& [\tx_{I \ell t}, \tx_{T \ell t}, \tx_{F \ell t}] \\
    \tx_{R \ell t} &=& \bW_{C \ell} \, \tx_{C \ell t} + \bb_{C \ell} \\

### 2019-11-14 paper/section_2_literature.tex
Add LSTM + weighted RoBERTa results

@@
 BPE offers an elegant solution to handling an open vocabulary. To date the only
-image captioning work that uses BPE is~\cite{Sharma2018ConceptualCA}, but they
+image captioning work that uses BPE is~\cite{Zhao2019InformativeIC}, but they
 did not use it for rare named entities as these were removed from

### 2019-11-14 paper/section_4_datasets.tex
Move figure
Add example figure

@@
       Number of articles & 434 272 & 3 052 & 8 495 \\
-      Number of images  & 764 049 & 7 852 & 22 143 \\
+      Number of images  & 764 049 & 7 852 & 21 977 \\
       Start month & Mar 15 & May 19 & Jun 19 \\
@@
 \end{table}
+
+\begin{figure*}[t]
+   \begin{center}
+		\includegraphics[width=0.99\linewidth, frame]{figures/figure_5.pdf}
+	\end{center}
+   \caption{An example from the NYTimes800k test set. The name ``Chromati'' has
+   never appeared in the training data. Words in blue do not appear in the
+   article and are hallucinated by the decoder. Words highlighted in red are
+   spelling mistakes. Underlined words are those that have been copied by the
+   copying mechanism.}
+   \label{fig:short}
+\end{figure*}
 

### 2019-11-14 paper/section_5_experiments.tex
Move figure
Move model complexity to appendix

@@
 
-As shown in Table~\ref{tab:models}, all of our baselines are designed to have
-roughly the same number of trainable parameters. This allows us to attribute
-improvement to the individual model components rather than to simply having a
-bigger model.
-
 The training pipeline is written in PyTorch~\cite{Paszke2017Automatic} using
@@
 
-\begin{table}[t]
-	\caption {Model complexity}
-	\label{tab:models}
-	\centering
-	\begin{tabularx}{\linewidth}{Xc}
-		\toprule
-        & No. of Parameters \\
-      \midrule
-      LSTM + GloVe & 157M \\
-      Transformer + GloVe & 148M \\
-      LSTM + weighted RoBERTa & 159M \\
-      \midrule
-      Transformer + RoBERTa & 154M \\
-      \quad + weighted RoBERTa & 154M \\
-      \quad\quad + face attention & 171M \\
-      \quad\quad\quad + copying & 207M \\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
 \subsection{Results}
-
-\begin{figure*}[t]
-   \begin{center}
-   \fbox{\rule{0pt}{3in} \rule{.9\linewidth}{0pt}}
-   \end{center}
-      \caption{Example captions with success and failure cases.}
-   \label{fig:short}
-\end{figure*}
 

### 2019-11-14 paper/section_5_experiments.tex
Add changes from Alex on experiments

@@
 
-In all experiments, we use Adam~\cite{Kingma2015Adam} with the weight decay fix
-\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
-parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
-decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
-number of training examples, which is 6.6 million. This is equivalent to 16
-epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
-learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
-it linearly afterwards. Training is done with mixed precision to reduce the
-memory footprint. The full model takes 5 days to train on one Titan V GPU.
+For parameter optimisation we use the adaptive gradient algorithm
+Adam~\cite{Kingma2015Adam} with the following
+parameter settings: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$. We
+warm up the
+learning rate in the first 5\% of the training steps to $10^{-4}$, and decay
+it linearly afterwards.
+
+We apply $L_2$ regularisation to all network weights with a value of $10^{-5}$
+and use the weight decay fix~\cite{Loshchilov2018DecoupledWD} to decouple the
+learning rate from the regularisation parameter. We clip the gradient norm at
+0.1. We \verify{ use a batch size of ****** and train all models for 6.6 million
+steps}. This is equivalent to 16
+epochs on GoodNews and 9 epochs on NYTimes800k. Training is done with mixed
+precision to reduce the
+memory footprint and allow our full model to be trained on a single GPU. This
+full model
+takes 5 days to train on one Titan V GPU and
+has 207 million trainable parameters -- see the supplement for the number of
+trainable parameters in each model variant.
 
@@
 
+\subsection{Evaluation Metrics}
+
+We use BLEU~\cite{Papineni2002Bleu}, ROUGE
+\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
+\cite{Vedantam2015CIDEr} scores as they are standard for evaluating image
+captions. These are obtained using the COCO
+caption evaluation toolkit
+\footnote{\href{https://github.com/tylin/coco-caption}
+{https://github.com/tylin/coco-caption}}. In addition, we evaluate the
+precision and recall on: named entities, personal names, and rare proper names.
+\verify{Named entities are identified in both the ground truth captions and
+the generated
+captions using the SpaCy~\cite{} natural language processing toolkit. We then
+count exact string matches between the ground truth entities and generated
+entities.
+For personal names we restrict the set of named entities to those marked as
+PERSON by the SpaCy parser. Rare proper nouns are nouns (as identified by the
+SpaCy Parts-of-Speech tagger) that occur less than ******** times in the
+training
+dataset.}
+
 \subsection{Results}
 
-Table~\ref{tab:results} shows the BLEU~\cite{Papineni2002Bleu}, ROUGE
-\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
-\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
+Table~\ref{tab:results} shows the BLEU, ROUGE
+,METEOR, and CIDEr metrics on GoodNews and NYTimes800k. We show two best
 results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that

### 2019-11-15 paper/section_5_experiments.tex
Add baseline description

@@
 
+\subsection{Baselines and Model Variants}
+
+We show two previous state-of-the-art
+models \textit{Biten (Avg + CtxIns)} and \textit{Biten (TBB +
+	AttIns)}~\cite{Biten2019GoodNews}. To provide a fair comparison we used the
+full caption results released by Biten \etal~\cite{Biten2019GoodNews} and
+re-evaluated them using our evaluation pipeline and slightly different test set
+(which we
+have because of
+broken image URLs). The final metrics are the same as originally reported if
+rounded to the nearest
+whole number.
+
+We evaluate a few key modelling choices: the decoder type (\textit{LSTM} or
+\textit{Transformer}), the text encoder type (\textit{GloVe} or
+\textit{weighted RoBERTa}), the additional context domains
+(\textit{location-aware} and \textit{face attention}), and word copying
+(\textit{copying}). \verify{We keep the total number of trainable parameter for
+each
+model to within 7\% of one another other (148 million to 159 million), with the
+unavoidable exceptions of
+models employing \textit{location-aware} (*****), \textit{face attention} (171
+million), and
+\textit{copying} (207 million).}
+
 \subsection{Results}
 
-Table~\ref{tab:results} shows the BLEU, ROUGE
-,METEOR, and CIDEr metrics on GoodNews and NYTimes800k. We show two best
-results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
+Table~\ref{tab:results} shows the BLEU, ROUGE, METEOR, and CIDEr metrics on
+GoodNews and NYTimes800k.
+
+\eat{The due primarily to broken image links the numbers in the table are
+slightly different to what was previously reported~\cite{Biten2019GoodNews}.
+Note that
 the numbers reported here are slightly different from the original paper since
@@
 both of which we did not do. Despite these differences, the final metrics
-are the same if rounded to the nearest whole number.
+are the same if rounded to the nearest whole number.}
 

### 2019-11-15 paper/section_4_datasets.tex
Move entity distribution to appendix

@@
    \begin{center}
-   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
-   \end{center}
-      \caption{Entity distribution in NYTimes800k training captions. The four
-               most common entity types are personal names, geopolitical
-               entities, organizations, and dates.}
-   \label{fig:entities}
-\end{figure}
-
-\begin{figure}[t]
-   \begin{center}
    \includegraphics[width=0.99\linewidth]{figures/figure_3_faces.pdf}
@@
 Entities play an important role in the dataset, with 97\% of captions
-containing at least one named entity. As shown in Figure~\ref{fig:entities},
-the most popular entity type are names of people, comprising a third of all
-named entities. Furthermore, 71\% of training images contain at least one face
+containing at least one named entity.
+The most popular entity type are names of people, comprising a third of all
+named entities (see the supplementary material for a detailed breakdown of entity types). Furthermore, 71\% of training images contain at least one face
 and 68\% of training captions mention at least one persons name. Figure

### 2019-11-15 paper/section_5_experiments.tex
Update discussion

@@
 \footnote{\href{https://github.com/tylin/coco-caption}
-{https://github.com/tylin/coco-caption}}. In addition, we evaluate the
+{https://github.com/tylin/coco-caption}}. Note that CIDEr is particularly
+suited to evaluating news captioning models as it puts more weight that other
+metrics on uncommon words. In addition, we evaluate the
 precision and recall on: named entities, personal names, and rare proper names.
@@
 dataset.}
+
+To evaluate the quality of the generated captions we also report: caption
+length (in words), type-token ratio (TTR), and Flesch
+reading ease. TTR is the ratio of the number of unique words to the total
+number of words in a caption. The Flesch reading ease takes into account the
+number of words and syllables and produces a score between 0 and 100, where
+higher means being easier to read.
 
@@
 (\textit{location-aware} and \textit{face attention}), and word copying
-(\textit{copying}). \verify{We keep the total number of trainable parameter for
+(\textit{copying}). \verify{Note that all our models use BPE encoding with
+adaptive softmax. We keep the total number of trainable parameter for
 each
@@
 
+\eat{The due primarily to broken image links the numbers in the table are
+	slightly different to what was previously
+	reported~\cite{Biten2019GoodNews}.
+	Note that
+	the numbers reported here are slightly different from the original paper
+	since
+	we had to remove a few samples from the test set where the image is no
+	longer
+	available.~\cite{Biten2019GoodNews} also did some post-processing on the
+	ground-truth captions such as removing contractions and non-ASCII
+	characters,
+	both of which we did not do. Despite these differences, the final metrics
+	are the same if rounded to the nearest whole number.}
+
 \subsection{Results}
+
+\eat{There is a strong correlation between of all these metrics, and in
+general, we
+mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
+(TF-IDF) to put more importance on less common words such as entity names.
+Table~\ref{tab:names} shows the recall and precision of the named entities,
+personal names, and rare proper nouns.}
 
@@
 
-\eat{The due primarily to broken image links the numbers in the table are
-slightly different to what was previously reported~\cite{Biten2019GoodNews}.
-Note that
-the numbers reported here are slightly different from the original paper since
-we had to remove a few samples from the test set where the image is no longer
-available.~\cite{Biten2019GoodNews} also did some post-processing on the
-ground-truth captions such as removing contractions and non-ASCII characters,
-both of which we did not do. Despite these differences, the final metrics
-are the same if rounded to the nearest whole number.}
-
-There is a strong correlation between of all these metrics, and in general, we
-mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
-(TF-IDF) to put more importance on less common words such as entity names.
-Table~\ref{tab:names} shows the recall and precision of the named entities,
-personal names, and rare proper nouns.
-
 We can make the following observations:
@@
 \begin{itemize}
-   \item Our baseline LSTM model with GloVe embeddings yields competitive
-   results to previous the state-of-the-art~\cite{Biten2019GoodNews}. This
-   means that BPE offers a viable alternative to template-based methods.
+   \item Our baseline LSTM model with GloVe embeddings outperforms the previous
+   state-of-the-art~\cite{Biten2019GoodNews}, indicating that BPE encoding
+   offers a viable alternative to template-based methods.
 
-   \item Models with GloVe embeddings are unable to generate rare proper nouns.
-   This is expected since GloVe has a fixed vocabulary and if there is a
-   unknown word in the article, the encoder will simply skip it.
+   \item The word copy mechanism leads to a substantial performance improvement
+   across all metrics. This suggests that BPE encoding is complemented by
+   direct copying, with both contributing to our full models success at
+   generating rare terms.
+
+   \item Models which encode articles using GloVe embeddings are unable to
+   generate rare proper nouns (precision and recall of 0).
+   This is because the encoder skips words that are not part of the fixed GloVe
+   vocabulary. Models that use the BPE based article encoder RoBERTa, and thus
+   have an unbounded input vocabulary, show
+   a clear advantage in rare proper noun generation, with precision as high as
+   38.3\% at a recall of 39.9\%.
 
@@
    the supplementary materials for a detailed breakdown).
+
 \end{itemize}
 
-Table~\ref{tab:names} also looks at the quality of the generated captions. We
-look at three metrics: caption length, type-token ratio (TTR), and Flesch
-reading ease. TTR is the ratio of the number of unique words to the total
-number of words in a caption. The Flesch reading ease takes into account the
-number of words and syllables and produces a score between 0 and 100, where
-higher means being easier to read.
-
-From these metrics, we see that our generated captions are in general still
-shorter than real-life captions, have lower lexical diversity (lower TTR)
-and still use simpler language (higher Flesch reading ease).
+The caption quality metrics in Table~\ref{tab:names} show that our
+models produce captions that are closer in length to the ground truth than
+\textit{Biten}. Moreover, our captions exhibit a level of language complexity
+(as measured
+by Flesch score) that is closer to the ground truth. LSTM based
+models tend to produce the shorter captions than Transformer based models but
+otherwise the quality metrics presented here are not particularly sensitive to
+our modelling choices. Overall our generated captions
+are still
+shorter than the ground-truth captions, have lower lexical diversity (lower TTR)
+and use simpler language (higher Flesch reading ease).

### 2019-11-15 paper/section_5_experiments.tex
Add paragraph on person names

@@
    vocabulary. Models that use the BPE based article encoder RoBERTa, and thus
-   have an unbounded input vocabulary, show
+   have an unbounded vocabulary show
    a clear advantage in rare proper noun generation, with precision as high as
@@
    of personal names. It has no significant effect on other entity types (see
-   the supplementary materials for a detailed breakdown).
+   the supplementary materials for a detailed breakdown). Importantly, personal
+   names is the most common entity type in news captions and so we also see an
+   improvement in BLEU, ROUGE, METEOR, and CIDEr scores. More broadly, this
+   result suggests that introducing specialised vision models tuned to the most
+   common types of objects such as organisations (via logos or landmarks) is a
+   promising way of improving performance on news image captioning.
 

### 2019-11-15 paper/section_2_literature.tex
Add model figure

@@
    \begin{center}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+		\includegraphics[width=0.99\linewidth, frame]{figures/figure_2.pdf}
 	\end{center}
-       \caption{Overall architecture of the model.}
-    \label{fig:short}
+       \caption{Overall architecture of the model. On the left is the decoder,
+       which takes as input a byte-pair token (e.g. 14980 represents the middle
+       token ``arsh'' in ``Varshini''). The grey arrows inside the decoder
+       indicate the convolutions in each layer (we only show the convolutions
+       in the final time step). In each convolution layer, we attend to the
+       three domains: article (green lines), image patches (yellow lines) and
+       faces (orange lines). The grey triangles are switches to determine if we
+       should copy or not. If we copy, we attend to the article embeddings to
+       copy the most attended token (dashed black line). The decoder outputs
+       are byte-pair tokens, which are then combined to form whole words.}
+    \label{fig:model}
  \end{figure*}

### 2019-11-15 scripts/compute_data_statistics.py
Recompute NYTimes800k stats

@@ -59,12 +59,14 @@ def compute_nytimes_stats(nytimes):
         pars = [s['text'] for s in sections if s['type'] == 'paragraph']
         captions = []
 
+        has_image = False
         for s in sections:
             if s['type'] == 'caption':
                 image_path = os.path.join('data/nytimes/images_processed',
                                           f"{s['hash']}.jpg")
                 if not os.path.exists(image_path):
                     continue
+                has_image = True
                 captions.append(s['text'])
 
                 if 'parts_of_speech' in s:
@@ -91,17 +93,18 @@ def compute_nytimes_stats(nytimes):
         if not captions:
             continue
 
-        n_article_words += len(' '.join(pars).split())
-        n_articles += 1
-        n_caption_words += len(' '.join(captions).split())
-        n_captions += len(captions)
-        caption_splits[article['split']] += len(captions)
-        article_splits[article['split']] += 1
+        if has_image:
+            n_article_words += len(' '.join(pars).split())
+            n_articles += 1
+            n_caption_words += len(' '.join(captions).split())
+            n_captions += len(captions)
+            caption_splits[article['split']] += len(captions)
+            article_splits[article['split']] += 1
 
-        if article['pub_date'] < min_date:
-            min_date = article['pub_date']
-        if article['pub_date'] > max_date:
-            max_date = article['pub_date']
+            if article['pub_date'] < min_date:
+                min_date = article['pub_date']
+            if article['pub_date'] > max_date:
+                max_date = article['pub_date']
 
     print('Full NYTimes Dataset:')
     print('No of articles:', n_articles)
@@ -426,10 +429,10 @@ def main():
     goodnews = client.goodnews
 
     # compute_goodnews_stats(goodnews)
-    # compute_nytimes_stats(nytimes)
+    compute_nytimes_stats(nytimes)
     # compute_nytimes_exact_subset_statistics(nytimes, goodnews)
     # compute_face_stats(nytimes)
-    compute_rare_stats(nytimes)
+    # compute_rare_stats(nytimes)
 
 
 if __name__ == '__main__':
